### 2025-02-17 paper/main.tex

% This must be in the first 5 lines to tell arXiv to use pdfLaTeX, which is strongly recommended.
\pdfoutput=1
% In particular, the hyperref package requires pdfLaTeX in order to break URLs across lines.

\documentclass[11pt]{article}

% Change "review" to "final" to generate the final (sometimes called camera-ready) version.
% Change to "preprint" to generate a non-anonymous version with page numbers.
\usepackage[preprint]{coling}

% Standard package includes
\usepackage{times}
\usepackage{latexsym}

% For proper rendering and hyphenation of words containing Latin characters (including in bib files)
\usepackage[T1]{fontenc}
% For Vietnamese characters
% \usepackage[T5]{fontenc}
% See https://www.latex-project.org/help/documentation/encguide.pdf for other character sets

% This assumes your files are encoded as UTF8
\usepackage[utf8]{inputenc}

% This is not strictly necessary, and may be commented out,
% but it will improve the layout of the manuscript,
% and will typically save some space.
\usepackage{microtype}

% This is also not strictly necessary, and may be commented out.
% However, it will improve the aesthetics of text in
% the typewriter font.
\usepackage{inconsolata}

%Including images in your LaTeX document requires adding
%additional package(s)
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{multirow}
\usepackage{booktabs}
\usepackage{amssymb}
\usepackage{hyperref}

% If the title and author information does not fit in the area allocated, uncomment the following
%
%\setlength\titlebox{<dim>}
%
% and set <dim> to something 5cm or larger.

\title{Multimodal Information Extraction of Supermarket Leaflets}

\author{Xincheng Liao\textsuperscript{}, Junwen Duan\textsuperscript{}\thanks{\ \ Corresponding author. Email: \href{mailto:jwduan@csu.edu.cn}{jwduan@csu.edu.cn}}, Yixi Huang\textsuperscript{}, Jianxin Wang\textsuperscript{} \\
Hunan Provincial Key Lab on Bioinformatics, School of Computer Science and Engineering, \\
Central South University, Changsha, Hunan, China \\
\texttt{\{ostars, jwduan, yx.huang\}@csu.edu.cn, jxwang@mail.csu.edu.cn} \\
\href{https://github.com/OStars/RUIE}{https://github.com/OStars/RUIE}
}

\begin{document}
\maketitle
\begin{abstract}
TODO
\end{abstract}

\section{Introduction}
\subsection{Motivation}
\subsection{Problem Statement}
\subsection{Structure of Paper}

\section{Related Works}
\indent{\textbf{Deal Detection}.}
\indent{\textbf{Optical Character Recognition}.}
OCR-Model-Driven methods use OCR tools to acquire text
and bounding box information. Subsequently, they rely
on the models to integrate text, layout, and visual data.

\indent{\textbf{Information Extraction}.}

\section{Methodological Overview}

\section{Deal Detection}
    \subsection{Datasets}
    \subsection{Model}
    \subsection{Experiments}

\section{Optical Character Recognition}

\section{Information Extraction}

\section{Application}

\section{Conclusion}
    \subsection{Summary}
    \subsection{Future Work}
    ww

% Bibliography entries for the entire Anthology, followed by custom entries
%\bibliography{anthology,custom}
% Custom bibliography entries only
\bibliography{references}

\end{document}

### 2025-02-17 src/webapp/main.py
Add webapp

@@ -1,0 +1,298 @@
+from fastapi import FastAPI, Request, File, UploadFile, Form
+from fastapi.responses import HTMLResponse, JSONResponse
+from fastapi.staticfiles import StaticFiles
+from fastapi.templating import Jinja2Templates
+
+import sqlite3
+import os
+from dotenv import load_dotenv
+from typing import Optional
+from datetime import datetime
+import uuid
+from tqdm import tqdm
+
+# YOLO
+from ultralytics import YOLO
+# PDF -> Images
+from pdf2image import convert_from_path
+
+# -------------------------------------------------------------------
+# Globale Variablen / "In-Memory-Speicher" für Demo
+# -------------------------------------------------------------------
+# Wir speichern Segmentationsergebnisse in einem Dictionary:
+# { session_id: [ { "page_image": "...", "detections": [ ... ] }, ... ] }
+# In einer echten Applikation würdest du vermutlich einen persistenten Speicher verwenden
+# oder das Ergebnis nach einer Zeit verwerfen.
+SEGMENTATION_CACHE = {}
+
+# -------------------------------------------------------------------
+# Projektordner aus .env laden
+# -------------------------------------------------------------------
+load_dotenv(override=True)
+
+PROJECT_DIR = os.getenv("PROJECT_DIR", ".")
+DB_PATH = os.path.join(PROJECT_DIR, "crawled_leaflets", "supermarket_leaflets.db")
+MODELS_DIR = os.path.join(PROJECT_DIR, "models")
+DEALS_DIR = os.path.join(PROJECT_DIR, "deals")
+YOLOV11_PATH = r"./models/model.pt"
+
+# Erstelle FastAPI-App
+app = FastAPI()
+model = YOLO(YOLOV11_PATH, verbose=False)
+
+# Static Files (CSS, JS etc.)
+app.mount("/static", StaticFiles(directory="static"), name="static")
+app.mount(
+    "/onedrive-images",
+    StaticFiles(directory=DEALS_DIR),
+    name="onedrive-images"
+)
+
+all_images = {}
+
+for root, dirs, files in tqdm(os.walk(DEALS_DIR), desc="Loading image paths"):
+    for file in files:
+        if file.endswith(".png") and "annotated" not in file:
+            # also replace DEALS_DIR with /onedrive-images/dirs_to_file/file
+            all_images[file] = f"/onedrive-images{root.replace(DEALS_DIR, '')}/{file}"
+
[…]

### 2025-02-17 src/webapp/static/js/app.js

@@ -1,0 +1,89 @@
+let currentPage = 1;
+
+async function fetchDeals(page = 1) {
+    currentPage = page;
+
+    const search = document.getElementById("searchInput").value.trim();
+    const metadataOnly = document.getElementById("metadataOnly").checked;
+    const supermarket = document.getElementById("supermarketSelect").value;
+    const validOnly = document.getElementById("validOnly").checked;
+    const sortByDate = document.getElementById("sortByDate").checked;
+
+    const params = new URLSearchParams();
+    params.append("page", page);
+    if (search) params.append("search", search);
+    if (supermarket) params.append("supermarket", supermarket);
+    if (validOnly) params.append("valid_only", "true");
+    if (metadataOnly) params.append("metadata_only", "true");
+    if (sortByDate) params.append("sort_by_date", "true");
+
+    const url = "/api/deals?" + params.toString();
+
+    try {
+        const res = await fetch(url);
+        const data = await res.json();
+        renderDeals(data.deals);
+    } catch (error) {
+        console.error("Error fetching deals:", error);
+    }
+}
+
+function renderDeals(deals) {
+    const container = document.getElementById("dealsContainer");
+    container.innerHTML = ""; // Reset
+
+    deals.forEach((deal) => {
+        const dealDiv = document.createElement("div");
+        dealDiv.classList.add("deal-card");
+
+        // Bild
+        const img = document.createElement("img");
+        // Du hast in der DB den Pfad, z.B. "img_name" -> hier anpassen:
+        img.src = deal.img_name ? deal.img_name : "/static/img/placeholder.png";
+        dealDiv.appendChild(img);
+
+        // Supermarkt + Produktname
+        const title = document.createElement("h2");
+        title.innerText = `${deal.supermarket_name || ""}: ${deal.clean_title || "Ohne Titel"}`;
+        dealDiv.appendChild(title);
+
+        // Preis
+        const priceInfo = document.createElement("p");
+        priceInfo.innerText = `Preis: ${deal.price || "?"} (alt: ${deal.price_old || "?"})`;
+        dealDiv.appendChild(priceInfo);
+
+        // Discount
+        if (deal.discount) {
+            const discount = document.createElement("p");
+            discount.innerText = `Discount: ${deal.discount}`;
+            dealDiv.appendChild(discount);
+        }
+
+        // Beschreibung
+        if (deal.description) {
[…]

### 2025-02-17 src/webapp/static/js/preview.js

@@ -1,0 +1,197 @@
+let pagesData = [];
+let currentPageIndex = 0;
+
+let pageImageEl;
+let canvasEl;
+let ctx;
+let highlightedPolygonIndex = -1; // Index des Polygons, das gerade gehighlightet ist
+
+let modal;
+let modalTitle;
+let modalText;
+let closeModalBtn;
+
+document.addEventListener("DOMContentLoaded", async () => {
+    pageImageEl = document.getElementById("pageImage");
+    canvasEl = document.getElementById("overlayCanvas");
+    ctx = canvasEl.getContext("2d");
+
+    modal = document.getElementById("modal");
+    modalTitle = document.getElementById("modalTitle");
+    modalText = document.getElementById("modalText");
+    closeModalBtn = document.getElementById("closeModal");
+
+    document.getElementById("prevBtn").addEventListener("click", prevPage);
+    document.getElementById("nextBtn").addEventListener("click", nextPage);
+
+    // Modal schließen
+    closeModalBtn.onclick = () => { modal.style.display = "none"; };
+    window.onclick = (evt) => {
+        if (evt.target === modal) {
+            modal.style.display = "none";
+        }
+    };
+
+    // Daten vom Server laden
+    await loadPreviewData();
+    renderPage();
+});
+
+async function loadPreviewData() {
+    const url = `/api/preview_data?session_id=${sessionId}`;
+    const res = await fetch(url);
+    if (!res.ok) {
+        alert("Fehler beim Laden der Preview-Daten.");
+        return;
+    }
+    const data = await res.json();
+    pagesData = data.pages || [];
+    if (pagesData.length === 0) {
+        alert("Keine Seiten enthalten.");
+    }
+    currentPageIndex = 0;
+}
+
+function renderPage() {
+    const pageData = pagesData[currentPageIndex];
+    const imgSrc = `/tmp/${pageData.page_image}`;
+    pageImageEl.src = imgSrc;
+
+    // Wenn das Bild geladen ist
+    pageImageEl.onload = () => {
+        // Canvas anpassen
+        canvasEl.width = pageImageEl.width;
+        canvasEl.height = pageImageEl.height;
+
+        // Originalgröße laut Server
+        const origWidth = pageData.original_size[0];
+        const origHeight = pageData.original_size[1];
+
+        // Aktuelle Anzeigegröße
[…]

### 2025-02-18 src/database/update_deal_metadata.py
Finish webapp

@@ -56,10 +56,11 @@ class DealMetadataUpdater:
             metadata_df.iterrows(), total=len(metadata_df), desc="Updating metadata"
         ):
             # img_name is with .png extension
+            deal_image_name = row["img_name"]
+            deal_image_name = deal_image_name + ".png" if not deal_image_name.endswith(".png") else deal_image_name
 
             if not self.force_recreate:
                 # check if deal already exists
-                deal_image_name = row["img_name"]
                 deal = self.db_queries._query_db(
                     "SELECT * FROM deals WHERE img_name = :deal_image_name",
                     {"deal_image_name": deal_image_name},
@@ -67,7 +68,6 @@ class DealMetadataUpdater:
                 if deal:
                     continue
 
-            deal_image_name = row["img_name"]
             deal_brand = row["Marke"]
             deal_product = row["Produktname"]
             deal_original_price = row["Original Preis"]

### 2025-02-18 src/webapp/deal_processing.py

@@ -1,0 +1,62 @@
+from pydantic import BaseModel
+from typing import Optional, List
+from collections import defaultdict
+import os
+import pandas as pd
+from tqdm import tqdm
+import json
+from ollama import chat
+
+class DealDescription(BaseModel):
+    brand: Optional[str] = None
+    productname: Optional[str] = None
+    unbinding_price_recommendation: Optional[float] = None
+    deal_price: float = None
+    weight: Optional[str] = None
+
+def process_image(img_path: str, model: str) -> dict:
+    """
+    Processes a single deal image given by its file path using the vision-language model.
+    Returns a dictionary with the extracted structured information.
+    """
+    response = chat(
+        model=model,
+        format=DealDescription.model_json_schema(),
+        messages=[{
+            "role": "user",
+            "content": (
+                """
+                You are an advanced vision language model specializing in structured data extraction from an image of a deal. Your task is to extract structured information from a supermarket deal.
+
+                Extraction Fields:
+                    - brand: The brand name, if available (e.g. "Coca Cola", "Milka", "Nestle", "Müller", "Iglo").
+                    - productname: The name of the product without mentioning the brand and description.
+                    - unbinding_price_recommendation: The price of the product without discount, if given (e.g. 2.99, 3.50, 1.99).
+                    - deal_price: The price of the product on sale (e.g. 1.99, 2.50, 0.99). Never negative.
+                    - weight: The amount of the product, if given (e.g. 500g, 1kg, 1 piece).
+                """
+            ),
+            "images": [img_path],
+        }],
+        options={"temperature": 0}
+    )
+
+    try:
+        image_description = DealDescription.model_validate_json(response.message.content)
+    except Exception as e:
+        image_description = DealDescription(
+            brand="unknown",
+            productname="unknown",
+            unbinding_price_recommendation=None,
+            deal_price=0.0,
+            weight="unknown"
+        )
+
+    return {
+        "img_name": os.path.basename(img_path),
+        "brand": image_description.brand,
+        "productname": image_description.productname,
+        "original_price": image_description.unbinding_price_recommendation,
+        "deal_price": image_description.deal_price,
+        "weight": image_description.weight
+    }

### 2025-02-18 src/webapp/main.py

@@ -11,76 +11,60 @@ from datetime import datetime
 import uuid
 from tqdm import tqdm
 
-# YOLO
 from ultralytics import YOLO
-# PDF -> Images
 from pdf2image import convert_from_path
+from PIL import Image, ImageDraw  # Ensure ImageDraw is imported
+from deal_processing import process_image  # import process_image from deal_processing.py
 
-# -------------------------------------------------------------------
-# Globale Variablen / "In-Memory-Speicher" für Demo
-# -------------------------------------------------------------------
-# Wir speichern Segmentationsergebnisse in einem Dictionary:
-# { session_id: [ { "page_image": "...", "detections": [ ... ] }, ... ] }
-# In einer echten Applikation würdest du vermutlich einen persistenten Speicher verwenden
-# oder das Ergebnis nach einer Zeit verwerfen.
 SEGMENTATION_CACHE = {}
 
-# -------------------------------------------------------------------
-# Projektordner aus .env laden
-# -------------------------------------------------------------------
 load_dotenv(override=True)
 
 PROJECT_DIR = os.getenv("PROJECT_DIR", ".")
 DB_PATH = os.path.join(PROJECT_DIR, "crawled_leaflets", "supermarket_leaflets.db")
 MODELS_DIR = os.path.join(PROJECT_DIR, "models")
 DEALS_DIR = os.path.join(PROJECT_DIR, "deals")
-YOLOV11_PATH = r"./models/model.pt"
 
-# Erstelle FastAPI-App
 app = FastAPI()
-model = YOLO(YOLOV11_PATH, verbose=False)
 
-# Static Files (CSS, JS etc.)
 app.mount("/static", StaticFiles(directory="static"), name="static")
 app.mount(
     "/onedrive-images",
     StaticFiles(directory=DEALS_DIR),
     name="onedrive-images"
 )
+YOLOV11_PATH = os.path.join(MODELS_DIR, "model.pt")
+model = YOLO(YOLOV11_PATH, verbose=False)
 
 all_images = {}
 
 for root, dirs, files in tqdm(os.walk(DEALS_DIR), desc="Loading image paths"):
     for file in files:
         if file.endswith(".png") and "annotated" not in file:
-            # also replace DEALS_DIR with /onedrive-images/dirs_to_file/file
             all_images[file] = f"/onedrive-images{root.replace(DEALS_DIR, '')}/{file}"
 
-# Templates (Jinja2)
 templates = Jinja2Templates(directory="templates")
 
[…]

### 2025-02-18 src/webapp/static/js/app.js

@@ -28,50 +28,115 @@ async function fetchDeals(page = 1) {
     }
 }
 
+function capitalizeFirstLetter(val) {
+    return String(val).charAt(0).toUpperCase() + String(val).slice(1);
+}
+
 function renderDeals(deals) {
     const container = document.getElementById("dealsContainer");
-    container.innerHTML = ""; // Reset
+    container.innerHTML = "";
 
     deals.forEach((deal) => {
-        const dealDiv = document.createElement("div");
-        dealDiv.classList.add("deal-card");
+        const card = document.createElement("div");
+        card.classList.add("deal-card");
 
-        // Bild
+        const header = document.createElement("div");
+        header.classList.add("deal-header");
+        header.innerText = capitalizeFirstLetter(deal.supermarket_name) || "Unbekannt";
+        card.appendChild(header);
+
+        const imgContainer = document.createElement("div");
+        imgContainer.classList.add("deal-image-container");
         const img = document.createElement("img");
-        // Du hast in der DB den Pfad, z.B. "img_name" -> hier anpassen:
-        img.src = deal.img_name ? deal.img_name : "/static/img/placeholder.png";
-        dealDiv.appendChild(img);
+        img.src = deal.img_name || "/static/img/placeholder.png";
+        imgContainer.appendChild(img);
+        card.appendChild(imgContainer);
 
-        // Supermarkt + Produktname
-        const title = document.createElement("h2");
-        title.innerText = `${deal.supermarket_name || ""}: ${deal.clean_title || "Ohne Titel"}`;
-        dealDiv.appendChild(title);
+        const content = document.createElement("div");
+        content.classList.add("deal-content");
 
-        // Preis
-        const priceInfo = document.createElement("p");
-        priceInfo.innerText = `Preis: ${deal.price || "?"} (alt: ${deal.price_old || "?"})`;
-        dealDiv.appendChild(priceInfo);
+        const titleEl = document.createElement("div");
+        titleEl.classList.add("deal-title");
+        titleEl.innerText = deal.clean_title || "Ohne Titel";
+        content.appendChild(titleEl);
 
-        // Discount
-        if (deal.discount) {
-            const discount = document.createElement("p");
-            discount.innerText = `Discount: ${deal.discount}`;
-            dealDiv.appendChild(discount);
+        const priceWrapper = document.createElement("div");
+        if (deal.price_old && deal.price_old > 0) {
[…]

### 2025-02-18 src/webapp/static/js/preview.js

@@ -4,7 +4,7 @@ let currentPageIndex = 0;
 let pageImageEl;
 let canvasEl;
 let ctx;
-let highlightedPolygonIndex = -1; // Index des Polygons, das gerade gehighlightet ist
+let highlightedPolygonIndex = -1;
 
 let modal;
 let modalTitle;
@@ -24,7 +24,6 @@ document.addEventListener("DOMContentLoaded", async () => {
     document.getElementById("prevBtn").addEventListener("click", prevPage);
     document.getElementById("nextBtn").addEventListener("click", nextPage);
 
-    // Modal schließen
     closeModalBtn.onclick = () => { modal.style.display = "none"; };
     window.onclick = (evt) => {
         if (evt.target === modal) {
@@ -32,7 +31,6 @@ document.addEventListener("DOMContentLoaded", async () => {
         }
     };
 
-    // Daten vom Server laden
     await loadPreviewData();
     renderPage();
 });
@@ -57,25 +55,19 @@ function renderPage() {
     const imgSrc = `/tmp/${pageData.page_image}`;
     pageImageEl.src = imgSrc;
 
-    // Wenn das Bild geladen ist
     pageImageEl.onload = () => {
-        // Canvas anpassen
         canvasEl.width = pageImageEl.width;
         canvasEl.height = pageImageEl.height;
 
-        // Originalgröße laut Server
         const origWidth = pageData.original_size[0];
         const origHeight = pageData.original_size[1];
 
-        // Aktuelle Anzeigegröße
         const dispWidth = pageImageEl.width;
         const dispHeight = pageImageEl.height;
 
-        // Skalierungsfaktoren
         const ratioX = dispWidth / origWidth;
         const ratioY = dispHeight / origHeight;
 
-        // Polygone runterskalieren
         const scaledPolygons = pageData.polygons.map(det => {
             const scaledPoly = det.polygon.map(([x, y]) => {
                 return [x * ratioX, y * ratioY];
@@ -87,14 +79,10 @@ function renderPage() {
             };
         });
 
-        // Zeichnen
         drawPolygons(scaledPolygons, -1);
 
-        // Mouse-Events
         canvasEl.onmousemove = e => handleMouseMove(e, scaledPolygons);
         canvasEl.onclick = e => handleMouseClick(e, scaledPolygons);
-
-        // ...
     };
 }
 
@@ -110,13 +98,12 @@ function drawPolygons(polygons, highlightIndex) {
         }
         ctx.closePath();
 
-        // Farbe wählen
[…]

### 2025-02-18 paper/main_ilyi.tex
Add recent changes.

% This must be in the first 5 lines to tell arXiv to use pdfLaTeX, which is strongly recommended.
\pdfoutput=1
% In particular, the hyperref package requires pdfLaTeX in order to break URLs across lines.

\documentclass[11pt]{article}

% Change "review" to "final" to generate the final (sometimes called camera-ready) version.
% Change to "preprint" to generate a non-anonymous version with page numbers.
\usepackage[preprint]{coling}

% Standard package includes
\usepackage{times}
\usepackage{latexsym}

% For proper rendering and hyphenation of words containing Latin characters (including in bib files)
\usepackage[T1]{fontenc}
% For Vietnamese characters
% \usepackage[T5]{fontenc}
% See https://www.latex-project.org/help/documentation/encguide.pdf for other character sets

% This assumes your files are encoded as UTF8
\usepackage[utf8]{inputenc}

% This is not strictly necessary, and may be commented out,
% but it will improve the layout of the manuscript,
% and will typically save some space.
\usepackage{microtype}

% This is also not strictly necessary, and may be commented out.
% However, it will improve the aesthetics of text in
% the typewriter font.
\usepackage{inconsolata}

%Including images in your LaTeX document requires adding
%additional package(s)
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{multirow}
\usepackage{booktabs}
\usepackage{amssymb}
\usepackage{hyperref}

% If the title and author information does not fit in the area allocated, uncomment the following
%
%\setlength\titlebox{<dim>}
%
% and set <dim> to something 5cm or larger.

\title{Multimodal Information Extraction of Supermarket Leaflets}

\author{Xincheng Liao\textsuperscript{}, Junwen Duan\textsuperscript{}\thanks{\ \ Corresponding author. Email: \href{mailto:jwduan@csu.edu.cn}{jwduan@csu.edu.cn}}, Yixi Huang\textsuperscript{}, Jianxin Wang\textsuperscript{} \\
Hunan Provincial Key Lab on Bioinformatics, School of Computer Science and Engineering, \\
Central South University, Changsha, Hunan, China \\
\texttt{\{ostars, jwduan, yx.huang\}@csu.edu.cn, jxwang@mail.csu.edu.cn} \\
\href{https://github.com/OStars/RUIE}{https://github.com/OStars/RUIE}
}

\begin{document}
\maketitle
\begin{abstract}
TODO
\end{abstract}

\section{Introduction}
\subsection{Motivation}
\subsection{Problem Statement}
\subsection{Contributions}

\section{Related Works}
\indent{\textbf{Deal Detection}.}
\indent{\textbf{Optical Character Recognition}.}
OCR-Model-Driven methods use OCR tools to acquire text
and bounding box information. Subsequently, they rely
on the models to integrate text, layout, and visual data.

\indent{\textbf{Information Extraction}.}

\section{Deal Detection}
    \subsection{Datasets}
    \subsection{Model}
    \subsection{Experiments}

\section{Information Extraction of Supermarket Deals}
    % - Subsequent to detection and separation of deals, the goal is to extract useful information from it.
    % - Difficulties
    %     - High variety of layouts, colors, fonts, sizes
    %         - Deal sometimes have superscripted decimals and no separation dot.
    %         - Original prices are sometimes striked through.
    %         - Deal prices are sometimes in a very different font to the ones it was trained on.
    %         - Overlapping elements
    %     - Multimodal information
    %         - Product image: visual
    %         - Text: alphabetical + numerical
    %     - OCR errors
    %     - Eigennamen (mostly brand names)
    %     - German language
    % - Goal: Extract 
    %     - Product name
    %     - brand
    %     - original price
    %     - deal price
    %     - unit
Subsequently to the detection and separation of supermarket deals, the overarching goal of using these in applications requires the extraction of the various useful information from these deals. 
The task of extracting meaningful and structured information from supermarket deal images is a complex and multi-faceted problem, requiring the integration of various modalities, overcoming challenges posed by noisy data, and leveraging deep learning techniques. This section provides a detailed exploration of the underlying challenges, methodologies, and the theoretical and practical framework needed to perform such extraction.

\subsection{Challenges in Information Extraction for Supermarket Deals}

Supermarket deal extraction involves a series of challenges that require careful attention and sophisticated methods to resolve. These challenges include the diversity of layout and format in the images, the multimodal nature of the data, the frequent occurrence of Optical Character Recognition (OCR) errors, and the specific linguistic and cultural issues posed by the German language.

% \subsubsection{High Variety in Layouts and Visual Elements}
\indent{\textbf{High Variety in Layouts and Visual Elements.}}
Supermarket deals exhibit considerable variability in layout, color schemes, font choices, and text sizes, which hinders automatic detection and extraction. Deals are often printed with superscripted decimals or without clear separation between integer and fractional components of the price (e.g., "2.29" might appear as "229"). This phenomenon exacerbates OCR difficulties. Additionally, original prices may be struck through, while deal prices are sometimes printed in drastically different fonts than those the OCR model was trained on. Furthermore, overlapping elements—such as product images or additional textual information—often interfere with text extraction and localization. These diverse visual elements require robust and flexible models capable of accommodating such variability.

% \subsubsection{Multimodal Information}
\indent{\textbf{Multimodal Information.}}
Supermarket deal images consist of both visual (e.g., product images) and textual (e.g., brand names, prices, and product descriptions) modalities, each contributing different types of information. While text provides rich information about the product’s identity, pricing, and units, the image serves as a supplementary modality that aids in product identification, brand recognition, and other visual cues. Multimodal fusion, where information from both text and image domains is integrated, is a key challenge, and existing models must effectively leverage both sources to provide high-quality extraction.

\indent{\textbf{Conversion Errors and Linguistic Challenges.}}
OCR systems frequently introduce errors, particularly when dealing with non-standard fonts, noisy backgrounds, or small text. This is particularly problematic when extracting numerical data such as prices. Common errors include misinterpretation of decimals and digits (e.g., "229" instead of "2.29") and missing characters. To address this, OCR post-processing steps, such as error correction using context-based reasoning or dedicated error models, are required. Additionally, the presence of proper nouns—particularly brand names—adds complexity, as these entities may not appear in typical language models, making their extraction difficult. Furthermore, the German language presents its own set of challenges, including compound words, specific punctuation conventions, and diverse word forms, all of which must be accounted for in any robust extraction model.

\indent{\textbf{Ambiguities.}}
The presence of overlapping elements—whether textual or graphical—can lead to a degradation in the extraction accuracy. This challenge is compounded when the overlap involves essential information, such as when the original price is partially obscured by a product image or strike-through marks. Furthermore, ambiguity in labeling and the context in which different pieces of information appear in the deal image can create difficulties in associating text with the correct object (e.g., associating a price with a product rather than the surrounding descriptive text).

\subsection{Formal Approach}
Formally, the task of information extraction from a deal image can be defined as the identification of specific entities, including the product name, brand, original price, deal price, and unit. We define the following set of output labels:
\begin{equation}
\mathcal{Y} = \{y_{i}\}_{i=1}^{n},
\end{equation}
where \(y_{i}\) represents the $i$-th entity in the deal image. In the following, the entities are defined as:
\begin{itemize}
    \item \(y_{\text{product\_name}}\): The name of the product.
    \item \(y_{\text{brand}}\): The brand of the product.
    \item \(y_{\text{original\_price}}\): The original price of the product.
    \item \(y_{\text{deal\_price}}\): The deal price of the product.
    \item \(y_{\text{unit}}\): The unit of the product (e.g., weight, volume).
\end{itemize}

To extract these entities, one aims to learn a function \(f(\cdot)\) that maps an input image \(I\) to the desired outputs:
\begin{equation}
    f: I \to \mathcal{Y},
\end{equation}
where \( I \) is the deal image, and \( \mathcal{Y} \) represents the extracted entities.

The choice of the function \( f(\cdot) \) is an architectural decision that depends on the specific requirements of the task, the nature of the data, the available resources, and the desired performance metrics.

\subsection{Architectural Approaches to Information Extraction}
- Classical methods: Rule-based, template-based
- Traditional methods: Dividing into multi-stage
    - 1. Text detection
    - 2. Text recognition
    - 3. Key-value pair extraction
- OCR + LLM
- End2End: Vision Encoder Decoder Model
    - Donut 
- E2E: LVLM

\subsection{Dataset Creation}
Since there was no dataset to evaluate or train, a custom dataset was created by manually annotating a collection of supermarket deal images. The dataset includes images with diverse layouts, fonts, and colors to ensure robustness. Each image is annotated with bounding boxes for text regions and corresponding labels for product name, brand, original price, deal price, and unit. The dataset is split into training, validation, and test sets to facilitate model development and evaluation. 
% Table \ref{tab:dataset} provides an overview of the custom dataset and Figure \ref{fig:dataset} shows sample images with annotations.
% TODO: Add table and figure

\subsection{Optical Character Recognition}
Optical Character Recognition (OCR) is a critical component in the information extraction pipeline. Several OCR solutions were evaluated to determine the most suitable one for our task. The evaluated OCR tools include Tesseract, EasyOCR, PaddleOCR, and DocTR. Each tool was assessed based on its accuracy, speed, and ability to handle diverse fonts and layouts.

\subsection{Experiments}
\indent{\textbf{Setup}.}
The experiments were conducted to compare the performance of different OCR solutions and end-to-end models for information extraction. The evaluation metrics include precision, recall, and F1-score for each entity type (product name, brand, original price, deal price, and unit). The experiments were performed on the test set of the custom dataset.

\indent{\textbf{Results}.}
The results of the experiments indicate that the end-to-end models, such as the Vision Encoder Decoder Model (e.g., Donut) and Large Vision-Language Models (LVLM), outperform traditional OCR-based methods in terms of accuracy and robustness. The OCR + LLM approach also shows promising results, particularly in handling OCR errors and extracting key-value pairs.

\subsection{Evaluation}
The evaluation of the models was conducted using standard metrics, including precision, recall, and F1-score. The comparison between LVLM, OCR + LLM, and Donut models highlights the strengths and weaknesses of each approach. The results demonstrate that end-to-end models provide superior performance in extracting structured information from supermarket deal images.

\section{Application}
\subsection{Database}

\subsection{Optical Character Recognition}

    \subsection{Experiments}
    \indent{\textbf{Setup}.}
    - Common OCR solutions: Tesseract, EasyOCR, PaddleOCR, DocTR
    - Goal: Which OCR solution is the best for our task?
    -

    \subsection{Evaluation}
    - LVLM, OCR+LLM, Donut
    - OCR + LLM Vergleich

\section{Application}
    \section{Database}
    \section{Front End / Webapp}

\section{Conclusion}
    \subsection{Summary}
    \subsection{Future Work}
    ww

% Bibliography entries for the entire Anthology, followed by custom entries
%\bibliography{anthology,custom}
% Custom bibliography entries only
\bibliography{references}

\end{document}

### 2025-02-18 src/extraction/evaluation/evaluate_ocr-llm_donut_lvlm.py

@@ -1,0 +1,596 @@
+# General imports
+from collections import defaultdict
+import datetime
+import json
+import os
+import pickle
+import re
+import traceback
+import cv2
+import matplotlib.pyplot as plt
+import pandas as pd
+import numpy as np
+from pathlib import Path
+import seaborn as sns
+import pickle
+import jellyfish
+from dotenv import load_dotenv
+
+# --- OCR
+from paddleocr import PaddleOCR
+import pytesseract
+import easyocr
+from doctr.models import ocr_predictor
+
+
+# --- LLM
+from openai import OpenAI
+from ollama import chat
+
+# Torch / Huggingface
+import torch
+from transformers import DonutProcessor, VisionEncoderDecoderModel
+
+
+SYSTEM_TEMPLATE ="""
+                    **Context:**  
+                    You are an advanced language model specializing in structured data extraction from OCR text. Your task is to extract structured information from a supermarket deal OCR result.  
+                    **Important: Extract exactly one deal. Output a single JSON object with the required four fields.**  
+
+                    **Extraction Fields:**  
+                    - **Marke**: The brand name, if explicitly mentioned.  
+                    - **Produktname**: The product name.
+                    - **Original Preis**: The original price of the product.
+                    - **Reduzierter Preis**: The reduced price of the product.
+                    - **Gewicht**: The weight of the product, if available.
+
+                    **Guidelines:**  
+                    - **Return data strictly in JSON format as a single object.**  
+                    - **Ensure accuracy** by considering spatial context if available.  
+                    - **Use null values** for missing fields.  
+                    - **Filter out irrelevant numbers** (e.g., product weight should not be confused with price).  
+                    - **Fix OCR errors**:  
+                    1. **Price correction**: Identify and fix missing decimals (e.g., `"229"` → `"2.29"`).  
+                    2. **Contextual reasoning**: Infer correct prices using the euro symbol and typical pricing patterns.  
+                    3. **Ignore OCR noise**: Disregard unrelated text like `"Faarconn Galh"` or `"4B6e3Alus"`.  
+                    4. **Correct spelling mistakes**: Use the correct spelling for brands and products.
+
[…]

### 2025-02-18 src/extraction/evaluation/evaluate_ocr.py

@@ -1,5 +1,6 @@
 # General imports
 from collections import defaultdict
+import datetime
 import json
 import os
 import pickle
@@ -13,6 +14,7 @@ from pathlib import Path
 import seaborn as sns
 import pickle
 import jellyfish
+from dotenv import load_dotenv
 
 # --- OCR
 from paddleocr import PaddleOCR
@@ -20,62 +22,9 @@ import pytesseract
 import easyocr
 from doctr.models import ocr_predictor
 
-# --- NLP   
-import spacy
-from spacy.lang.de import stop_words
-from spellchecker import SpellChecker
-
-# --- LLM
-from openai import OpenAI
-from ollama import chat
-
-# Torch / Huggingface
-import torch
-from transformers import DonutProcessor, VisionEncoderDecoderModel, VisionEncoderDecoderConfig
 
 
-# os.system("python -m spacy download de_core_news_md")
-nlp = spacy.load('de_core_news_md')
 
-llm = OpenAI(base_url="http://127.0.0.1:1234/v1", api_key="lm-studio")
-LLM_MODEL = "qwen2.5-7b-instruct-1m@q8_0"  
-
-SYSTEM_TEMPLATE ="""
-                    **Context:**  
-                    You are an advanced language model specializing in structured data extraction from OCR text. Your task is to extract structured information from a supermarket deal OCR result.  
-                    **Important: Extract exactly one deal. Output a single JSON object with the required four fields.**  
-
-                    **Extraction Fields:**  
-                    - **Marke**: The brand name, if explicitly mentioned.  
-                    - **Produktname**: The product name.
-                    - **Original Preis**: The original price of the product.
-                    - **Reduzierter Preis**: The reduced price of the product.
-                    - **Gewicht**: The weight of the product, if available.
-
-                    **Guidelines:**  
-                    - **Return data strictly in JSON format as a single object.**  
-                    - **Ensure accuracy** by considering spatial context if available.  
-                    - **Use null values** for missing fields.  
-                    - **Filter out irrelevant numbers** (e.g., product weight should not be confused with price).  
-                    - **Fix OCR errors**:  
-                    1. **Price correction**: Identify and fix missing decimals (e.g., `"229"` → `"2.29"`).  
[…]

### 2025-02-18 src/extraction/evaluation/evaluate_ocr_llm.py

@@ -1,0 +1,679 @@
+# General imports
+from collections import defaultdict
+import datetime
+import json
+import os
+import pickle
+import re
+import traceback
+import cv2
+import matplotlib.pyplot as plt
+import pandas as pd
+import numpy as np
+from pathlib import Path
+import seaborn as sns
+import pickle
+import jellyfish
+from dotenv import load_dotenv
+
+# --- OCR
+from paddleocr import PaddleOCR
+import pytesseract
+import easyocr
+from doctr.models import ocr_predictor
+
+
+# --- LLM
+from openai import OpenAI
+from ollama import chat
+
+
+SYSTEM_TEMPLATE = """
+**Context:**  
+You are an advanced language model specializing in extracting structured information from OCR text. Your task is to extract one supermarket deal from the given OCR result.
+
+**Extraction Requirements:**  
+- **Fields:**  
+  - "Marke": Brand name (if explicitly mentioned)  
+  - "Produktname": Product name  
+  - "Original Preis": Original price  
+  - "Reduzierter Preis": Reduced price  
+  - "Gewicht": Weight (if available; otherwise, use null)
+
+- **Instructions:**  
+  - Return a single JSON object containing exactly one deal.
+  - Use JSON only—no additional text.
+  - If a field is missing, assign a null value.
+  - Correct OCR errors such as missing decimals (e.g., "229" → "2.29"), incorrect spellings, and OCR noise.
+  - Use contextual cues (e.g. euro symbols) to infer and correct pricing.
+
+**Example:**  
+OCR Input:                     
+Dallmayr Prodomo Kaffee gemahlen 500g 1kg=51.73 Dallmayr -24% prodomo 5 69 UVP7,49  
+
+JSON OUTPUT:
+{
+    "Marke": "Dallmayr",
+    "Produktname": "Prodomo Kaffee gemahlen",
+    "Original Preis": "UVP7,49",
+    "Reduzierter Preis": "3,99 €",
+    "Gewicht": null
+}
+
+IMPORTANT: Return the JSON object in the above format only once.
+"""
+
+
+DTYPES = {
+    "img_name": str,
+    "Marke": str,
+    "Produktname": str,
+    "Original Preis": str,
+    "Reduzierter Preis": str,
+    "Gewicht": str,
+    }
+
+ALIGNMENT_LABELS = {
+    "brand": ["marke", "brand", "hersteller", "manufacturer"],
+    "product_name": ["produktname", "productname", "name", "produkt", "product"],
[…]

### 2025-02-18 src/webapp/main.py

@@ -12,7 +12,9 @@ import uuid
 from tqdm import tqdm
 
 from ultralytics import YOLO
-from pdf2image import convert_from_path
+# from pdf2image import convert_from_path
+import fitz
+
 from PIL import Image, ImageDraw  # Ensure ImageDraw is imported
 from deal_processing import process_image  # import process_image from deal_processing.py
 
@@ -150,7 +152,21 @@ async def upload_pdf(file: UploadFile = File(...)):
         f.write(pdf_contents)
 
     # 2. convert pdf to images
-    pages = convert_from_path(pdf_path)
+    # Pdf2image
+    # pages = convert_from_path(pdf_path)
+
+    # PyMuPDF
+    # zoom_x = 2.0  # horizontal zoom
+    # zoom_y = 2.0  # vertical zoom
+    # mat = pymupdf.Matrix(zoom_x, zoom_y)  # zoom factor 2 in each dimension
+    # pix = page.get_pixmap(matrix=mat)  # use 'mat' instead of the identity matrix
+    pages = []
+    doc = fitz.open(pdf_path)
+    for i in range(doc.page_count):
+        page = doc.load_page(i)
+        pix = page.get_pixmap()
+        img = Image.frombytes("RGB", [pix.width, pix.height], pix.samples)
+        pages.append(img)
     # new unique session_id for this pdf
     session_id = str(uuid.uuid4())
     SEGMENTATION_CACHE[session_id] = []
@@ -280,7 +296,8 @@ async def process_deal(request: Request):
     # Use process_image to extract structured deal info from the cropped image
     # deal_info = process_image(crop_path, model="llama3.2-vision")
     # deal_info = process_image(crop_path, model="llama3.2-vision:11b-instruct-q8_0")
-    deal_info = process_image(crop_path, model="minicpm-v")
+    # deal_info = process_image(crop_path, model="minicpm-v")
+    deal_info = {}
     extracted_info = f"""
     Brand: {deal_info.get("brand", "unknown")}<br>
     Product Name: {deal_info.get("productname", "unknown")}<br>
@@ -310,6 +327,8 @@ def get_preview_data(session_id: str):
         return JSONResponse({"error": "Session not found"}, status_code=404)
     return {"pages": SEGMENTATION_CACHE[session_id]}
 
+# if not os.path.exists("tmp"):
+#     os.makedirs("tmp")
 app.mount("/tmp", StaticFiles(directory="tmp"), name="tmp")
 
 def clear_tmp_folder():

### 2025-02-18 src/extraction/evaluation/evaluate_ocr-llm_donut_lvlm.py
Finalized evaluation.

@@ -88,14 +88,6 @@ ALIGNMENT_LABELS = {
 }
 
 
-# Conduct OCR of different models
-MODELS = {
-    "ppocr_ocr": "PaddleOCR",
-    "easyocr_ocr": "EasyOCR",
-    "tesseract_ocr": "Tesseract",
-    "doctr_ocr": "DocTR",
-    "donut_model": "Donut"
-}
 
 LABELS = {
     "brand": "Brand",
@@ -126,6 +118,49 @@ def df_label_alignment(df, alignment_labels=ALIGNMENT_LABELS):
     print(f"Datframe columns aligned to: {new_colnames}")
     return df
     
+
+def final_normalize_text(text):
+    REPLACEMENTS = {
+        "ä": "a", 
+        "ö": "o", 
+        "ü": "u", 
+        "ß": "ss", 
+        ",": ".", 
+        "€": "", 
+        "–": " ", 
+        "—": " ", 
+        "−": " ", 
+        "ô": "o", 
+        "é": "e", 
+        "ç": "c",
+        "è": "e",
+        "à": "a",
+        "ê": "e",
+        "â": "a",
+        "û": "u",
+        "î": "i",
+        "ë": "e",
+        "ï": "i",
+        "œ": "oe",
+        "æ": "ae",
+        "ù": "u",
+    }
+    for key, value in REPLACEMENTS.items():
+        text = text.replace(key, value)
+    text = "".join([char for char in text if char.isalnum() or char in {".", " "}])
+    text = "".join(text.split())
+    
+    text = text.strip().lower()
+    return text
+
+def final_normalize_prices(price_text):
+    # Replace commas with dots
+    price_text = price_text.replace(",", ".")
+    # Only keep numbers and dots
+    price_text = "".join([char for char in price_text if char.isdigit() or char == "."])
+    
+    return price_text
+
 
 
 # Preprocessing function
@@ -165,7 +200,7 @@ def extract_json(string):
 
 
 def get_images_by_name(root, imgnames):
-    imgnames = list(imgnames)
+    imgnames = [str(Path(name).stem) for name in imgnames]  
     imgpaths = np.ones(len(imgnames), dtype=object)
     for root, dirs, files in os.walk(root):
         for file in files:
@@ -182,118 +217,6 @@ def get_images_by_name(root, imgnames):
             imgpaths[idx] = None
             print("\t\t - "+imgnames[idx])
[…]

### 2025-02-18 src/extraction/evaluation/evaluate_ocr_llm.py

@@ -442,11 +442,7 @@ def visualize_levdistances(levdistances, outname):
 def main(level=1,
         PROJECT_DIR=None, 
          LABELS_PATH=None, 
-         LEAFLET_DIR=None, 
-         DB_PATH=None, 
-         MODELS_DIR=None, 
-         LLM_RESULTS_PATH=None, 
-         DONUT_RESULTS_PATH=None,
+         RESULTS_DIR=None, 
          OCR_RESULTS_PATH=None, 
          LLM_ENGINE=None, 
          LLM_MODELS=None):
@@ -511,13 +507,13 @@ def main(level=1,
     for model_name in LLM_MODELS:
         model_out_name = model_name.replace(":","_")
         outpath = f"llm_results_{model_out_name}.pkl"
-        if not os.path.exists(outpath):
+        if not os.path.exists(os.path.join(RESULTS_DIR, outpath)):
             print(f"Prompting LLM {model_out_name}...")
             llm_responses = llm_prompting(ocr_results_df, LLM_ENGINE, model_name)            
             pickle.dump(llm_responses, open(f"llm_results_{model_out_name}.pkl", "wb"))
         else:
             print(f"Results for LLM {model_out_name} already exist. Loading...")
-            llm_responses = pickle.load(open(outpath, "rb"))
+            llm_responses = pickle.load(open(os.path.join(RESULTS_DIR, outpath), "rb"))
         llm_responses_list.append(llm_responses)
 
 
@@ -584,6 +580,9 @@ def main(level=1,
             print(entity_acc, llmmodel)
             avg_accuracies_per_llm[ocrmodel][llmmodel] = np.mean([np.mean(acc) for acc in entity_acc.values()])
 
+    for ocrmodel, levdistances in levdistances_dict.items():
+        for llmmodel, entity_lev in levdistances.items():
+            avg_levdistances_per_llm[ocrmodel][llmmodel] = np.mean([np.mean(lev) for lev in entity_lev.values()])
 
 
     
@@ -595,21 +594,21 @@ def main(level=1,
             for entity, acc in entity_acc.items():
                 data.append((model, entity, np.mean(acc)))
         
-        df = pd.DataFrame(data, columns=["Model", "Entity", "Accuracy"])
+        df = pd.DataFrame(data, columns=["Model", "LLM", "Accuracy"])
         
         # Create grouped bar plot
         fig, ax = plt.subplots(figsize=(14, 10))
[…]

### 2025-02-19 src/yolo/train.py
Add evaluation scripts for yolo-seg

@@ -1,6 +1,7 @@
 from ultralytics import YOLO
 import yaml
 import os
+import argparse
 
 cur_dir = os.path.dirname(os.path.realpath(__file__))
 
@@ -10,9 +11,16 @@ def load_config(config_path):
         config = yaml.safe_load(f)
     return config
 
+def parse_args():
+    parser = argparse.ArgumentParser(description="Train YOLO model")
+    parser.add_argument(
+        "--config", default=os.path.join(cur_dir, "train_configs.yaml"), type=str
+    )
+    args = parser.parse_args()
+    return args
 
 def train(cfg):
-    model = YOLO(cfg["model_path"])
+    model = YOLO(cfg["model_path"], verbose=False)
     results = model.train(
         data=cfg["data_path"],
         imgsz=cfg["imgsz"],
@@ -41,11 +49,12 @@ def validate(cfg, best_model_path):
 def main(cfg):
     results = train(cfg)
     run_path = results.save_dir
-    best_model_path = os.path.join(run_path, "weights", "best.pt")
-    val_results = validate(cfg, best_model_path)
-    print(val_results)
+    print(f"Results saved to {run_path}")
+    # best_model_path = os.path.join(run_path, "weights", "best.pt")
+    # val_results = validate(cfg, best_model_path)
 
 
 if __name__ == "__main__":
-    cfg = load_config(os.path.join(cur_dir, "train_configs.yaml"))
+    args = parse_args()
+    cfg = load_config(args.config)
     main(cfg)

### 2025-02-20 paper/main_ilyi.tex
Add new plots and worked on paper.

@@
+% !TEX root = main_ilyi.tex
+
 % This must be in the first 5 lines to tell arXiv to use pdfLaTeX, which is strongly recommended.
@@
 % Change to "preprint" to generate a non-anonymous version with page numbers.
-\usepackage[preprint]{coling}
+\usepackage[preprint]{lib}
 
@@
 \section{Introduction}
+
+Automated information extraction from supermarket leaflets poses significant challenges due to the unstructured nature of promotional content, diverse layouts, and varying text-image relationships.
+The ability to accurately extract product names, prices, and discount details is critical for applications such as competitive analysis, dynamic pricing strategies, and digital retail transformation.
+Traditional OCR-based approaches often struggle with these complexities, as they are not well-suited for handling visually complex layouts that integrate both textual and graphical elements.
+Consequently, there is a growing need for advanced methodologies that leverage deep learning and multimodal techniques to improve extraction accuracy and robustness.
+
 \subsection{Motivation}
+
+Retailers distribute promotional leaflets regularly, providing crucial information about product pricing, discounts, and special offers.
+Extracting structured data from these leaflets is essential for a variety of downstream applications, including price monitoring, personalized marketing, and retail analytics.
+However, the nature of these documents presents several challenges.
+Leaflets often feature intricate layouts that combine product images with multiple text regions, making it difficult to separate relevant information from decorative or promotional elements.
+Furthermore, text appears in different font styles, orientations, and colors, increasing the difficulty of standard OCR-based extraction.
+The presence of multilingual content and retail-specific terminologies further complicates the process, as many OCR systems struggle to recognize domain-specific jargon or currency symbols correctly.
+Additionally, supermarket leaflets often contain noisy backgrounds, overlapping elements, and handwritten annotations, all of which contribute to OCR errors.
+Given these challenges, traditional rule-based and template-based methods fall short of delivering reliable results.
+Recent advancements in deep learning, particularly in vision-language models, provide a more adaptable and powerful approach to structured information extraction.
+Large Vision-Language Models (LVLMs) and end-to-end document understanding architectures such as Donut have demonstrated significant potential in tackling these challenges by integrating contextual understanding with visual processing.
+
 \subsection{Problem Statement}
+
+The core problem addressed in this work is the extraction of structured product and pricing information from supermarket leaflets.
+Given an image $I$ containing both textual and visual information, the objective is to extract a structured representation $\mathcal{D}$ that encapsulates relevant entities.
+More formally, this representation can be defined as:
+\begin{equation}
+    \mathcal{D} = \{ (p_i, v_i, c_i) \}_{i=1}^{N},
+\end{equation}
+where $p_i$ represents a product name, $v_i$ denotes its corresponding price, and $c_i$ categorizes the type of promotional offer, such as a direct discount or a multi-buy deal.
+Several challenges make this task particularly difficult.
+First, segmenting and localizing relevant text and graphical regions in a cluttered layout is non-trivial, as different sections of the leaflet may contain multiple, overlapping elements.
+Additionally, associating product names with the correct prices requires context-aware processing, particularly when multiple prices exist for a single product due to variations such as original price, discounted price, and special membership discounts.
+Finally, OCR errors, layout inconsistencies, and missing textual fields introduce additional obstacles, necessitating robust extraction techniques that can generalize across different leaflet designs and promotional structures.
+
+% \subsection{Contributions}
+
+% This work presents a systematic investigation into various information extraction approaches, evaluating both traditional OCR pipelines and state-of-the-art deep learning methods.
+A comparative analysis is conducted between OCR-based systems, OCR-LLM hybrid models, and end-to-end vision-language architectures to assess their effectiveness in extracting structured information from supermarket leaflets.
+To enhance the reliability of extracted text, a normalization pipeline is introduced to correct common OCR errors and standardize output representations.
+Additionally, benchmark evaluations are performed on supermarket leaflet datasets, using models such as Donut and LVLMs to analyze their performance in structured data extraction.
+Beyond the technical contributions, this work also provides an open-source implementation and dataset annotations to facilitate further research in retail document analysis.
+By bridging the gap between conventional OCR techniques and modern deep learning approaches, this study aims to advance the field of automated leaflet analysis and contribute to more accurate and efficient retail information extraction.
+
 \subsection{Contributions}
+
+This work makes the following key contributions:
+\begin{itemize}
+    \item We conduct a systematic evaluation of various information extraction approaches, including traditional OCR pipelines, OCR-LLM hybrid models, and end-to-end deep learning frameworks.
+    \item We introduce a normalization pipeline to improve OCR output consistency, mitigating common recognition errors in promotional leaflets.
+    \item We benchmark state-of-the-art document understanding models such as Donut and LVLMs on supermarket leaflet datasets, analyzing their effectiveness in structured information extraction.
+    \item We provide an open-source implementation and dataset annotations to facilitate future research in retail document analysis.
+\end{itemize}
+These contributions aim to bridge the gap between traditional OCR-based methods and modern deep learning approaches, advancing the field of automated leaflet analysis.
 
@@
 \indent{\textbf{Information Extraction}.}
+
+\section{Nature of Supermarket Leaflet Data}
+Supermarket leaflets constitute a complex and heterogeneous data source, characterized by multimodal content with varying levels of structured and unstructured information.
+This data presents unique challenges in computational processing due to its inherent ambiguities, multi-instance object representation, and spatial dependencies.
+The reader is encouraged to simulanously inspect the visual representation of the specific data-related challenges in \figref{fig:leaflet_data} while reading ahead.
+
+Formally, let $I \in \mathbb{R}^{H \times W \times C}$ denote a supermarket leaflet image, where $H$ and $W$ represent height and width, and $C$ indicates the number of channels.
+The primary goal in leaflet analysis is to extract a structured representation $\mathcal{D} = \{(c_i, p_i, d_i, m_i)\}_{i=1}^{N}$, where each tuple represents category $c_i$, price $p_i$, product description $d_i$, and brand marker $m_i$ for $N$ detected items.
+
+The ambiguity in leaflet data stems from multiple contributing factors.
+First, price recognition is hindered by the existence of multiple price points associated with a single product.
+Given product $P_j$, we define a set of associated prices $P_j = \{ p_{j,1}, p_{j,2}, ..., p_{j,K} \}$, where $K$ denotes the number of distinct price entries, including original prices, discounts, membership-based reductions, and additional incentives (e.g., coupon-based deductions).
+The decision function for selecting the correct price entry can be formulated as:
+\begin{equation}
+    p^*_j = \arg\max_{p \in P_j} \Phi(p, C),
+\end{equation}
+where $\Phi(p, C)$ represents a learned scoring function incorporating context $C$, including proximity to textual cues and visual emphasis features.
+
+Furthermore, the representation of products in supermarket leaflets does not conform to a strict one-to-one mapping between textual and visual elements.
+Some product deals encapsulate multiple distinct items, leading to a one-to-many mapping between product images and extracted textual features.
+Let $X = \{x_i\}_{i=1}^{M}$ represent a set of detected product images and $T = \{t_j\}_{j=1}^{N}$ a set of textual entities; the optimal pairing function $\mathcal{M}: X \to 2^T$ requires the resolution of occlusions, segmentation artifacts, and inconsistent typographic hierarchies.
+
+In the context of visual information extraction, a major challenge arises from the misinterpretation of numerical values due to errors in punctuation extraction.
+Specifically, the process is prone to systematic errors in decimal place recognition due to font-specific artifacts and noisy backgrounds.
+Let $s_t$ denote the OCR-extracted string, where $s_t \sim P(S)$ represents the probability distribution over possible transcriptions.
+A corrective decoding function $\Gamma(s_t)$ can be optimized via:
+\begin{equation}
+    \Gamma(s_t) = \arg\max_{s \in \mathcal{S}} P(s | s_t, \mathcal{C}),
+\end{equation}
+where $\mathcal{S}$ is the space of plausible price values, and $\mathcal{C}$ integrates surrounding contextual information.
+
+Finally, spatial dependencies play a critical role in entity association.
+Traditional object detection methods relying purely on bounding box regression, such as Faster R-CNN \cite{ren2015faster}, may be insufficient due to the lack of explicit spatial reasoning mechanisms.
+Therefore, the incorporation of spatial modeling is essential to ensure accurate entity association and disambiguation.
+
+%Figure Placeholder
+\begin{figure}[ht]
+    \centering
+    \fbox{\parbox[c][3cm][c]{5cm}{\centering Figure Placeholder: Leaflet Data Challenges}}
+    \caption{Visual representation of the challenges in supermarket leaflet data.}
+    \label{fig:leaflet_data}
+\end{figure}
+
+% Alternative formulations leveraging graph-based modeling, where detected entities form nodes in a graph $G = (V, E)$, have demonstrated improved robustness.
+Edges $E$ encode spatial adjacency relationships, and an optimal matching function can be obtained via:
+% \begin{equation}
+%     \mathcal{A}^* = \arg\max_{\mathcal{A} \subseteq E} \sum_{(i,j) \in \mathcal{A}} \Psi(v_i, v_j),
+% \end{equation}
+% where $\Psi(v_i, v_j)$ measures the semantic compatibility of entity pair $(i,j)$.
+The inference of $\mathcal{A}^*$ can be approached using graph neural networks (GNNs) \cite{scarselli2008graph} or optimization techniques such as maximum weight matching.
 
@@
 \begin{itemize}
-    \item \(y_{\text{product\_name}}\): The name of the product.
-    \item \(y_{\text{brand}}\): The brand of the product.
-    \item \(y_{\text{original\_price}}\): The original price of the product.
-    \item \(y_{\text{deal\_price}}\): The deal price of the product.
-    \item \(y_{\text{unit}}\): The unit of the product (e.g., weight, volume).
+    \item \code{\(y_{\text{product\_name}}\)}: The name of the product.
+    \item \code{\(y_{\text{brand}}\)}: The brand of the product.
+    \item \code{\(y_{\text{original\_price}}\)}: The original price of the product.
+    \item \code{\(y_{\text{deal\_price}}\)}: The deal price of the product.
+    \item \code{\(y_{\text{unit}}\)}: The unit of the product (e.g., weight, volume).
 \end{itemize}
@@
 \subsection{Architectural Approaches to Information Extraction}
-- Classical methods: Rule-based, template-based
-- Traditional methods: Dividing into multi-stage
-    - 1. Text detection
-    - 2. Text recognition
-    - 3. Key-value pair extraction
-- OCR + LLM
-- End2End: Vision Encoder Decoder Model
-    - Donut 
-- E2E: LVLM
+Among the various existing architectural approaches to information extraction, several methodologies have been developed to address the inherent complexities in supermarket deal images.
+These methods can be categorized into classical approaches, multi-stage traditional models, hybrid OCR-LLM systems, and end-to-end deep learning frameworks.
+Each paradigm offers distinct advantages, and their applicability depends on computational resources, dataset characteristics, and performance requirements.
+
+\subsection{Traditional Multi-Stage Methods}
+Traditional architectures decompose the problem into sequential sub-tasks and solve these independently through sub-task-specific systems. While these methods have been studied extensively  %ADD REF
+and with high variability in methodology, they are often divided into three main stages: text detection, text recognition, and key-value pair extraction.
+
+\indent{\textbf{Text Detection.}} Text detection is the process of identifying regions in the image that contain textual information.
+Commonly used methods include rule-based systems, as well as mostly small object detection neural networks to detect regions of textural interest by predicting $M$ bounding boxes $\{b_i\}_{i=1}^{M}$.
+
+\indent{\textbf{Text Recognition.}} Each bounding box $b_i$ is used to extract the corresponding region in the image, which is passed to a text recognition model to convert the visual representation into a textual one.
+Since this task is often more complex than it might appear due to decoding errors, there exists a high variety of models that can be used for this task, such as CRNN \cite{shi2016crnn} or transformer-based recognizers.
+Given a set of $M$ bounding boxes $\{b_i\}_{i=1}^{M}$, the goal is to predict the corresponding textual entities $\{t_i\}_{i=1}^{M}$.
+\begin{equation}
+    \{t_i\}_{i=1}^{M} = \arg\max_{\{t_i\}_{i=1}^{M}} P(\{t_i\}_{i=1}^{M} | \{b_i\}_{i=1}^{M}).
+\end{equation}
+
+Text detection and recognition, together with pre-and post-processing steps, is often referred to and standardized as Optical Character Recognition (OCR).
+
+\textbf{Key-Value Pair Extraction:} Finally, extracted text is structured into meaningful entities.
+Named Entity Recognition (NER) models or Graph Neural Networks (GNNs) can be used to learn associations between extracted elements:
+\begin{equation}
+    \mathcal{A}^* = \arg\max_{\mathcal{A} \subseteq E} \sum_{(i,j) \in \mathcal{A}} \Psi(v_i, v_j),
+\end{equation}
+where $E$ represents textual adjacency relationships.
+
+While these types of appraoches are widely used, they inherit a high complexity due to the need for multiple models with each being trained, evaluated, tested and managed independently, which also leads to a higher computational overhead due to input-output transformations between the stages.
+Furthermore, the lack of end-to-end training can lead to suboptimal performance and error propagation, which is often seen when applying these types of models to edge cases or unseen data.
+
+\subsection{Hybrid OCR-LLM Models}
+The rise of large language models (LLMs) has led to the development of hybrid OCR-LLM models that combine the strengths of OCR tools with the linguistic capabilities of LLMs.
+While these appraoches still rely on a more traditional process to convert visually appearing text into a machine-readable form, the LLM is used to enhance the robustness of the OCR output by providing contextual reasoning capabilities.
+
+\begin{equation}
+    \hat{y} = F_\theta (T),
+\end{equation}
+where $T$ is the OCR output and $F_\theta$ is a pretrained, general-purpose LLM that is being prompted with a specific task. 
+%TODO: Add more information about the architecture as well as problems
+
+\subsection{End-to-End Models}
+The
+
+End-to-End (E2E) approaches eliminate pipeline fragmentation by learning a unified mapping $F: I \to \mathcal{D}$. Two major architectures dominate this space:
+
+\textbf{Vision Encoder-Decoder Models:} Models such as Donut \cite{kim2022donut} encode input images via a Vision Transformer (ViT) and generate structured outputs via an autoregressive decoder:
+\begin{equation}
+    P(Y | I) = \prod_{t=1}^{T} P(y_t | I, y_{<t}).
+\end{equation}
+These methods improve robustness by directly training on image-text pairs without explicit OCR supervision.
+
+\textbf{Large Vision-Language Models (LVLMs):} Multimodal transformers such as BLIP \cite{li2022blip} and LLaVA \cite{liu2023llava} leverage joint vision-text embeddings to infer structured outputs.
+Given an image-text embedding $z = f_\theta(I, T)$, task-specific decoding is performed via:
+\begin{equation}
+    \hat{y} = \text{Decoder}(z),
+\end{equation}
+where $\text{Decoder}$ is a domain-adapted transformer head.
+
+E2E models significantly reduce error propagation but require large-scale annotated datasets for effective training.
+Their adoption is growing with advancements in multimodal pretraining strategies and self-supervised learning.
 
 \subsection{Dataset Creation}
-Since there was no dataset to evaluate or train, a custom dataset was created by manually annotating a collection of supermarket deal images.
-The dataset includes images with diverse layouts, fonts, and colors to ensure robustness.
-Each image is annotated with bounding boxes for text regions and corresponding labels for product name, brand, original price, deal price, and unit.
-The dataset is split into training, validation, and test sets to facilitate model development and evaluation.
-% Table \ref{tab:dataset} provides an overview of the custom dataset and Figure \ref{fig:dataset} shows sample images with annotations.
-% TODO: Add table and figure
+Since the availability of German supermarket leaflet data is literally not findable, a custom dataset was created by manually annotating a collection of supermarket deal images.
+The dataset includes images from the most common supermarket chains, each with unique layout, fonts, and colors to, in general, ensure the highest diversity and robustness possible.
+Each image is annotated with a corresponding label file that includes the desired entities as well as the image_id.
+The dataset is split into a training and a validation set for each model to be trained and evaluated on.
+Table \tabref{tab:ie_dataset} provides an overview of the dataset with the sample size for each entity and \figref{fig:ie_dataset_samples} shows some sample images with their annotations.
 
-\subsection{Optical Character Recognition}
-Optical Character Recognition (OCR) is a critical component in the information extraction pipeline.
-Several OCR solutions were evaluated to determine the most suitable one for our task.
-The evaluated OCR tools include Tesseract, EasyOCR, PaddleOCR, and DocTR.
-Each tool was assessed based on its accuracy, speed, and ability to handle diverse fonts and layouts.
+\begin{table}[ht]
+\centering
+\caption{Leaflet-IE Dataset}
+\label{tab:ie_dataset}
+\begin{tabular}{ll}
+\toprule
+Entity           & Sample Size \\
+\midrule
+\code{image\_id}        & 372  \\
+\code{brand}            & 357  \\
+\code{product\_name}    & 370  \\
+\code{original\_price}  & 286  \\
+\code{deal\_price}      & 372  \\
+\code{weight}           & 369  \\
+\bottomrule
+\end{tabular}
+\end{table}
 
-\subsection{Experiments}
-\indent{\textbf{Setup}.}
-The experiments were conducted to compare the performance of different OCR solutions and end-to-end models for information extraction.
-The evaluation metrics include precision, recall, and F1-score for each entity type (product name, brand, original price, deal price, and unit).
-The experiments were performed on the test set of the custom dataset.
+Even though the Leaflet-IE dataset is relatively small, the reader will be able to see that the dataset is sufficient to evaluate the performance of different IE appraoches as well as to train an competitive end-to-end model.
+However, as the reader may notice, the dataset is solely focused on single product deals at this point and explicitly does not include
+
+\begin{figure}[ht]
+\centering
+\fbox{\parbox[c][3cm][c]{5cm}{\centering Figure Placeholder: Sample Annotation}}
+\caption{Sample images with annotations from the custom dataset.}
+\label{fig:ie_dataset_samples}
+\end{figure}
+
+% \subsection{Experiments}
+% - Goal: Find the best appraoch for our use case
+% - Research conducted > comparison on general performance, trends, and similar use cases > Identify candidate approaches > OCR + LLM, Donut, LVLM
+
+% # Implementation Details
+% - Hardware: 1. station with 1x NVIDIA RTX4080, 2. station with 1x NVIDIA GTX1080
+% - Software: PyTorch, HuggingFace Transformers, OpenCV
+
+% \subsubsection{Plain Deal OCR Performance}
+% - End case: Extract values from OCR.
+% - Tesseract, EasyOCR, PaddleOCR, DocTR
+% - Evaluation: 
+%     - Accuracy: can the values be found in the OCR output?
+%     - Ngram Accuracy: Can a ngram of the value be found in the OCR output? (ngrams of [len(value)//2,len(value)-1])
+
+%     - for better comparison, the ocr outputs (preds) were compared 1. raw (as it comes from the ocr), as well as 2. normalized
+%     - Normalization approach: 
+%     ```psuedo code
+%         REPLACEMENTS = {
+%             "ä": "a", 
+%             "ö": "o", 
+%             "ü": "u", 
+%             "ß": "ss", 
+%             ",": ".", 
+%             "€": "", 
+%             "–": " ", 
+%             "—": " ", 
+%             "−": " ", 
+%             "ô": "o", 
+%             "é": "e", 
+%             "ç": "c",
+%             "è": "e",
+%             "à": "a",
+%             "ê": "e",
+%             "â": "a",
+%             "û": "u",
+%             "î": "i",
+%             "ë": "e",
+%             "ï": "i",
+%             "œ": "oe",
+%             "æ": "ae",
+%             "ù": "u",
+%         }
+%         for key, value in REPLACEMENTS.items():
+%             text = text.replace(key, value)
+%         text = "".join([char for char in text if char.isalnum() or char in {".", " "}])
+%         text = "".join(text.split())
+
+%         text = text.strip().lower()
+%         return text
+%     ```
+
+\section{Experiments}
+
+The primary objective of the experiments is to identify the most effective approach for extracting structured information from supermarket leaflets.
+The evaluation considers general performance trends and use cases to determine candidate methodologies, including OCR + LLM, Donut, and LVLM.
+
+\subsection{Implementation Details}
+
+\textbf{Hardware Configuration:} The experiments were conducted on two distinct computational setups:
+\begin{itemize}
+    \item Station 1: NVIDIA RTX 4080 GPU
+    \item Station 2: NVIDIA GTX 1080 GPU
+\end{itemize}
+
+\textbf{Software Stack:} The following libraries and frameworks were utilized:
+\begin{itemize}
+    \item PyTorch
+    \item HuggingFace Transformers
+    \item OpenCV
+\end{itemize}
+
+\subsection{Comparison of Hybrid OCR+LLM, Donut, and LVLM}
+- Comparison of Hybrid OCR+LLM, Donut, and LVLM
+- Evaluation on Leaflet-IE validation subset.
+- Evaluation Metrics: Accuracy, levenshtein distance
+
+- Sections X and Y show prepended studies to determine the best model in a selected candidate pool for OCR and LLM.
 
 \indent{\textbf{Results}.}
-The results of the experiments indicate that the end-to-end models, such as the Vision Encoder Decoder Model (e.g., Donut) and Large Vision-Language Models (LVLM), outperform traditional OCR-based methods in terms of accuracy and robustness.
-The OCR + LLM approach also shows promising results, particularly in handling OCR errors and extracting key-value pairs.
+TODO
 
-\subsection{Evaluation}
-The evaluation of the models was conducted using standard metrics, including precision, recall, and F1-score.
-The comparison between LVLM, OCR + LLM, and Donut models highlights the strengths and weaknesses of each approach.
-The results demonstrate that end-to-end models provide superior performance in extracting structured information from supermarket deal images.
+% SUB-STUDIES
+\subsection{Plain Deal OCR Performance}
+
+The baseline experiment focuses on the effectiveness of OCR models in extracting values directly from the document images.
+
+\textbf{Models Evaluated:}
+\begin{itemize}
+    \item Tesseract
+    \item EasyOCR
+    \item PaddleOCR
+    \item DocTR
+\end{itemize}
+
+- Data: All 372 samples of the Leaflet-IE dataset were used for evaluation since all OCR models probably have not seen the data before.
+
+\textbf{Evaluation Metrics:}
+\begin{itemize}
+    \item \textbf{Accuracy}: Measures whether the expected value is present in the OCR output.
+    \item \textbf{N-gram Accuracy}: Determines if an n-gram substring of the expected value exists in the OCR output, computed for $n \in \left[\frac{|v|}{2}, |v| - 1\right]$, where $|v|$ represents the string length.
+\end{itemize}
+
+To improve comparability, OCR outputs were evaluated in different levels of normalization.
+# Preprocessing function
+% def normalize_text(text, level=6):
+%     if not text or pd.isnull(text) or text == "":
+%         return ""
+
+%     # Level 1: Basic cleaning (handles empty values)
+%     if level >= 1:
+%         text = str(text).strip()
+
+%     # Level 2: Lowercasing & basic replacements (whitespace, German characters)
+%     if level >= 2:
+%         text = text.lower()
+%         text = text.replace("\n", " ").replace("\t", " ").replace("\r", " ")
+%         text = text.replace("ö", "o").replace("ä", "a").replace("ü", "u").replace("ß", "ss")
+
+%     # Level 3: Extended normalization (remove special characters, normalize hyphens)
+%     if level >= 3:
+%         text = text.replace("-", " ").replace("–", " ").replace("—", " ").replace("−", " ")
+%         text = "".join([char for char in text if char.isalnum() or char in {".", " "}])
+%         text = " ".join(text.split())  # Remove extra spaces
+
+%     if level >= 4:
+%         text = text.replace(" ", "")
+%         text = text.replace(".", "")
+%     return text
+% TODO: In appendix
+% TODO: Continue
+
+\indent{\textbf{Results}.}
+TODO
+
+The performance comparison across different OCR models is visualized in Figure \ref{fig:ocr_results}, where each system's accuracy is evaluated across different deal structures.
+The raw and normalized outputs provide insights into the robustness of each approach in handling textual inconsistencies.
+\begin{figure}[h]
+    \centering
+    % \includegraphics[width=0.8\linewidth]{ocr_performance_plot.pdf}
+    \fbox{\parbox[c][5cm][c]{8cm}{\centering Figure Placeholder: OCR Model Performance}}
+    \caption{OCR Model Performance on Plain Deal Text Extraction}
+    \label{fig:ocr_results}
+\end{figure}
+
+\subsubsection{OCR + LLM Performance}
+Experiment Question: 
+-Which LLM is best suited to work with OCR outputs?
+-Which LLM + OCR combination works best in IE?
+
+Data:
+- All 372 samples of the Leaflet-IE dataset were used for evaluation since all OCR models as well as the LLMs probably have not seen the data before.
+
+The LLM is tasked via a prompt to extract the entities from the OCR output. 
+%TODO: Prompt in appendix
+
+Models Evaluated:
+-    "llama3.1_8b": "Llama 3.1 [8b, Q4]",
+-    "qwen2.5_1.5b-instruct-q8_0": "Qwen 2.5 [1.5b, Q8]",
+-    "llama3.2_3b-instruct-q8_0": "Llama 3.2 [3b, Q8]",
+-    "qwen2.5_7b": "Qwen 2.5 [7b, Q4]"
+
+Evaluation Metrics:
+- For each OCR: Per Entity accuracy and levenshtein distance between predictio
+
+Normalization:
+The reader might get confused with the normalization of the OCR experiment.
+Here, the decision was made to keep the OCR results as they are, as normalization may remove valuable information.
+In addition, the LLMs are considered to deal with such inconsistencies and errors as input.
+
+Here, to improve comparability, The entity values for the comparison between the LLM prediction and the ground truth value were compared in raw form as well as with a normalization prepended.
+The normalization function used is as follows:
+. The normalization procedure applied character replacements and filtering based on linguistic artifacts commonly encountered in OCR errors.
+
+% \textbf{Normalization Procedure:}
+
+% \begin{lstlisting}[language=Python, caption=Text Normalization Procedure]
+% REPLACEMENTS = {
+%     "ä": "a", "ö": "o", "ü": "u", "ß": "ss", ",": ".", "€": "",
+%     "–": " ", "—": " ", "−": " ", "ô": "o", "é": "e", "ç": "c",
+%     "è": "e", "à": "a", "ê": "e", "â": "a", "û": "u", "î": "i",
+%     "ë": "e", "ï": "i", "œ": "oe", "æ": "ae", "ù": "u"
+% }
+% def normalize(text):
+%     for key, value in REPLACEMENTS.items():
+%         text = text.replace(key, value)
+%     text = "".join([char for char in text if char.isalnum() or char in {".", " "}])
+%     text = "".join(text.split())
+%     return text.strip().lower()
+% \end{lstlisting}
+% TODO -> In appendix
+% TODO: Continue
+
+\indent{\textbf{Results}.}
+% TODO: Add results
+
+\subsection{Donut Fine-Tuning Performance}
+Experiment Question:
+- Is it possible to train a Vision Encoder Decoder model to extract end2end information from supermarket leaflet deal images?
 
 \section{Application}
+
 \subsection{Database}
-
-\subsection{Optical Character Recognition}
-
-    \subsection{Experiments}
-    \indent{\textbf{Setup}.}
-    - Common OCR solutions: Tesseract, EasyOCR, PaddleOCR, DocTR
-    - Goal: Which OCR solution is the best for our task?
-    -
 

### 2025-02-20 src/extraction/evaluation/evaluate_ocr_llm.py

@@ -507,13 +507,15 @@ def main(level=1,
     for model_name in LLM_MODELS:
         model_out_name = model_name.replace(":","_")
         outpath = f"llm_results_{model_out_name}.pkl"
-        if not os.path.exists(os.path.join(RESULTS_DIR, outpath)):
+        # outpath = os.path.join(RESULTS_DIR, f"llm_results_{model_out_name}.pkl")
+        if not os.path.exists(outpath):
             print(f"Prompting LLM {model_out_name}...")
             llm_responses = llm_prompting(ocr_results_df, LLM_ENGINE, model_name)            
             pickle.dump(llm_responses, open(f"llm_results_{model_out_name}.pkl", "wb"))
         else:
             print(f"Results for LLM {model_out_name} already exist. Loading...")
-            llm_responses = pickle.load(open(os.path.join(RESULTS_DIR, outpath), "rb"))
+            llm_responses = pickle.load(open(outpath, "rb"))
+
         llm_responses_list.append(llm_responses)
 
 
@@ -577,7 +579,6 @@ def main(level=1,
     avg_levdistances_per_llm = defaultdict(lambda: defaultdict(list))
     for ocrmodel, accuracies in accuracies_dict.items():
         for llmmodel, entity_acc in accuracies.items():
-            print(entity_acc, llmmodel)
             avg_accuracies_per_llm[ocrmodel][llmmodel] = np.mean([np.mean(acc) for acc in entity_acc.values()])
 
     for ocrmodel, levdistances in levdistances_dict.items():
@@ -649,7 +650,7 @@ def main(level=1,
         plt.tight_layout()
         plt.savefig(f"{outname}.png", dpi=400, bbox_inches="tight")
 
-    
+    print("Visualizing...")
     visualize_avg_accuracies(avg_accuracies_per_llm, outname=f"./plots/avg_accuracies")
     visualize_avg_levdistances(avg_levdistances_per_llm, outname=f"./plots/avg_levdistances")
     
@@ -663,7 +664,7 @@ if __name__ == "__main__":
     args = {
         "PROJECT_DIR": PROJECT_DIR,
         "RESULTS_DIR": RESULTS_DIR,
-        "LABELS_PATH": os.path.join(RESULTS_DIR, "val_deals.csv"),
+        "LABELS_PATH": os.path.join(RESULTS_DIR, "labeled_deals_all_imgpath.csv"),
 
[…]

### 2025-02-21 paper/main_ilyi.tex
Add recent changes to paper.

--- 2025-02-18 paper/main_ilyi.tex
@@
-% This must be in the first 5 lines to tell arXiv to use pdfLaTeX, which is strongly recommended.
+% !TEX root = main_ilyi.tex
+
+% for pdfLaTeX
 \pdfoutput=1
-% In particular, the hyperref package requires pdfLaTeX in order to break URLs across lines.
 
@@
 % Change to "preprint" to generate a non-anonymous version with page numbers.
-\usepackage[preprint]{coling}
+\usepackage{lib}
 
@@
 \usepackage[T1]{fontenc}
-% For Vietnamese characters
-% \usepackage[T5]{fontenc}
-% See https://www.latex-project.org/help/documentation/encguide.pdf for other character sets
 
@@
 
-% This is not strictly necessary, and may be commented out,
-% but it will improve the layout of the manuscript,
-% and will typically save some space.
 \usepackage{microtype}
 
-% This is also not strictly necessary, and may be commented out.
-% However, it will improve the aesthetics of text in
-% the typewriter font.
 \usepackage{inconsolata}
 
-%Including images in your LaTeX document requires adding
-%additional package(s)
 \usepackage{graphicx}
@@
 
-\author{Xincheng Liao\textsuperscript{}, Junwen Duan\textsuperscript{}\thanks{\ \ Corresponding author.
-Email: \href{mailto:jwduan@csu.edu.cn}{jwduan@csu.edu.cn}}, Yixi Huang\textsuperscript{}, Jianxin Wang\textsuperscript{} \\
-Hunan Provincial Key Lab on Bioinformatics, School of Computer Science and Engineering, \\
-Central South University, Changsha, Hunan, China \\
-\texttt{\{ostars, jwduan, yx.huang\}@csu.edu.cn, jxwang@mail.csu.edu.cn} \\
-\href{https://github.com/OStars/RUIE}{https://github.com/OStars/RUIE}
+\author{Ilyesse Hettenbach\textsuperscript{}, Gabriel Schurr\textsuperscript{} \\
+HKA, Karlsruhe, Germany \\
+\texttt{\{heil1012, scga1011\}@h-ka.de} \\
+\href{https://github.com/ilyii/leaflets}{https://github.com/ilyii/leaflets}
 }
@@
 \section{Introduction}
+
 \subsection{Motivation}
+If one thinks of a paper-heavy country, Germany is likely to come to mind.
+The country's affinity for printed materials is deeply ingrained in its culture, with activities such as browsing through supermarket leaflets serving as a familiar ritual for many individuals.
+These leaflets have long been an essential medium for consumers to plan their purchases, discover special offers, and compare prices.
+The tactile nature of printed leaflets, the excitement of spotting discounts, and the satisfaction of making a well-informed shopping decision contribute to their enduring appeal.
+However, the rapid advancement of digital technology is transforming consumer behavior.
+While some individuals still find browsing through physical leaflets a nostalgic and even relaxing experience, younger generations are increasingly turning to digital alternatives for their shopping needs.
+The modern shopper expects convenience, efficiency, and instant access to information, yet the digital transformation of supermarket leaflets lags significantly behind other aspects of e-commerce and retail technology.
+
+Despite the existence of applications that compile digital versions of these leaflets, their usability and overall quality remain suboptimal.
+Many digital leaflets are plain documents, failing to leverage the full potential of interactivity, searchability, and intelligent recommendation systems.
+There is a pressing need for sophisticated digital solutions that not only present supermarket deals but also enable consumers to interact with them in a meaningful way.
+
+Possibly, one can imagine a seamless digital platform where users can search for specific items across multiple supermarket chains, apply dietary filters to instantly highlight suitable products, or receive personalized recommendations based on past preferences.
+A tool that allows consumers to create a dynamic shopping list, track price trends over time, and receive real-time updates on the best deals would revolutionize the way people approach grocery shopping.
+Yet, these features remain largely absent from existing digital leaflet solutions.
+Furthermore, while price comparison websites and applications have become commonplace for electronics, fashion, and travel, the grocery sector remains an overlooked frontier.
+Consumers are often left navigating multiple supermarket websites or manually cross-referencing prices to find the best deals—a tedious and inefficient process.
+A comprehensive digital ecosystem that integrates grocery price comparisons, personalized discounts, and AI-driven shopping assistants could bridge this gap and act as a workaround, offering an enhanced, data-driven shopping experience tailored to individual needs.
+
+The future of supermarket deal discovery should not be a static PDF or an unorganized collection of scanned pages—it should be a dynamic, interactive, and intelligent experience that aligns with the evolving digital landscape.
+
 \subsection{Problem Statement}
+The primary objective of this research is to develop an intelligent system for extracting, structuring, and utilizing information from supermarket leaflets in a digital format.
+Given a set of supermarket leaflets \(\mathcal{L} = \{L_1, L_2, ..., L_n\}\), each containing a collection of product deals with specific attributes such as product name, brand, price, discount, product image and other product specifications, the goal is to extract and normalize these attributes to enable efficient querying and comparison across multiple supermarket chains.
+
+Each leaflet \( L_i \) consists of a set of $m$ product entries \( P_i = \{p_1, p_2, ..., p_m\} \), where each product \( p_j \) is associated with a set of varying attributes:
+
+\begin{equation}
+    p_j = \{a_1, a_2, ..., a_k\},   
+\end{equation}
+where each attribute \( a_k \) represents a specific entity. Common attributes include:
+\begin{itemize}
+    \item Product Name
+    \item Brand
+    \item Original Price
+    \item Deal Price
+    \item Unit (e.g., weight, volume)
+    \item Product Image
+\end{itemize}
+among others. Each attribute may or may not be present in a given product entry, and the format and layout of these attributes can vary significantly across different leaflets.
+
+To enable advanced applications such as the abovementioned, one has to tackle different challenges, such as:
+% Nummerierung der Challenges
+\begin{enumerate}
+    \item Detecting and separating deals $p$ from the leaflet $L$.
+    \item Extracting structured information from the detected deals.
+    \item Normalizing the extracted information to ensure consistency and comparability.
+    \item Validating the extracted information to ensure accuracy.
+\end{enumerate}
+
+Therefore, a function $$f: \mathcal{L} \to \mathcal{D}$$ has to be designed, where $\mathcal{D}$ represents the structured information extracted from the leaflets.
+The function $f$ should minimize the extraction error $E$.
+
 \subsection{Contributions}  
+This work presents a comprehensive approach to digitalizing and structuring supermarket leaflet information by leveraging advanced computer vision, OCR, and language models.
+The key contributions of this research are as follows:
+
+% 1. **Development of a Detection and Extraction Pipeline for Supermarket Leaflets**  
+\indent{\textbf{Development of a Detection and Extraction Pipeline for Supermarket Leaflets.}} We propose a modular and efficient pipeline for detecting, extracting, and structuring information from supermarket leaflets.
+This pipeline integrates OCR-based text extraction, image processing, and layout understanding to accurately associate textual and visual elements such as product names, prices, descriptions, and images.
+Additionally, we incorporate normalization techniques to standardize extracted data across different retailers and formats.
+
+% 2. **Design of an Interactive Application for Deal Browsing and Price Comparison**  
+\indent{\textbf{Design of an Interactive Application for Deal Browsing and Price Comparison.}} To facilitate practical use, we wrap the extracted data into a user-friendly application that enables consumers to browse, filter, and compare deals across multiple supermarket chains.
+This application includes basic functionalities to search, track and compare deals across different supermarket chains.
+
+% 3. **Comprehensive Evaluation of Information Extraction Models**  
+\indent{\textbf{Comprehensive Evaluation of Information Extraction Models.}} We systematically evaluate multiple state-of-the-art models for supermarket leaflet information extraction, including hybrid OCR+LLM approaches, end-to-end Vision-Language Models (VLMs), and Large Vision-Language Models (LVLMs).
+Our evaluation covers accuracy metrics such as per-entity correctness, Levenshtein distance, and robustness across different supermarket layouts and textual formats.
+This analysis provides insights into the trade-offs between computational efficiency and extraction performance.
+
+% 4. **Training of Custom Deal Detection and Information Extraction Models**  
+\indent{\textbf{Training of Custom Deal Detection and Information Extraction Models.}} To further improve extraction performance, we develop and fine-tune specialized models for deal detection and information extraction.
+This includes training custom object detection models to identify product regions within leaflets, as well as domain-specific sequence-to-sequence models for structured text extraction.
+These models are designed to enhance recognition accuracy, particularly for complex layouts and noisy scan conditions.
+
+% 5. **Creation of a Benchmark Dataset: Leaflet-IE**  
+\indent{\textbf{Creation of a Benchmark Dataset: Leaflet-IE.}} We introduce **Leaflet-IE**, a novel dataset curated for supermarket leaflet information extraction.
+The dataset consists of annotated images spanning multiple supermarket chains, with labeled entities including product names, prices, discounts, brands, and categories.
+This dataset serves as a benchmark for future research in structured information extraction from promotional materials and contributes to advancing OCR and multimodal learning for real-world retail applications.
 
@@
 
+\section{Nature of Supermarket Leaflet Data}
+Supermarket leaflets constitute a complex and heterogeneous data source, characterized by multimodal content that combines structured and unstructured information.
+This data presents unique challenges for computational processing due to its inherent ambiguities, multi-instance object representations, and spatial dependencies.
+The reader is encouraged to simultaneously inspect the visual representation of these challenges in \figref{fig:leaflet_data} while proceeding with the discussion.
+
+One of the primary challenges lies in the ambiguity of price recognition, where a single product may be associated with multiple price points, such as discounted prices, bulk purchase offers, or tiered pricing structures.
+This ambiguity is further exacerbated by errors in punctuation extraction, particularly in recognizing decimal places, which often arise from font-specific artifacts or noisy backgrounds.
+Resolving such issues requires advanced plausibility checks, contextual reasoning, and robust numerical interpretation mechanisms to ensure accurate data extraction.
+Additionally, the non-strict one-to-one mapping between textual and visual elements introduces further complexity.
+For instance, a single product image may represent multiple items, or textual descriptions may not align precisely with their corresponding visual representations.
+This misalignment necessitates sophisticated multimodal fusion techniques to bridge the gap between visual and textual data, ensuring accurate association and interpretation of product information.
+
+The inconsistent layouts of supermarket leaflets further complicate data extraction.
+Promotional deals and product information are often placed in varying positions across different leaflets, making it difficult to design a universal extraction method that generalizes across diverse formats.
+Text elements frequently overlap with product images or other textual information, leading to misidentification or incorrect parsing of data.
+These challenges are compounded by the variability in fonts, sizes, and weights used within a single leaflet, which complicates the differentiation between product names, prices, and promotional tags.
+The presence of multilingual content and special characters adds another layer of complexity, as leaflets may contain text in multiple languages or stylized symbols that require optical character recognition (OCR) and natural language processing (NLP) models capable of handling diverse linguistic structures and alphabet systems.
+
+Promotion labels and discount representations introduce additional challenges due to their non-standard or highly stylized text formats.
+Identifying the exact nature of promotions, such as "Buy 1, get 1 free" or "20\% off," requires precise extraction and interpretation, particularly when the text is embedded in noisy backgrounds or overlaps with other elements.
+Furthermore, the temporal context of deals and promotions adds a critical dimension to the extraction process.
+Some offers may only be valid for specific periods, and extracting and associating the correct date ranges with these offers can be challenging, especially when the information is not explicitly stated or is presented in ambiguous formats.
+
+Therefore, the nature of supermarket leaflet data necessitates an advanced toolkit of visual and textual processing, analysis, extraction and generation techniques to effectively interpret and utilize the information contained within these documents.
+The subsequent sections will delve into the methodologies and models used to address these challenges and extract structured information from supermarket leaflets.
+
 \section{Deal Detection}
@@
 \section{Information Extraction of Supermarket Deals}
-    % - Subsequent to detection and separation of deals, the goal is to extract useful information from it.
-    % - Difficulties
-    %     - High variety of layouts, colors, fonts, sizes
-    %         - Deal sometimes have superscripted decimals and no separation dot.
-    %         - Original prices are sometimes striked through.
-    %         - Deal prices are sometimes in a very different font to the ones it was trained on.
-    %         - Overlapping elements
-    %     - Multimodal information
-    %         - Product image: visual
-    %         - Text: alphabetical + numerical
-    %     - OCR errors
-    %     - Eigennamen (mostly brand names)
-    %     - German language
-    % - Goal: Extract 
-    %     - Product name
-    %     - brand
-    %     - original price
-    %     - deal price
-    %     - unit
 Subsequently to the detection and separation of supermarket deals, the overarching goal of using these in applications requires the extraction of the various useful information from these deals. 
@@
 \subsection{Architectural Approaches to Information Extraction}
-- Classical methods: Rule-based, template-based
-- Traditional methods: Dividing into multi-stage
-    - 1. Text detection
-    - 2. Text recognition
-    - 3. Key-value pair extraction
-- OCR + LLM
-- End2End: Vision Encoder Decoder Model
-    - Donut 
-- E2E: LVLM
+Among the various existing architectural approaches to information extraction, several methodologies have been developed to address the inherent complexities in supermarket deal images.
+These methods can be categorized into classical approaches, multi-stage traditional models, hybrid OCR-LLM systems, and end-to-end deep learning frameworks.
+Each paradigm offers distinct advantages, and their applicability depends on computational resources, dataset characteristics, and performance requirements.
+
+\subsubsection{Traditional and Hybrid Approaches for Supermarket Leaflet Information Extraction}  
+Information extraction from supermarket leaflets has traditionally been approached through a pipeline of sequential sub-tasks, each addressed by specialized systems.
+These methods, while extensively studied and methodologically diverse, are typically divided into three main stages: text detection, text recognition, and key-value pair extraction.
+Although effective in certain scenarios, these approaches suffer from inherent limitations, including computational overhead, error propagation, and suboptimal performance on edge cases.
+Recent advancements in large language models (LLMs) have led to the development of hybrid OCR-LLM architectures, which combine the precision of optical character recognition (OCR) with the contextual reasoning capabilities of LLMs.
+Below, we formalize these approaches and discuss their strengths and limitations.
+
+Traditional architectures decompose the problem into independent sub-tasks, each handled by specialized models.
+While this modularity allows for targeted optimization, it introduces complexity and inefficiencies due to the lack of end-to-end training and error propagation across stages.
+
+The first stage, \emph{text detection}, involves identifying regions in the image \( I \in \mathbb{R}^{H \times W \times 3} \) that contain textual information.
+This is typically achieved using rule-based systems or neural networks designed for small object detection.
+The output is a set of \( M \) bounding boxes \( \{b_i\}_{i=1}^{M} \), where each \( b_i = (x_{\text{min}}, y_{\text{min}}, x_{\text{max}}, y_{\text{max}}}) \) defines the coordinates of a text region.
+Modern approaches often employ convolutional neural networks (CNNs) or transformer-based architectures to improve robustness to varying fonts, orientations, and overlapping text.
+
+Each detected bounding box \( b_i \) is cropped and processed by a \emph{text recognition} model to convert the visual representation into a textual one.
+This task is challenging due to decoding errors caused by noisy backgrounds, stylized fonts, and ambiguous characters.
+Commonly used models include convolutional recurrent neural networks (CRNNs) \cite{shi2016crnn} and transformer-based recognizers.
+Given the set of bounding boxes \( \{b_i\}_{i=1}^{M} \), the goal is to predict the corresponding textual entities \( \{t_i\}_{i=1}^{M} \):
+\[
+\{t_i\}_{i=1}^{M} = \arg\max_{\{t_i\}_{i=1}^{M}} P(\{t_i\}_{i=1}^{M} | \{b_i\}_{i=1}^{M}).
+\]  
+The text recognition stage is often optimized using connectionist temporal classification (CTC) loss or sequence-to-sequence objectives, depending on the model architecture.
+
+The final stage structures the extracted text into meaningful entities, such as product names, prices, and promotional tags.
+Named entity recognition (NER) models or graph neural networks (GNNs) are commonly used to learn associations between textual elements.
+The objective is to maximize the alignment score \( \Psi(v_i, v_j) \) between related entities:
+\[
+\mathcal{A}^* = \arg\max_{\mathcal{A} \subseteq E} \sum_{(i,j) \in \mathcal{A}} \Psi(v_i, v_j),
+\]  
+where \( E \) represents textual adjacency relationships. This stage is critical for resolving ambiguities, such as associating prices with the correct products.
+
+While traditional pipelines are widely used, they suffer from several limitations.
+The need for multiple independently trained models increases computational overhead and complicates system management.
+Additionally, the lack of end-to-end training often leads to suboptimal performance, particularly on edge cases or unseen data, as errors propagate through the pipeline.
+
+The rise of large language models (LLMs) has enabled the development of hybrid OCR-LLM architectures, which combine the strengths of OCR tools with the linguistic and reasoning capabilities of LLMs.
+These approaches retain the traditional OCR pipeline for converting visual text into machine-readable form but leverage LLMs to enhance robustness through contextual reasoning and structured output generation.
+
+In a hybrid OCR-LLM system, the OCR stage processes the input image \( I \) to produce a set of unstructured text fragments \( T = \{t_i\}_{i=1}^{M} \) with associated spatial coordinates.
+These fragments are serialized into a prompt \( \mathbf{P} \) and fed into a pretrained LLM \( F_\theta \), which performs contextual parsing and generates structured output \( \hat{y} \):
+\[
+\hat{y} = F_\theta (T).
+\]  
+The LLM leverages its pretrained knowledge to resolve ambiguities, infer relationships between text fragments, and generate outputs in a structured format (e.g., JSON).
+For example, it can distinguish between bulk pricing (e.g., "2 for \$4") and unit pricing (e.g., "\$2 each") through arithmetic reasoning embedded in its attention mechanisms.
+
+Hybrid OCR-LLM models offer several advantages over traditional pipelines.
+By integrating contextual reasoning, they reduce error propagation and improve robustness to noisy or ambiguous inputs.
+Additionally, the use of pretrained LLMs eliminates the need for task-specific training, simplifying system development.
+However, these models still rely on the accuracy of the OCR stage, and misrecognitions (e.g., "O" vs.
+"0") can propagate to the LLM.
+Furthermore, the computational cost of LLM inference can be prohibitive for large-scale applications.
+
+\subsubsection{End-to-End Models}
+End-to-End (E2E) approaches eliminate pipeline fragmentation by learning a unified mapping $F: I \to \mathcal{D}$.
+
+\indent{\textbf{Vision-Encoder-Decoder Models.}} These models represent a paradigm shift in document understanding by unifying text detection, recognition, and semantic parsing into a single end-to-end trainable framework.
+Among these, the Donut architecture \cite{kim2022donut} has emerged as a state-of-the-art model for tasks such as information extraction from supermarket leaflets.
+Donut eliminates the need for intermediate OCR steps by directly mapping input images to structured outputs, leveraging a transformer-based encoder-decoder architecture.
+Below, we formalize the Donut model, its mathematical foundations, and its application to supermarket leaflet data.
+
+Donut consists of two primary components: a vision encoder and a text decoder, both built on transformer layers.
+Given an input image \( I \in \mathbb{R}^{H \times W \times 3} \), the model generates a structured output \( \mathbf{Y} \) in an autoregressive manner.
+The encoder extracts high-level visual features, while the decoder translates these features into a sequence of tokens representing the desired output format.
+
+The \emph{vision encoder} processes the input image \( I \) into a sequence of visual embeddings \( \mathbf{Z} = \{z_i\}_{i=1}^{L} \), where \( L \) is the sequence length.
+This is achieved using a Swin Transformer \cite{liu2021swin}, which partitions the image into non-overlapping patches and applies hierarchical self-attention to capture both local and global context.
+Let \( \mathbf{X} \in \mathbb{R}^{N \times (P^2 \cdot C)} \) denote the patch embeddings, where \( N \) is the number of patches, \( P \) is the patch size, and \( C \) is the number of input channels.
+The Swin Transformer computes multi-head self-attention (MSA) and feed-forward network (FFN) operations as follows:
+\[
+\mathbf{X}' = \text{MSA}(\text{LayerNorm}(\mathbf{X})) + \mathbf{X},  
+\]  
+\[
+\mathbf{Z} = \text{FFN}(\text{LayerNorm}(\mathbf{X}')) + \mathbf{X}',
+\]  
+where LayerNorm denotes layer normalization. The output \( \mathbf{Z} \) serves as the visual representation for the decoder.
+
+The \emph{text decoder} is a transformer-based autoregressive model that generates the output sequence \( \mathbf{Y} = (y_1, y_2, \dots, y_T) \) conditioned on the visual embeddings \( \mathbf{Z} \).
+At each time step \( t \), the decoder predicts the next token \( y_t \) based on the previously generated tokens \( y_{<t} \) and the encoder output \( \mathbf{Z} \).
+The decoder computes self-attention over the output sequence and cross-attention over the visual embeddings:
+\[
+\mathbf{Q} = \mathbf{W}_Q \mathbf{H}_{t-1}, \quad \mathbf{K} = \mathbf{W}_K \mathbf{Z}, \quad \mathbf{V} = \mathbf{W}_V \mathbf{Z},
+\]  
+\[
+\text{Cross-Attention}(\mathbf{Q}, \mathbf{K}, \mathbf{V}) = \text{softmax}\left(\frac{\mathbf{Q} \mathbf{K}^\top}{\sqrt{d_k}}\right) \mathbf{V},
+\]  
+where \( \mathbf{H}_{t-1} \) is the hidden state at step \( t-1 \), and \( \mathbf{W}_Q, \mathbf{W}_K, \mathbf{W}_V \) are learnable projection matrices.
+The final token probabilities are computed as:
+\[
+P(y_t | y_{<t}, \mathbf{Z}) = \text{softmax}(\mathbf{W}_o \mathbf{H}_t),
+\]  
+where \( \mathbf{W}_o \) is an output projection matrix. The model is trained end-to-end using a cross-entropy loss:  
+\[
+\mathcal{L} = -\sum_{t=1}^T \log P(y_t^* | y_{<t}, \mathbf{Z}),
+\]  
+where \( y_t^* \) is the ground-truth token at step \( t \).
+
+Donut is particularly well-suited for supermarket leaflet data due to its ability to handle multimodal inputs and generate structured outputs without intermediate OCR steps.
+The model can directly process leaflet images and produce JSON representations of product information.
+By eliminating the need for OCR, it avoids error propagation and simplifies the pipeline.
+Its end-to-end trainability ensures optimal performance, and its ability to generate structured outputs reduces the need for post-processing.
+However, Donut requires large-scale pretraining on diverse document datasets, which can be computationally expensive.
+Additionally, its performance on low-resolution or highly noisy images may be suboptimal, as the vision encoder relies on high-quality visual features.
+
+\indent\textbf{Large Vision-Language Models.} Large Vision-Language Models (LVLMs) represent the latest advancement in multimodal learning, combining the strengths of LLMs and vision encoders to achieve state-of-the-art performance on a wide range of tasks.
+These models, such as CLIP \cite{radford2021clip} and ALIGN \cite{li2022align}, leverage large-scale pretraining on diverse multimodal datasets to learn robust representations of visual and textual information.
+Below, we formalize the ALIGN model and discuss its application to supermarket leaflet data.
+
+\section{Large Vision-Language Models for Supermarket Leaflet Understanding}  
+Large Vision-Language Models (LVLMs) represent a transformative advancement in multimodal artificial intelligence, unifying visual perception and linguistic reasoning within a single cohesive framework.
+These models, such as LLaVA \cite{liu2023llava} and GPT-4V \cite{openai2023gpt4}, eliminate the traditional separation between vision and language processing by jointly encoding images and text into a shared latent space.
+For supermarket leaflet analysis, LVLMs enable end-to-end extraction of structured information directly from raw images, bypassing explicit OCR stages while leveraging contextual synergies between visual and textual data.
+We formalize the architectural principles, mathematical foundations, and application-specific adaptations of LVLMs below.
+
+---
+
+### **Architecture and Mathematical Formulation**  
+LVLMs integrate a vision encoder, a language model, and cross-modal fusion mechanisms into a unified architecture.
+Given an input leaflet image \( I \in \mathbb{R}^{H \times W \times 3} \), the model generates structured textual output \( \mathbf{Y} \) through joint reasoning over visual and linguistic features.
+
+#### **Vision Encoder**  
+The vision encoder processes \( I \) into a sequence of patch embeddings \( \mathbf{Z} \in \mathbb{R}^{L \times d_v} \), where \( L \) is the number of patches and \( d_v \) is the embedding dimension.
+A Vision Transformer (ViT) \cite{dosovitskiy2020vit} is commonly employed, partitioning \( I \) into \( N \) non-overlapping patches \( \{\mathbf{p}_i\}_{i=1}^N \), linearly projecting each patch, and applying transformer layers with self-attention:
+\[
+\mathbf{z}_i = \text{MSA}(\mathbf{p}_i) + \mathbf{p}_i, \quad \mathbf{Z} = [\mathbf{z}_1; \mathbf{z}_2; \dots; \mathbf{z}_N],
+\]  
+where MSA denotes multi-head self-attention. For supermarket leaflets, the encoder captures spatial relationships critical for disambiguating overlapping text and product layouts.
+
+#### **Cross-Modal Fusion**  
+Visual embeddings \( \mathbf{Z} \) are aligned with textual representations through a cross-modal projector, which maps \( \mathbf{Z} \) into the language model's embedding space.
+Let \( \mathbf{W}_p \in \mathbb{R}^{d_v \times d_t} \) denote a learnable projection matrix, where \( d_t \) is the language model's hidden dimension.
+The projected visual tokens \( \mathbf{V} \) are computed as:
+\[
+\mathbf{V} = \mathbf{Z} \mathbf{W}_p.
+\]  
+These tokens are concatenated with text token embeddings \( \mathbf{E}_{\text{text}} \in \mathbb{R}^{T \times d_t} \) to form a unified input sequence:  
+\[
+\mathbf{H}_{\text{in}} = [\mathbf{V}; \mathbf{E}_{\text{text}}].
+\]
+
+#### **Language Model Decoding**  
+The language model (e.g., LLaMA \cite{touvron2023llama}) processes \( \mathbf{H}_{\text{in}} \) autoregressively to generate structured output \( \mathbf{Y} = (y_1, \dots, y_T) \).
+At each step \( t \), cross-attention layers attend to visual tokens \( \mathbf{V} \) while self-attention layers model dependencies within the output sequence:
+\[
+\mathbf{Q}_t = \mathbf{W}_Q \mathbf{h}_{t-1}, \quad \mathbf{K}_v = \mathbf{W}_K \mathbf{V}, \quad \mathbf{V}_v = \mathbf{W}_V \mathbf{V},
+\]  
+\[
+\mathbf{h}_t' = \text{softmax}\left(\frac{\mathbf{Q}_t \mathbf{K}_v^\top}{\sqrt{d_t}}\right) \mathbf{V}_v + \mathbf{h}_{t-1},
+\]  
+\[
+P(y_t | y_{<t}, \mathbf{Z}) = \text{softmax}(\mathbf{W}_o \mathbf{h}_t'),
+\]  
+where \( \mathbf{W}_Q, \mathbf{W}_K, \mathbf{W}_V, \mathbf{W}_o \) are learnable parameters. The model is trained end-to-end using a cross-entropy loss:  
+\[
+\mathcal{L} = -\sum_{t=1}^T \log P(y_t^* | y_{<t}, \mathbf{Z}),
+\]  
+where \( y_t^* \) is the ground-truth token.
+
+---
+
+### **Application to Supermarket Leaflets**  
+LVLMs excel at extracting structured product information (e.g., prices, promotions) by jointly reasoning over visual and textual cues.
+For instance, given a leaflet image with the text "\$2.99" adjacent to an apple image, the model infers the association through cross-attention, generating output:
+\[
+\{\text{product: "Apples", price: 2.99, promotion: "Weekly Special"}\}.
+\]  
+Key advantages include:  
+1. **Ambiguity Resolution**: Differentiates prices from non-price numerals (e.g., "2 lbs") via contextual alignment of text and images.  
+2. **Layout Robustness**: Leverages spatial attention to associate scattered text fragments (e.g., disclaimers linked to products).  
+3. **Multilingual Support**: Inherits multilingual capabilities from pretrained language models, handling leaflets with mixed languages.
+
+---
+
+### **Advantages and Limitations**  
+LVLMs eliminate error-prone OCR pipelines and enable zero-shot generalization through their pretrained knowledge.
+Their unified architecture simplifies deployment and reduces computational overhead compared to hybrid OCR-LLM systems.
+However, limitations persist:
+- **Training Complexity**: Requires large-scale multimodal datasets (e.g., leaflet images paired with JSON outputs) for fine-tuning.  
+- **Hallucination Risks**: May generate plausible but incorrect details if visual grounding is weak (e.g., inventing prices for occluded text).  
+- **Resource Intensity**: High memory and compute demands during inference, limiting real-time applications.
+
+---
+
+### **Conclusion**  
+Large Vision-Language Models redefine supermarket leaflet information extraction by unifying visual and linguistic reasoning into an end-to-end framework.
+Their ability to directly map raw images to structured outputs, bypassing intermediate OCR stages, positions them as a promising solution for complex retail document understanding.
+Future work should focus on enhancing visual grounding, optimizing inference efficiency, and expanding multilingual support to address current limitations.
 
 \subsection{Dataset Creation}
-Since there was no dataset to evaluate or train, a custom dataset was created by manually annotating a collection of supermarket deal images.
-The dataset includes images with diverse layouts, fonts, and colors to ensure robustness.
-Each image is annotated with bounding boxes for text regions and corresponding labels for product name, brand, original price, deal price, and unit.
-The dataset is split into training, validation, and test sets to facilitate model development and evaluation.
-% Table \ref{tab:dataset} provides an overview of the custom dataset and Figure \ref{fig:dataset} shows sample images with annotations.
-% TODO: Add table and figure
+Since the availability of German supermarket leaflet data is literally not findable, a custom dataset was created by manually annotating a collection of supermarket deal images.
+The dataset includes images from the most common supermarket chains, each with unique layout, fonts, and colors to, in general, ensure the highest diversity and robustness possible.
+Each image is annotated with a corresponding label file that includes the desired entities as well as the image identificator.
+The dataset is split into a training (~ 80\%) and a validation set (~ 20\%) for each model to be trained and evaluated on.
+Table \tabref{tab:ie_dataset} provides an overview of the dataset with the sample size for each entity and \figref{fig:ie_dataset_samples} shows some sample images with their annotations.
 
-\subsection{Optical Character Recognition}
-Optical Character Recognition (OCR) is a critical component in the information extraction pipeline.
-Several OCR solutions were evaluated to determine the most suitable one for our task.
-The evaluated OCR tools include Tesseract, EasyOCR, PaddleOCR, and DocTR.
-Each tool was assessed based on its accuracy, speed, and ability to handle diverse fonts and layouts.
+\begin{table}[ht]
+\centering
+\caption{Leaflet-IE Dataset}
+\label{tab:ie_dataset}
+\begin{tabular}{lc}
+\toprule
+Entity           & Sample Size \\
+\midrule
+\code{image\_id}        & 372  \\
+\code{brand}            & 357  \\
+\code{product\_name}    & 370  \\
+\code{original\_price}  & 286  \\
+\code{deal\_price}      & 372  \\
+\code{weight}           & 369  \\
+\bottomrule
+\end{tabular}
+\end{table}
 
-\subsection{Experiments}
-\indent{\textbf{Setup}.}
-The experiments were conducted to compare the performance of different OCR solutions and end-to-end models for information extraction.
-The evaluation metrics include precision, recall, and F1-score for each entity type (product name, brand, original price, deal price, and unit).
-The experiments were performed on the test set of the custom dataset.
+Even though the Leaflet-IE dataset is relatively small, the reader will be able to see that the dataset is sufficient to evaluate the performance of different IE appraoches as well as to train an competitive end-to-end model.
+However, as the reader may notice, the dataset is solely focused on single product deals at this point and explicitly does not include
 
-\indent{\textbf{Results}.}
-The results of the experiments indicate that the end-to-end models, such as the Vision Encoder Decoder Model (e.g., Donut) and Large Vision-Language Models (LVLM), outperform traditional OCR-based methods in terms of accuracy and robustness.
-The OCR + LLM approach also shows promising results, particularly in handling OCR errors and extracting key-value pairs.
+\begin{figure*}[ht]
+\centering
+\fbox{\parbox[c][3cm][c]{5cm}{\centering Figure Placeholder: Sample Annotation}}
+\caption{Sample images with annotations from the custom dataset.}
+\label{fig:ie_dataset_samples}
+\end{figure*}
 
-\subsection{Evaluation}
-The evaluation of the models was conducted using standard metrics, including precision, recall, and F1-score.
-The comparison between LVLM, OCR + LLM, and Donut models highlights the strengths and weaknesses of each approach.
-The results demonstrate that end-to-end models provide superior performance in extracting structured information from supermarket deal images.
+\section{Experiments}
+
+The primary objective of these experiments is to identify the most effective approach for extracting structured information from supermarket leaflets.
+The evaluation considers general performance trends and use cases to determine candidate methodologies, including Hybrid OCR + LLM, end-to-end Vision-Encoder-Decoder models, and LVLMs.
+The order of the experiments is as follows:
+- Plain Deal OCR Performance
+- OCR + LLM Performance
+- Donut Fine-Tuning Performance
+- MAIN: Comparison of Hybrid OCR+LLM, Donut, and LVLM
+
+\subsection{Implementation Details}
+The experiments were conducted on two distinct computational workstations - station 1 equipped with an NVIDIA RTX 4080 GPU and station 2 with an NVIDIA GTX 1080 GPU.
+Therefore, the experiments could be conducted in parallel, ensuring efficient model training and evaluation.
+
+The software stack includegraphics Python with PyTorch as the primary deep learning framework, HuggingFace Transformers for leveraging pre-trained models, and OpenCV for image preprocessing and data augmentation.
+ PyTorch, HuggingFace Transformers, and various other libraries for data pre-and post-processing, visualization, data management and monitoring \footnote{The codebase is available at \href{https://github.com/ilyii/leaflets}{https://github.com/ilyii/leaflets}}.
+
+% SUB-STUDIES
+\subsection{Plain Deal OCR Performance}
+The aim of this experiment is to evaluate the performance of various OCR models in extracting text from supermarket leaflets.
+The evaluation focuses on the accuracies of the extracted entities from \tabref{tab:ie_dataset} and the impact of different normalization levels on the recognition performance.
+The results provide insights into the robustness and accuracy of different OCR models in handling the complexities of supermarket leaflet data.
+
+The most commonly used OCR models include:
+\begin{itemize}
+    \item Tesseract,
+    \item EasyOCR,
+    \item PaddleOCR,
+    \item DocTR.
+\end{itemize}
+These models have been trained on a variety of datasets and are known for their robustness and accuracy in text extraction.
+Since it is likely that none of the OCR models have seen this data before, all 372 samples of the Leaflet-IE dataset were used for evaluation.
+While OCR alone is not capable of generating key-value mappings, the evaluation used a different set of metrics:
+
+\begin{itemize}
+    \item \textbf{Accuracy}: Measures whether the expected value is present in the OCR output.
+    \item \textbf{N-gram Accuracy}: Determines if an n-gram substring of the expected value exists in the OCR output, computed for \(n \in \left[\frac{|v|}{2}, |v| - 1\right]\), where \(|v|\) represents the string length of the ground truth entity value.
+\end{itemize}
+
+Given that language-specific OCR errors are common, the evaluation was conducted at different levels of normalization to improve comparability. The text normalization included the following layers:
+\begin{itemize}
+    \item \textbf{Level 1:} Text stripping and string conversion.
+    \item \textbf{Level 2:} Lowercasing and basic replacements.
+    \item \textbf{Level 3:} Use-case specific replacements.
+    \item \textbf{Level 4:} Punctuation and whitespace removal.
+\end{itemize}
+Each level includes the normalization steps of the previous levels.
+Therefore, the normalization procedure can be thought of as a gradual alignment of the OCR output to the ground truth to investigate the OCR model's robustness to different normalization levels.
+
+\indent{\textbf{Results}.} Figure \ref{fig:eval_ocr_accuracies} presents a comparative analysis of various OCR models and normalization levels based on per-entity accuracy.
+The results highlight several key trends regarding the recognition performance of different entities.
+
+\begin{figure*}[h!]
+    \centering
+    \includegraphics[width=0.8\linewidth]{figures/eval_ocr_accuracies.png}
+    \caption{Accuracy per Entity of OCR Models at Different Normalization Levels.}
+    \label{fig:eval_ocr_accuracies}
+\end{figure*}
+
+In general, the OCR models exhibit superior performance in extracting words compared to numerical values.
+This discrepancy is particularly evident in entity-wise accuracy variations.
+At the baseline level (normalization level 1), the deal price entity consistently shows the lowest accuracy, whereas the brand entity achieves the highest.
+The accuracy of other entities varies significantly, with PaddleOCR, EasyOCR, and docTR displaying comparable performance, while Tesseract lags behind.
+
+The overall accuracy improves with increasing normalization levels, with normalization level 4 yielding the highest accuracy gains.
+At this level, Tesseract continues to struggle with deal price recognition, failing in over 90\% of cases.
+In contrast, the other OCR models achieve accuracies exceeding 70\% across nearly all entity types.
+
+Among the different entities, brand names are consistently recognized with the highest accuracy.
+This can be attributed to their simpler linguistic structure and distinct visual presentation, as brand names are often bolded or highlighted in promotional material.
+In contrast, product names tend to have more complex linguistic structures, making exact string matching more challenging.
+
+The recognition of unit information lags behind brand names but remains more accurate than deal prices.
+The reduced accuracy can be explained by the smaller font size of unit labels, their less prominent placement, and the high variability in unit measurements (e.g., "kg", "g", "Stück"), which complicates recognition.
+
+A significant gap is observed between deal price and original price accuracy.
+This can be attributed to the typographic differences between the two: deal prices are often emphasized using distinctive fonts and superscripted decimals, making them harder for OCR models to interpret correctly.
+In contrast, original prices are typically displayed in a standard inline format, which is easier to recognize.
+
+\begin{figure*}[h!]
+    \centering
+    \includegraphics[width=0.8\linewidth]{figures/eval_ocr_ngram_accuracies.png}
+    \caption{N-gram Accuracy per Entity of OCR Models at Different Normalization Levels.}
+    \label{fig:eval_ocr_ngram_accuracies}
+\end{figure*}
+
+When evaluating n-gram accuracy per-entity in \figref{fig:eval_ocr_ngram_accuracies}, the results reveal a similar trend to per-entity accuracy.
+When comparing the OCR models, PaddleOCR consistently outperforms the other models especially in the price extractions while Tesseract lacks behind in all entities.
+
+The most significant observation is that the deal price and original price exhibit in lower normalization levels significantly worse accuracies.
+Since the length of n-gram sequences increase superlinearly, longer entity values, precisely the brand and product name, more likely achieve higher accuracies, which is also reflected in the results.
+
+At the highest normalization level, most models achieve 100\% or close to 100\% n-gram accuracy in the majority of entites.
+Additionally, here the discrepancy of Tesseract is most visible, where it cannot nearly achieve comparable scores.
+Also, one can observe that the unit entity drops significantly at level 4 across all models.
+This can be attributed to the high variability in unit measurements, which makes it challenging to match the exact n-grams.
+
+%TODO: Add table with entity-avg results
+
+% EXPERIMENT: OCR+LLM
+\subsubsection{Hybrid-OCR+LLM Performance}
+
+In addition to evaluating the OCR capabilities, the performance of OCR models was assessed in conjunction with large language models (LLMs). The primary questions addressed were:
+\begin{itemize}
+    \item Which LLM is best suited to work with these OCR outputs?
+    \item Which OCR and LLM combination works best for information extraction (IE)?
+\end{itemize}
+
+All 372 samples of the Leaflet-IE dataset were used for evaluation.
+It is assumed that neither the OCR models nor the LLMs have previously encountered this data, similar to the OCR evaluation.
+Since the task is to extract structured information, the evaluation metrics were adapted to reflect the performance of the OCR-LLM combination in generating key-value mappings.
+The evaluation metrics include:
+\begin{itemize}
+    \item \textbf{Accuracy (Per Entity):} Measures the accuracy (of each extracted entity).
+    \item \textbf{Levenshtein Distance:} Calculates the distance between the prediction and the ground truth.
+\end{itemize}
+
+The LLMs were prompted to extract entities from the OCR output. The specific prompt used can be found in the appendix (see Appendix \ref{appendix:prompt}).
+
+\paragraph{Models Evaluated:}
+\begin{itemize}
+    \item \textbf{Llama 3.1 [8b, Q4]}: \texttt{llama3.1\_8b},
+    \item \textbf{Qwen 2.5 [1.5b, Q8]}: \texttt{qwen2.5\_1.5b-instruct-q8\_0},
+    \item \textbf{Llama 3.2 [3b, Q8]}: \texttt{llama3.2\_3b-instruct-q8\_0},
+    \item \textbf{Qwen 2.5 [7b, Q4]}: \texttt{qwen2.5\_7b},
+\end{itemize}
+where the LLM name and version is additionally specified through the model size (in billions of parameters) and the quantization level.
+
+To avoid confusion with the normalization used in the OCR experiment, the OCR results were kept raw, as normalization may remove valuable information.
+The LLMs are expected to handle such inconsistencies and errors in the input.
+Instead, here the entity values were evaluated in both raw form and with a normalization applied for the comparability between the LLM prediction and the ground truth value .
+The normalization procedure includes usual character replacements and filtering based on linguistic artifacts commonly encountered in OCR errors.
+The specific normalization procedure can be found in the appendix
+% TODO: (see Appendix \ref{appendix:ocr_llm_normalization}).
+
+\paragraph{Results:}
+The entity-averaged accuracies and Levenshtein distances for the raw OCR output are depicted in Figures \ref{fig:eval_ocr_llm_accuracies_avg} and \ref{fig:eval_ocr_llm_levdist_avg}, respectively.
+
+\begin{figure*}[h!]
+    \centering
+    \includegraphics[width=0.8\linewidth]{figures/eval_ocr_llm_accuracies_avg.png}
+    \caption{Entity-Averaged Accuracy of LLM Models per Raw OCR Output.}
+    \label{fig:eval_ocr_llm_accuracies_avg}
+\end{figure*}
+
+The averaged accuracies reveal that a higher number of parameters is more beneficial for the LLMs in this task than a higher quantization level.
+Specifically, the Llama 3.1:8b and Qwen 2.5:7b models achieve significantly higher accuracy scores than their counterparts with a lower number of parameters.
+Qwen 2.5:1.5b in Q8 performs worse than Llama 3.2:3b in Q8, but Qwen 2.5:7b in Q4 is overall the best.
+These differences can be attributed to multiple factors, such as the pre-training data of the models, the model architecture, or the prompt used to extract the entities.
+DocTR and PaddleOCR achieve equal or better results than Tesseract and EasyOCR.
+Specifically, Tesseract consistently performs the worst among the evaluated models.
+
+% \begin{figure*}[h!]
+%     \centering
+%     \includegraphics[width=0.8\linewidth]{figures/eval_ocr_llm_levdist_avg.png}
+%     \caption{Entity-Averaged Levenshtein Distance of OCR-LLM Models (Raw OCR Output).}
+%     \label{fig:eval_ocr_llm_levdist_avg}
+% \end{figure*}
+% FIGURE TWO COLUMNS WIDE
+\begin{figure*}[h!]
+    \centering
+    \includegraphics[width=0.7\linewidth]{figures/eval_ocr_llm_levdist_avg.png}
+    \caption{Entity-Averaged Levenshtein Distance of OCR-LLM Models (Raw OCR Output).}
+    \label{fig:eval_ocr_llm_levdist_avg}
+\end{figure*}
+
+When regarding the levenshtein distances, the results show similar trends.
+DocTR delivers by far the best OCR input across all OCR models.
+Suprisingly, Tesseract achieves lower levenshtein distances than PaddleOCR and EasyOCR, with EasyOCR being the worst across all models.
+This could be due to the fact that Tesseract delivers more often slightly wrong but still similar results, while EasyOCR delivers less often wrong but more different results.
+The LLMs show similar trends as in the accuracy evaluation, but Llama 3.1:8b now slightly outperforms Qwen 2.5:7b.
+The differences between the LLMs are less pronounced than in the accuracy evaluation, which can be attributed to the unnormalized levenshtein distance calculation used.
+
+% The entity-specific accuracies for the raw OCR output are shown in \figref{fig:eval_ocr_llm_accuracies_raw}, while the entity-specific levenshtein distances for the raw OCR output are shown in \figref{fig:eval_ocr_llm_levenshtein_raw}.
+
+% \begin{figure*}[h!]
+%     \centering
+%     \includegraphics[width=0.8\linewidth]{figures/eval_ocr_llm_accuracies_raw.png}
+%     \caption{Accuracy per Entity of OCR-LLM Models (Raw OCR Output).}
+%     \label{fig:eval_ocr_llm_accuracies_raw}
+% \end{figure*}
+
+% \begin{figure*}[h!]
+%     \centering
+%     \includegraphics[width=0.8\linewidth]{figures/eval_ocr_llm_accuracies_normalized.png}
+%     \caption{Accuracy per Entity of OCR-LLM Models (Normalized OCR Output).}
+%     \label{fig:eval_ocr_llm_accuracies_normalized}
+% \end{figure*}
+
+% \begin{figure*}[h!]
+%     \centering
+%     \includegraphics[width=0.8\linewidth]{figures/eval_ocr_llm_levenshtein_raw.png}
+%     \caption{Levenshtein Distance per Entity of OCR-LLM Models (Raw OCR Output).}
+%     \label{fig:eval_ocr_llm_levenshtein_raw}
+% \end{figure*}
+
+% \begin{figure*}[h!]
+%     \centering
+%     \includegraphics[width=0.8\linewidth]{figures/eval_ocr_llm_levenshtein_normalized.png}
+%     \caption{Levenshtein Distance per Entity of OCR-LLM Models (Normalized OCR Output).}
+%     \label{fig:eval_ocr_llm_levenshtein_normalized}
+% \end{figure*}
+
+\subsection{Donut Fine-Tuning Performance}
+Experiment Question:
+- Is it possible to train a Vision Encoder Decoder model to extract end2end information from supermarket leaflet deal images?
+
+Setup:
+
+Results:
+
+% \subsection{Comparison of Hybrid OCR+LLM, Donut, and LVLM}
+% - Evaluating the results from the prepending experiments, the main goal is to compare the performance of the best OCR + LLM model with end-to-end models.
+% - As best OCR + LLM model, the decision was made to use DocTR as OCR model and Qwen 2.5:7b as well as Llama 3.1:8b as LLM models due to their similar performance.
+% - Donut was used as end-to-end Vision Encoder Decoder Model
+% - As LVLMs, MiniCPM-V and Llama3.2-Vision were used.
+
+% - Dataset: Leaflet-IE validation subset, since Donut was trained on the train subset.
+% - Evaluation Metrics: Accuracy, levenshtein distance on entity level
+% - Normalization: The same approach as in OCR + LLM evaluation was used to normalize the entity value predictions and the corresponding ground truth values.
+
+% \indent{\textbf{Results}.}
+% - Per-Entity Accuracy without normalization (\figref{fig:eval_final_acc_raw})
+%     - OCR+LLM significantly worst, on validation subset original and deal price at 0\% accuracy
+%     - LVLM by far the best, especially in deal price. This is because LVLMs are able to use spatial information and context to infer the correct entity values.
+%     - Donut can keep up with the LVLMs, but is slightly worse, especially in brand
+% - Per-Entity Levenshtein Distance without normalization (\figref{fig:eval_final_levdis_raw})
+%     - LVLMs and donut overall very low scores, which is expected due to the high accuracy
+%     - OCR+LLM much higher scores, Suprisingly especially in brand.
+%     - Overall, brand has the highest levenshtein distance, which is uncommon.
+
+% - Per-Entity Accuracy with normalization (\figref{fig:eval_final_acc_norm})
+%     - Overall results are much better, especially for OCR+LLM. Here, the price detection is even the best.
+%     - But OCR+LLM still significantly worse than LVLMs and Donut.
+%     - It is mentionable that Donut achieves very solid and stable accuracies across all entities, whereas the LVLMs have a higher variance.
+%     - LVLMs still by fare the best, especially in the prices.
+% - Per-Entity Levenshtein Distance with normalization (\figref{fig:eval_final_levdis_norm})
+%     - Overall drops in levenshtein distance, especially for OCR+LLM
+%     - LVLMs achieve lowest scores, but have high variance
+%     - Donut very consistent
+%     - Still highest levenshtein distance in brand, which is uncommon.
+
+% Conclusions 
+% -> LVLMs are the best choice for IE tasks, especially when spatial information is important. However, LVLMs are very resource-intensive and require a lot of computational power.
+% -> Donut is a good alternative, especially when the computational resources are limited.
+When regarding the limited training resources, it is possible that, in the long run, Donut could outperform the LVLMs in this specific task.
+It is to mention that models like Donut are very hard to generalize to other tasks, whereas LVLMs can be used for a wide range of tasks.
+% -> OCR+LLM is significantly worse.
+Attributed to the lack of spatial and visual information, error propagation from OCR to LLM, and the lack of training data.
+However, it is a good choice when computational resources are limited and the task is not too complex.
+
+\subsection{Comparison of Hybrid OCR+LLM, Donut, and LVLM}
+
+This section presents a comparative evaluation of a hybrid OCR+LLM pipeline against end-to-end models, specifically Donut and Large Vision-Language Models (LVLMs), for information extraction (IE) from supermarket leaflets.
+The assessment focuses on model performance using the best OCR+LLM configuration and two end-to-end approaches.
+
+\subsubsection{Experimental Setup}
+
+\paragraph{Models.} The following models were selected for evaluation:
+\begin{itemize}
+    \item \textbf{OCR+LLM:} DocTR was utilized as the OCR engine, with Qwen 2.5-7B and LLaMA 3.1-8B serving as LLMs due to their comparable performance.
+    \item \textbf{Donut:} An end-to-end Vision Encoder-Decoder model optimized for document understanding.
+    \item \textbf{LVLMs:} MiniCPM-V and LLaMA 3.2-Vision were chosen as large vision-language models for comparison.
+\end{itemize}
+
+\paragraph{Dataset.} The Leaflet-IE validation subset was used for evaluation since Donut had been trained on the train subset.
+
+\paragraph{Evaluation Metrics.} The models were evaluated using:
+\begin{itemize}
+    \item \textbf{Accuracy}: The percentage of correctly extracted entity values.
+    \item \textbf{Levenshtein Distance}: The edit distance between predicted and ground truth values at the entity level.
+\end{itemize}
+
+\paragraph{Normalization.} To ensure consistency, the same normalization approach from the OCR+LLM evaluation was applied to both model predictions and ground truth values.
+
+\subsubsection{Results and Discussion}
+
+\paragraph{Per-Entity Accuracy Without Normalization} (\figref{fig:eval_final_acc_raw})
+\begin{itemize}
+    \item The OCR+LLM pipeline performed significantly worse than both Donut and LVLMs. Specifically, its accuracy for original and deal price entities was close to 0\%.
+    \item LVLMs outperformed all other models, particularly in extracting price-related information.
+Their superior performance is attributed to their ability to leverage spatial information and contextual cues.
+    \item Donut achieved competitive results, closely trailing LVLMs, but showed a notable drop in accuracy for brand recognition.
+\end{itemize}
+
+\paragraph{Per-Entity Levenshtein Distance Without Normalization} (\figref{fig:eval_final_levdis_raw})
+\begin{itemize}
+    \item As expected from the accuracy results, LVLMs and Donut exhibited low Levenshtein distances, indicating high precision.
+    \item The OCR+LLM approach had significantly higher edit distances, particularly for brand recognition, suggesting a consistent difficulty in extracting brand names accurately.
+    \item Among all entities, brand names showed the highest Levenshtein distance across models, which is uncommon in IE tasks.
+\end{itemize}
+
+\paragraph{Per-Entity Accuracy With Normalization} (\figref{fig:eval_final_acc_norm})
+\begin{itemize}
+    \item Applying normalization significantly improved accuracy, especially for OCR+LLM. Interestingly, its price detection performance exceeded that of Donut in some cases.
+    \item Despite the improvements, OCR+LLM remained notably weaker than LVLMs and Donut.
+    \item Donut displayed stable and balanced accuracy across all entities, whereas LVLMs exhibited higher variance.
+    \item LVLMs retained their leading performance, particularly in price extraction.
+\end{itemize}
+
+\paragraph{Per-Entity Levenshtein Distance With Normalization} (\figref{fig:eval_final_levdis_norm})
+\begin{itemize}
+    \item Levenshtein distances decreased across all models post-normalization, especially for OCR+LLM.
+    \item LVLMs achieved the lowest Levenshtein distances but maintained high variance.
+    \item Donut demonstrated remarkable consistency across all entities.
+    \item The brand entity continued to exhibit the highest Levenshtein distances across models.
+\end{itemize}
+
+\subsubsection{Conclusions}
+
+\begin{itemize}
+    \item \textbf{LVLMs are the most effective for IE tasks}, particularly when spatial information is crucial.
+However, their computational requirements are significantly higher, making them less practical in resource-constrained environments.
+    \item \textbf{Donut provides a strong trade-off between accuracy and efficiency}.
+Given the limited training resources, Donut has the potential to outperform LVLMs in the long run for this specific task.
+However, its generalization ability is limited compared to LVLMs, which can be applied to a wider range of tasks.
+    \item \textbf{OCR+LLM is considerably weaker} than the other approaches. Its performance limitations are primarily attributed to:
+    \begin{itemize}
+        \item Lack of spatial and visual information.
+        \item Error propagation from OCR to LLM.
+        \item Insufficient training data for robust IE.
+    \end{itemize}
+    Nevertheless, OCR+LLM remains a viable option when computational resources are constrained, and the task complexity is moderate.
+\end{itemize}
+
+\begin{figure*}[h!]
+    \centering
+    \includegraphics[width=0.8\linewidth]{figures/eval_final_acc_raw.png}
+    \caption{Per-Entity Accuracy without normalization.}
+    \label{fig:eval_final_acc_raw}
+\end{figure*}
+
+\begin{figure*}[h!]
+    \centering
+    \includegraphics[width=0.8\linewidth]{figures/eval_final_levdis_raw.png}
+    \caption{Per-Entity Levenshtein Distance without normalization.}
+    \label{fig:eval_final_levdis_raw}
+\end{figure*}
+
+\begin{figure*}[h!]
+    \centering
+    \includegraphics[width=0.8\linewidth]{figures/eval_final_acc_norm.png}
+    \caption{Per-Entity Accuracy with normalization.}
+    \label{fig:eval_final_acc_norm}
+\end{figure*}
+
+\begin{figure*}[h!]
+    \centering
+    \includegraphics[width=0.8\linewidth]{figures/eval_final_levdis_norm.png}
+    \caption{Per-Entity Levenshtein Distance with normalization.}
+    \label{fig:eval_final_levdis_norm}
+\end{figure*}
 
 \section{Application}
+
 \subsection{Database}
-
-\subsection{Optical Character Recognition}
-
-    \subsection{Experiments}
-    \indent{\textbf{Setup}.}
-    - Common OCR solutions: Tesseract, EasyOCR, PaddleOCR, DocTR
-    - Goal: Which OCR solution is the best for our task?
-    -
-
-    \subsection{Evaluation}
-    - LVLM, OCR+LLM, Donut
-    - OCR + LLM Vergleich
 
@@
 
+\appendix
+\section{Appendices}
+\subsection{OCR Evaluation:Normalization Procedure}
+% def normalize_text(text, level=6):
+%     if not text or pd.isnull(text) or text == "":
+%         return ""
+
+%     # Level 1: Basic cleaning (handles empty values)
+%     if level >= 1:
+%         text = str(text).strip()
+
+%     # Level 2: Lowercasing & basic replacements (whitespace, German characters)
+%     if level >= 2:
+%         text = text.lower()
+%         text = text.replace("\n", " ").replace("\t", " ").replace("\r", " ")
+%         text = text.replace("ö", "o").replace("ä", "a").replace("ü", "u").replace("ß", "ss")
+
+%     # Level 3: Extended normalization (remove special characters, normalize hyphens)
+%     if level >= 3:
+%         text = text.replace("-", " ").replace("–", " ").replace("—", " ").replace("−", " ")
+%         text = "".join([char for char in text if char.isalnum() or char in {".", " "}])
+%         text = " ".join(text.split())  # Remove extra spaces
+
+%     if level >= 4:
+%         text = text.replace(" ", "")
+%         text = text.replace(".", "")
+%     return text
+
+\subsection{LLM Prompt}
+TODO
+
+\subsection{OCR + LLM Evaluation: Normalization Procedure}
+
+% \textbf{Normalization Procedure:}
+
+% \begin{lstlisting}[language=Python, caption=Text Normalization Procedure]
+% REPLACEMENTS = {
+%     "ä": "a", "ö": "o", "ü": "u", "ß": "ss", ",": ".", "€": "",
+%     "–": " ", "—": " ", "−": " ", "ô": "o", "é": "e", "ç": "c",
+%     "è": "e", "à": "a", "ê": "e", "â": "a", "û": "u", "î": "i",
+%     "ë": "e", "ï": "i", "œ": "oe", "æ": "ae", "ù": "u"
+% }
+% def normalize(text):
+%     for key, value in REPLACEMENTS.items():
+%         text = text.replace(key, value)
+%     text = "".join([char for char in text if char.isalnum() or char in {".", " "}])
+%     text = "".join(text.split())
+%     return text.strip().lower()
+% \end{lstlisting}
+% TODO -> In appendix
+% TODO: Continue
+
 \end{document}

### 2025-02-22 paper/main_ilyi.tex
Pre-final paper version of ilyi.

--- 2025-02-18 paper/main_ilyi.tex
@@
 \usepackage{hyperref}
+\usepackage{subfig}
+
+\usepackage{algorithm}
+\usepackage{algpseudocode}
+\usepackage{verbatim}
 
@@
 \section{Introduction}
+
 \subsection{Motivation}
+When one thinks of a paper-heavy country, Germany is likely to come to mind.
+The country's affinity for printed materials is deeply ingrained in its culture, with activities such as browsing through supermarket leaflets serving as a familiar ritual for many individuals.
+These leaflets have long been an essential medium for consumers to plan their purchases, discover special offers, and compare prices.
+The tactile nature of printed leaflets, the excitement of spotting discounts, and the satisfaction of making a well-informed shopping decision contribute to their enduring appeal.
+However, the rapid advancement of digital technology is transforming consumer behavior.
+While some individuals still find browsing through physical leaflets a nostalgic and even relaxing experience, younger generations are increasingly turning to digital alternatives for their shopping needs.
+The modern shopper expects convenience, efficiency, and instant access to information, yet the digital transformation of supermarket leaflets lags significantly behind other aspects of e-commerce and retail technology.
+
+Despite the existence of applications that compile digital versions of these leaflets, their usability and overall quality remain suboptimal.
+Many digital leaflets are plain documents, failing to leverage the full potential of interactivity, searchability, and intelligent recommendation systems.
+There is a pressing need for sophisticated digital solutions that not only present supermarket deals but also enable consumers to interact with them in a meaningful way.
+
+Possibly, one can imagine a seamless digital platform where users can search for specific items across multiple supermarket chains, apply dietary filters to instantly highlight suitable products, or receive personalized recommendations based on past preferences.
+A tool that allows consumers to create a dynamic shopping list, track price trends over time, and receive real-time updates on the best deals would revolutionize the way people approach grocery shopping.
+Yet, these features remain largely absent from existing digital leaflet solutions.
+Furthermore, while price comparison websites and applications have become commonplace for electronics, fashion, and travel, the grocery sector remains an overlooked frontier.
+Consumers are often left navigating multiple supermarket websites or manually cross-referencing prices to find the best deals—a tedious and inefficient process.
+A comprehensive digital ecosystem that integrates grocery price comparisons, personalized discounts, and AI-driven shopping assistants could bridge this gap and act as a workaround, offering an enhanced, data-driven shopping experience tailored to individual needs.
+
 \subsection{Problem Statement}
+The primary objective of this research is to develop an intelligent system for extracting, structuring, and utilizing information from supermarket leaflets in a digital format.
+Given a set of supermarket leaflets $\mathbf{L} = \{L_1, L_2, ..., L_n\}$, where each $L_i$ contains a set ofproduct deals $\{p_j\}_{j=1}^{m} \in P_{L_i}$, the goal is to extract and normalize these attributes to enable efficient querying and comparison across multiple supermarket chains.
+
+Each product deal $p_j$ is represented by a set of attributes $\{y_1, y_2, ..., y_k\}$, where each attribute $y_k$ represents a specific entity.
+Common attributes include the name and brand of the product, the original and deal prices, the unit (e.g., weight, volume), and the product image.
+The challenge lies in detecting and separating deals from the leaflet, extracting structured information from the detected deals, normalizing the extracted information to ensure consistency and comparability, and validating the extracted information to ensure accuracy.
+
+To enable advanced applications such as the abovementioned, one has to tackle different challenges, such as:
+\begin{enumerate}
+    \item Detecting and separating deals $p$ from the leaflet $L$.
+    \item Extracting structured information from the detected deals.
+    \item Normalizing the extracted information to ensure consistency and comparability.
+    \item Validating the extracted information to ensure accuracy.
+\end{enumerate}
+
+Therefore, a function $f: \mathcal{L} \to \mathcal{D}$ has to be designed, that maps a set of leaflets $\mathcal{L}$ to a set of structured deals $\mathcal{D}$, where each deal $d \in \mathcal{D}$ is represented by a set of attributes $\{y_1, y_2, ..., y_k\}$.
+
 \subsection{Contributions}
+To build this mapping, this work presents the conducted research and the practical result of a comprehensive approach to digitalizing and structuring supermarket leaflet information by leveraging advanced computer vision, OCR, and language models, as shown in \figref{fig:overview}.
+A \emph{modular pipeline} is proposed that encompasses deal detection, information extraction and normalization to transform raw leaflet data into structured, actionable insights.
+
+\begin{figure*}
+    \centering
+    \includegraphics[width=0.8\linewidth]{figures/overview.png}
+    \caption{Overview of the proposed approach to digitalizing and structuring supermarket leaflet information.}
+    \label{fig:overview}
+\end{figure*}
+
+To enhance usability, an \emph{interactive application} is developed that allows consumers to browse, filter, and compare deals across multiple supermarket chains.
+It provides essential search, tracking, and comparison features for improved deal discovery.
+
+To facilitate research and development in this domain, \emph{Leaflet-IE}, an end-to-end benchmark dataset for information extraction from supermarket leaflets, is introduced.
+This dataset stands as a valuable resource for evaluating and comparing different models and approaches in the field.
+
+\subsection{Structure}
+This work is structured to systematically address supermarket deal detection and information extraction, beginning with a scientific overview of related works in Section 2, which categorizes existing approaches and identifies their limitations.
+Section 3 provides a detailed analysis of the nature of supermarket leaflet data, formalizing challenges such as layout variability, OCR noise, and multimodal fusion.
+Section 4 focuses on deal detection, covering dataset creation, model selection, and experimental results for identifying promotional content.
+Section 5 extends this to information extraction, detailing dataset construction, model architectures, and performance evaluation for extracting structured product and pricing information.
+Finally, Section 6 concludes with key contributions, limitations, and future directions, including scalability and temporal reasoning improvements.
 
 \section{Related Works}
+\indent{\textbf{Supermarket Leaflet Analysis}.}
+The field of supermarket leaflet analysis has evolved to tackle key challenges such as product classification, promotion identification, and customer interaction.
+Recent studies have leveraged AI-driven techniques to enhance efficiency and accuracy in this domain.
+For instance, Ladwig et al.
+\cite{ladwig2023} explore fine-grained product classification in leaflet advertisements, while Arroyo et al.
+\cite{arroyo2020} employ multi-label classification methods to analyze promotions using both textual and visual information.
+Additionally, Zhang et al.
+\cite{zhang2024} introduce PKU-GoodsAD, a dataset designed for unsupervised anomaly detection and segmentation of supermarket goods.
+Complementing these efforts, Nandkumar et al.
+\cite{nandkumar2024} propose a multi-level LLM conversational interface to enhance supermarket robot interactions by handling diverse customer intents.
+
 \indent{\textbf{Deal Detection}.}
-\indent{\textbf{Optical Character Recognition}.}
-OCR-Model-Driven methods use OCR tools to acquire text
-and bounding box information. Subsequently, they rely
-on the models to integrate text, layout, and visual data.
 
 \indent{\textbf{Information Extraction}.}
+Recent advancements in Optical Character Recognition (OCR), Large Language Models (LLMs), and end-to-end multimodal architectures have significantly refined the landscape of document information extraction.
+These improvements have led to increased accuracy, efficiency, and versatility in processing structured and unstructured text from diverse document formats.
 
+OCR technology has evolved from traditional rule-based approaches to sophisticated deep learning-driven systems.
+Open-source OCR frameworks such as Tesseract, PaddleOCR, EasyOCR, and DocTR integrate state-of-the-art methodologies to enhance both text detection \cite{liao2019, liao2022} and recognition \cite{shi2015, li2022}.
+These systems employ deep neural networks to improve accuracy in complex document layouts, including distorted and low-quality images.
+Preprocessing techniques play a crucial role in optimizing OCR performance.
+Methods such as rectification \cite{shi2019}, deskewing \cite{pham2022}, and denoising \cite{zhao2018} significantly enhance text clarity by mitigating distortions, reducing noise, and improving alignment.
+These preprocessing steps are especially useful in real-world scenarios where scanned or photographed documents contain various inconsistencies.
+LLMs have emerged as powerful tools for refining OCR outputs through context-aware reasoning and semantic corrections.
+Models like GPT-3 \cite{brown2020} and LLaMA \cite{touvron2023} demonstrate exceptional performance in natural language understanding, enabling improved entity recognition and post-processing of extracted text \cite{yenduri2023}.
+These models enhance the reliability of OCR by resolving ambiguities, correcting misinterpretations, and providing structured outputs in diverse domains such as finance, healthcare, and legal documentation.
+
+Transformer-based architectures \cite{vaswani2017, dosovitskiy2021} have revolutionized document understanding by integrating vision and language processing into unified frameworks.
+Models such as Donut \cite{kim2022} and DocFormer \cite{appalaraju2021} leverage attention mechanisms to jointly process textual and visual cues, achieving state-of-the-art performance in document analysis.
+These models are particularly effective in handling complex layouts, handwriting recognition, and tabular data extraction.
+Furthermore, multimodal approaches \cite{peng2022, li2021} introduce hybrid learning techniques that enhance information retrieval from scanned documents and digital forms.
+
+The integration of large vision-language models (LVLMs) has further expanded the capabilities of document intelligence.
+Models such as LLaMA 3.2 Vision \cite{touvron2023}, Qwen-VL \cite{qwen2025}, and GPT-4V \cite{dai2023} utilize large-scale multimodal training to perform sophisticated image-text reasoning.
+These advancements enable robust document understanding, particularly in scenarios where textual information is closely intertwined with graphical elements.
+Recent contributions \cite{li2024, wei2024} emphasize the growing potential of LVLMs.
+
+\section{The Nature of Supermarket Leaflet Data}  
+Supermarket leaflets constitute a complex multimodal data domain characterized by heterogeneous layouts, ambiguous associations, and noisy signal extraction.
+As illustrated in \figref{fig:leaflet_data_samples}, these documents present unique computational challenges that demand joint reasoning over visual, textual, and contextual modalities.
+We formalize the key obstacles below.
+
+Leaflets exhibit extreme variability in design elements that impede automated parsing.
+The spatial heterogeneity, thus the non-standardized arrangements of product images, prices, and promotions across retailers, is a primary concern.
+The layout of leaflets can vary significantly, with product images, prices, and promotional text appearing in diverse configurations.
+Additionally, typography challenges, such as superscripted decimals, struck-through original prices, and font inconsistencies between deals and regular text, further complicate the extraction process.
+Overlapping elements, where text is occluded by product images or graphical overlays, violate the assumptions of Optical Character Recognition (OCR) systems, which assume planar text.
+
+\begin{figure}[h!]
+    \centering
+    \includegraphics[width=0.8\linewidth]{figures/samples.png}
+    \caption{Common German supermarket deals.}
+    \label{fig:leaflet_data_samples}
+\end{figure}
+
+Inherently, these leaflets contain both textual and visual information, which must be jointly processed to extract meaningful insights.
+The textual elements include product names, brands, prices, and units, while the visual components consist of product images, logos, and promotional graphics.
+The challenge lies in aligning these modalities to extract structured information accurately.
+Furthermore, the multimodal nature of the data introduces semantic ambiguities, where textual and visual elements maintain non-strict correspondences.
+For instance, a product image may correspond to multiple text entries, or price interpretation may require visual grounding.
+
+Due to these characteristics, leaflets are prone to linguistic ambiguities, conversion errors and cultural-specific semantics.
+The German language, with its compound nouns, specific punctuation conventions, and diverse word forms, poses unique challenges for text extraction.
+OCR errors, such as glyph confusion and tokenization failures, are common due to font artifacts and compound nouns.
+Multilingual mix, where English promotion terms appear alongside German body text, further complicates the parsing process.
+Price disambiguation, distinguishing unit prices from total prices without weight references, is a critical challenge.
+Additionally, more complex offer strategies, such as buy-one-get-one-free, coupon-based discounts, and permanent price reductions, require nuanced interpretation beyond simple text extraction.
+
+Additionally, supermarket leaflets are commonly scheduled for a weekly release, with each leaflet containing a set of deals that are valid for a specific period.
+However, not every supermarket chain follows this pattern, and some may release leaflets bi-weekly, monthly or even irregularly.
+This temporal grounding problem requires associating each deal with an expiry time, which is often implicit in the leaflet text.
+For instance, a deal may be valid only in specific store branches or for a limited time, indicated by small print codes or context clues.
+
+This multifaceted nature demands architectures that jointly optimize for visual-textual alignment, error-resilient parsing, and contextual plausibility. 
 \section{Deal Detection}
@@
 \section{Information Extraction of Supermarket Deals}
-    % - Subsequent to detection and separation of deals, the goal is to extract useful information from it.
-    % - Difficulties
-    %     - High variety of layouts, colors, fonts, sizes
-    %         - Deal sometimes have superscripted decimals and no separation dot.
-    %         - Original prices are sometimes striked through.
-    %         - Deal prices are sometimes in a very different font to the ones it was trained on.
-    %         - Overlapping elements
-    %     - Multimodal information
-    %         - Product image: visual
-    %         - Text: alphabetical + numerical
-    %     - OCR errors
-    %     - Eigennamen (mostly brand names)
-    %     - German language
-    % - Goal: Extract 
-    %     - Product name
-    %     - brand
-    %     - original price
-    %     - deal price
-    %     - unit
 Subsequently to the detection and separation of supermarket deals, the overarching goal of using these in applications requires the extraction of the various useful information from these deals. 
 The task of extracting meaningful and structured information from supermarket deal images is a complex and multi-faceted problem, requiring the integration of various modalities, overcoming challenges posed by noisy data, and leveraging deep learning techniques.
-This section provides a detailed exploration of the underlying challenges, methodologies, and the theoretical and practical framework needed to perform such extraction.
+This section provides a detailed exploration of methodologies, as well as the theoretical and practical framework needed to perform such extraction.
 
-\subsection{Challenges in Information Extraction for Supermarket Deals}
-
-Supermarket deal extraction involves a series of challenges that require careful attention and sophisticated methods to resolve.
-These challenges include the diversity of layout and format in the images, the multimodal nature of the data, the frequent occurrence of Optical Character Recognition (OCR) errors, and the specific linguistic and cultural issues posed by the German language.
-
-% \subsubsection{High Variety in Layouts and Visual Elements}
-\indent{\textbf{High Variety in Layouts and Visual Elements.}}
-Supermarket deals exhibit considerable variability in layout, color schemes, font choices, and text sizes, which hinders automatic detection and extraction.
-Deals are often printed with superscripted decimals or without clear separation between integer and fractional components of the price (e.g., "2.29" might appear as "229").
-This phenomenon exacerbates OCR difficulties.
-Additionally, original prices may be struck through, while deal prices are sometimes printed in drastically different fonts than those the OCR model was trained on.
-Furthermore, overlapping elements—such as product images or additional textual information—often interfere with text extraction and localization.
-These diverse visual elements require robust and flexible models capable of accommodating such variability.
-
-% \subsubsection{Multimodal Information}
-\indent{\textbf{Multimodal Information.}}
-Supermarket deal images consist of both visual (e.g., product images) and textual (e.g., brand names, prices, and product descriptions) modalities, each contributing different types of information.
-While text provides rich information about the product’s identity, pricing, and units, the image serves as a supplementary modality that aids in product identification, brand recognition, and other visual cues.
-Multimodal fusion, where information from both text and image domains is integrated, is a key challenge, and existing models must effectively leverage both sources to provide high-quality extraction.
-
-\indent{\textbf{Conversion Errors and Linguistic Challenges.}}
-OCR systems frequently introduce errors, particularly when dealing with non-standard fonts, noisy backgrounds, or small text.
-This is particularly problematic when extracting numerical data such as prices.
-Common errors include misinterpretation of decimals and digits (e.g., "229" instead of "2.29") and missing characters.
-To address this, OCR post-processing steps, such as error correction using context-based reasoning or dedicated error models, are required.
-Additionally, the presence of proper nouns—particularly brand names—adds complexity, as these entities may not appear in typical language models, making their extraction difficult.
-Furthermore, the German language presents its own set of challenges, including compound words, specific punctuation conventions, and diverse word forms, all of which must be accounted for in any robust extraction model.
-
-\indent{\textbf{Ambiguities.}}
-The presence of overlapping elements—whether textual or graphical—can lead to a degradation in the extraction accuracy.
-This challenge is compounded when the overlap involves essential information, such as when the original price is partially obscured by a product image or strike-through marks.
-Furthermore, ambiguity in labeling and the context in which different pieces of information appear in the deal image can create difficulties in associating text with the correct object (e.g., associating a price with a product rather than the surrounding descriptive text).
-
-\subsection{Formal Approach}
+\subsection{Approaches to Information Extraction}
 Formally, the task of information extraction from a deal image can be defined as the identification of specific entities, including the product name, brand, original price, deal price, and unit.
@@
 \end{equation}
-where \(y_{i}\) represents the $i$-th entity in the deal image. In the following, the entities are defined as:
+where $y_{i}$ represents the $i$-th entity in the deal image. In the following, the entities are defined as:
 \begin{itemize}
-    \item \(y_{\text{product\_name}}\): The name of the product.
-    \item \(y_{\text{brand}}\): The brand of the product.
-    \item \(y_{\text{original\_price}}\): The original price of the product.
-    \item \(y_{\text{deal\_price}}\): The deal price of the product.
-    \item \(y_{\text{unit}}\): The unit of the product (e.g., weight, volume).
+    \item \code{$y_{\text{product\_name}}$}: The name of the product.
+    \item \code{$y_{\text{brand}}$}: The brand of the product.
+    \item \code{$y_{\text{original\_price}}$}: The original price of the product.
+    \item \code{$y_{\text{deal\_price}}$}: The deal price of the product.
+    \item \code{$y_{\text{unit}}$}: The unit of the product (e.g., weight, volume).
 \end{itemize}
 
-To extract these entities, one aims to learn a function \(f(\cdot)\) that maps an input image \(I\) to the desired outputs:
+To extract these entities, one aims to learn a function $f(\cdot)$ that maps an input image $I$ to the desired outputs:
 \begin{equation}
@@
 \end{equation}
-where \( I \) is the deal image, and \( \mathcal{Y} \) represents the extracted entities.
+where $ I $ is the deal image, and $ \mathcal{Y} $ represents the extracted entities.
 
-The choice of the function \( f(\cdot) \) is an architectural decision that depends on the specific requirements of the task, the nature of the data, the available resources, and the desired performance metrics.
+The choice of the function $ f(\cdot) $ is an architectural decision that depends on the specific requirements of the task, the nature of the data, the available resources, and the desired performance metrics.
 
-\subsection{Architectural Approaches to Information Extraction}
-- Classical methods: Rule-based, template-based
-- Traditional methods: Dividing into multi-stage
-    - 1. Text detection
-    - 2. Text recognition
-    - 3. Key-value pair extraction
-- OCR + LLM
-- End2End: Vision Encoder Decoder Model
-    - Donut 
-- E2E: LVLM
+Among the various existing architectural approaches to learn $ f(\cdot) $ for information extraction, several methodologies have been developed to address the inherent complexities in supermarket deal images.
+These methods can be categorized into classical approaches, multi-stage traditional models, hybrid OCR-LLM systems, and end-to-end deep learning frameworks.
+Each paradigm offers distinct advantages, and their applicability depends on computational resources, dataset characteristics, and performance requirements.
+
+\subsubsection{Traditional and Hybrid Approaches for Supermarket Leaflet Information Extraction}  
+Information extraction from supermarket leaflets has traditionally been approached through a pipeline of sequential sub-tasks, each addressed by specialized systems.
+These methods, while extensively studied and methodologically diverse, are typically divided into three main stages: text detection, text recognition, and key-value pair extraction.
+Although effective in certain scenarios, these approaches suffer from inherent limitations, including computational overhead, error propagation, and suboptimal performance on edge cases.
+Recent advancements in large language models (LLMs) have led to the development of hybrid OCR-LLM architectures, which combine the precision of optical character recognition (OCR) with the contextual reasoning capabilities of LLMs.
+Below, we formalize these approaches and discuss their strengths and limitations.
+
+Traditional architectures decompose the problem into independent sub-tasks, each handled by specialized models.
+While this modularity allows for targeted optimization, it introduces complexity and inefficiencies due to the lack of end-to-end training and error propagation across stages.
+
+The first stage, \emph{text detection}, involves identifying regions in the image $ I \in \mathbb{R}^{H \times W \times 3} $ that contain textual information.
+This is typically achieved using rule-based systems or neural networks designed for small object detection.
+The output is a set of $ M $ bounding boxes $ \{b_i\}_{i=1}^{M} $, where each $ b_i = (x_{\text{min}}, y_{\text{min}}, x_{\text{max}}, y_{\text{max}}) $ defines the coordinates of a text region.
+
+Each detected bounding box $ b_i $ is cropped and processed by a \emph{text recognition} model to convert the visual representation into a textual one.
+This task is challenging due to decoding errors caused by noisy backgrounds, stylized fonts, and ambiguous characters.
+Given the set of bounding boxes $ \{b_i\}_{i=1}^{M} $, the goal is to predict the corresponding textual entities $ \{t_i\}_{i=1}^{M} $:
+\begin{equation}
+\{t_i\}_{i=1}^{M} = \arg\max_{\{t_i\}_{i=1}^{M}} P(\{t_i\}_{i=1}^{M} | \{b_i\}_{i=1}^{M}).
+\end{equation}
+
+To use the recognized texts for information extraction, the final stage involves parsing the textual entities into structured outputs.
+This is typically achieved through rule-based systems or sequence-to-sequence models that generate key-value pairs from the recognized text.
+The output is a set of structured entities $ \{y_i\}_{i=1}^{N} $, where each $ y_i $ represents a specific entity (e.g., product name, price, unit).
+
+The rise of \emph{large language models }(LLMs) has enabled the development of hybrid OCR-LLM architectures, which combine the strengths of OCR tools with the linguistic and reasoning capabilities of LLMs.
+These approaches retain the traditional OCR pipeline for converting visual text into machine-readable form but leverage LLMs to enhance robustness through contextual reasoning and structured output generation.
+
+In a hybrid OCR-LLM system, the OCR stage processes the input image $ I $ to produce a set of unstructured text fragments $ T = \{t_i\}_{i=1}^{M} $ with associated spatial coordinates.
+These fragments are serialized into a prompt and fed into a pretrained LLM, which performs contextual parsing and generates some linguistic output that, in most cases, has to be somewhat postprocessed to extract the desired information.
+
+Hybrid OCR-LLM models offer several advantages over traditional pipelines.
+By integrating contextual reasoning, they reduce error propagation and improve robustness to noisy or ambiguous inputs.
+Additionally, the use of pretrained LLMs eliminates the need for task-specific training, simplifying system development.
+However, these models still rely on the accuracy of the OCR stage, and misrecognitions (e.g., "O" vs.
+"0") can propagate to the LLM.
+Furthermore, the computational cost of LLM inference can be prohibitive for large-scale applications.
+
+\subsubsection{End-to-End Models}  
+End-to-End (E2E) approaches unify document understanding by learning a direct mapping $ F: I \to \mathcal{D} $ and thus jointly optimize visual feature extraction and semantic parsing.
+We formalize two dominant paradigms: vision-encoder-decoder architectures and large vision-language models (LVLMs), which share foundational principles but diverge in scale and architectural complexity.
+
+Foundationally, all E2E models decompose into three components: a vision encoder, a representation projection, and a decoder.
+The vision encoder extracts hierarchical visual features $ \mathbf{Z} = \text{Enc}(I) $, which are then aligned with textual semantics through a representation projection.
+The decoder generates structured output $ \mathbf{Y} $ autoregressively.
+\figref{fig:e2e_arch} illustrates the unified architecture.
+
+\begin{figure}[h!]
+    \centering
+    \includegraphics[width=0.5\linewidth]{figures/vlm_arch.png}
+    \caption{End-to-End Vision-Encoder-Decoder Architecture.}
+    \label{fig:e2e_arch}
+\end{figure}
+
+\indent{\textbf{Donut \cite{kim2022}}.} This model employs a compact transformer-based encoder-decoder.
+Let $ I $ be partitioned into $ N $ patches $ \{\mathbf{p}_i\}_{i=1}^N $, each linearly projected to dimension $ d $.
+The used vision encoder $E$ computes an encoded representation mainly through:
+\begin{equation}
+Z = E(I) = \text{FFN}(\text{MSA}(X) + X) + \text{MSA}(X)
+\end{equation}  
+where $\text{MSA}$ denotes multi-head self-attention and $\text{FFN}$ a feed-forward network. The hierarchical structure captures local textural patterns as well as global layout cues.
+
+Subsequently, a transformer decoder generates tokens $ Y = (y_1, \dots, y_T) $ using cross-attention over $ Z $:  
+\begin{equation}
+P(y_t | y_{<t}, Z) = \text{Softmax}(\text{FFN}(\text{MSA}(Y) + Z)),
+\end{equation}  
+where $ Y $ is the token sequence and $ Z $ the encoded image features. The model is trained end-to-end with a maximum likelihood objective.
+
+\indent{\textbf{Large Vision-Language Models (LVLMs)}.} In the realm of upscaling language models into LLMs, computer vision utilizes this trend to process multimodal data.
+LVLMs like Llama 3.2 Vision \cite{touvron2023} scale this framework by integrating pretrained vision encoders with large language models (LLMs).
+These architectures utilize \emph{cross-modal projection}, which aligns visual features with the LLM's embedding space, and \emph{multimodal decoding}, which attends to both visual tokens and textual prompts.
+The LVLM's strength lies in zero-shot reasoning and leveraging pretrained knowledge for structured output generation.
+
+While smaller models like Donut offer efficiency and direct output generation, LVLMs provide zero-shot reasoning and open-world capabilities at increased computational cost.
 
 \subsection{Dataset Creation}
-Since there was no dataset to evaluate or train, a custom dataset was created by manually annotating a collection of supermarket deal images.
-The dataset includes images with diverse layouts, fonts, and colors to ensure robustness.
-Each image is annotated with bounding boxes for text regions and corresponding labels for product name, brand, original price, deal price, and unit.
-The dataset is split into training, validation, and test sets to facilitate model development and evaluation.
-% Table \ref{tab:dataset} provides an overview of the custom dataset and Figure \ref{fig:dataset} shows sample images with annotations.
-% TODO: Add table and figure
+Since the availability of German supermarket leaflet data is literally not findable, a custom dataset was created by manually annotating a collection of supermarket deal images.
+The dataset includes images from the most common supermarket chains, each with unique layout, fonts, and colors to, in general, ensure the highest diversity and robustness possible.
+Each image is annotated with a corresponding label file that includes the desired entities as well as the image identificator.
+The dataset is split into a training (\~ 80\%) and a validation set (\~ 20\%) for each model to be trained and evaluated on.
+Table \tabref{tab:ie_dataset} provides an overview of the dataset with the sample size for each entity and \figref{fig:ie_dataset_samples} shows some sample images with their annotations.
 
-\subsection{Optical Character Recognition}
-Optical Character Recognition (OCR) is a critical component in the information extraction pipeline.
-Several OCR solutions were evaluated to determine the most suitable one for our task.
-The evaluated OCR tools include Tesseract, EasyOCR, PaddleOCR, and DocTR.
-Each tool was assessed based on its accuracy, speed, and ability to handle diverse fonts and layouts.
+\begin{table}[h!]
+\centering
+\caption{Leaflet-IE Dataset}
+\label{tab:ie_dataset}
+\begin{tabular}{lc}
+\toprule
+Entity           & Sample Size \\
+\midrule
+\code{image\_id}        & 372  \\
+\code{brand}            & 357  \\
+\code{product\_name}    & 370  \\
+\code{original\_price}  & 286  \\
+\code{deal\_price}      & 372  \\
+\code{weight}           & 369  \\
+\bottomrule
+\end{tabular}
+\end{table}
 
-\subsection{Experiments}
-\indent{\textbf{Setup}.}
-The experiments were conducted to compare the performance of different OCR solutions and end-to-end models for information extraction.
-The evaluation metrics include precision, recall, and F1-score for each entity type (product name, brand, original price, deal price, and unit).
-The experiments were performed on the test set of the custom dataset.
+Even though the Leaflet-IE dataset is relatively small, the reader will be able to see that the dataset is sufficient to evaluate the performance of different IE appraoches as well as to train an competitive end-to-end model.
+However, as the reader may notice, the dataset is solely focused on single product deals at this point and explicitly does not include
 
-\indent{\textbf{Results}.}
-The results of the experiments indicate that the end-to-end models, such as the Vision Encoder Decoder Model (e.g., Donut) and Large Vision-Language Models (LVLM), outperform traditional OCR-based methods in terms of accuracy and robustness.
-The OCR + LLM approach also shows promising results, particularly in handling OCR errors and extracting key-value pairs.
+\begin{figure*}[h!]
+\centering
+\includegraphics[width=0.8\linewidth]{figures/ie_samples.png}
+\caption{Sample images with annotations from the custom dataset.}
+\label{fig:ie_dataset_samples}
+\end{figure*}
 
-\subsection{Evaluation}
-The evaluation of the models was conducted using standard metrics, including precision, recall, and F1-score.
-The comparison between LVLM, OCR + LLM, and Donut models highlights the strengths and weaknesses of each approach.
-The results demonstrate that end-to-end models provide superior performance in extracting structured information from supermarket deal images.
+\section{Experiments}
+
+The experiments aim to identify the most effective methodology for extracting structured information from supermarket leaflets by evaluating three candidate approaches: (1) Hybrid OCR + LLM pipelines, (2) end-to-end Vision-Encoder-Decoder models, and (3) Large Vision-Language Models (LVLMs).
+The evaluation is structured into four sequential phases to systematically assess performance and scalability.
+
+First, Plain Deal OCR Performance establishes a baseline by measuring the accuracy of standalone OCR systems in extracting textual content from leaflets, highlighting challenges such as font variability and noisy backgrounds.
+Second, OCR + LLM Performance evaluates the combined pipeline, where OCR outputs are processed by large language models to resolve ambiguities and extract structured information.
+Third, Donut Fine-Tuning Performance assesses the Vision-Encoder-Decoder model's effectiveness after fine-tuning on leaflet-specific data, focusing on its ability to handle multimodal inputs without intermediate OCR steps.
+Finally, the MAIN experiment conducts a comprehensive comparison of Hybrid OCR+LLM, Donut, and LVLM approaches, analyzing their accuracy, robustness, and computational efficiency in real-world leaflet data scenarios.
+
+\subsection{Implementation Details}
+The experiments were conducted on two distinct computational workstations - station 1 equipped with an NVIDIA RTX 4080 GPU and station 2 with an NVIDIA GTX 1080 GPU.
+Therefore, the experiments could be conducted in parallel, ensuring efficient model training and evaluation.
+
+The software stack includegraphics Python with PyTorch\footnote{\href{https://pytorch.org/}{https://pytorch.org/}} as the primary deep learning framework, HuggingFace Transformers \footnote{\href{https://huggingface.co/transformers/}{https://huggingface.co/transformers/}}
+for leveraging pre-trained models, ollama \footnote{\href{https://ollama.com/}{https://ollama.com/}}
+and lmstudio \footnote{\href{https://lmstudio.ai/}{https://lmstudio.ai/}} for large language models and large vision-language models, and OpenCV \footnote{\href{https://opencv.org/}{https://opencv.org/}} for image preprocessing and data augmentation, as well as various other libraries for data pre-and post-processing, visualization, data management and monitoring \footnote{The codebase is available at \href{https://github.com/ilyii/leaflets}{https://github.com/ilyii/leaflets}}.
+
+% SUB-STUDIES
+\subsection{Plain Deal OCR Performance}
+The aim of this experiment is to evaluate the performance of various OCR models in extracting text from supermarket leaflets.
+The evaluation focuses on the accuracies of the extracted entities from \tabref{tab:ie_dataset} and the impact of different normalization levels on the recognition performance.
+The results provide insights into the robustness and accuracy of different OCR models in handling the complexities of supermarket leaflet data.
+
+The most commonly used OCR models include:
+\begin{itemize}
+    \item Tesseract \footnote{\href{https://github.com/tesseract-ocr/tesseract}{https://github.com/tesseract-ocr/tesseract}},
+    \item EasyOCR \footnote{\href{https://github.com/JaidedAI/EasyOCR}{https://github.com/JaidedAI/EasyOCR}},
+    \item PaddleOCR \footnote{\href{https://github.com/PaddlePaddle/PaddleOCR}{https://github.com/PaddlePaddle/PaddleOCR}},
+    \item DocTR \footnote{\href{https://github.com/mindee/doctr}{https://github.com/mindee/doctr}}.
+\end{itemize}
+These models have been trained on a variety of datasets and are known for their robustness and accuracy in text extraction.
+Since it is likely that none of the OCR models have seen this data before, all 372 samples of the Leaflet-IE dataset were used for evaluation.
+While OCR alone is not capable of generating key-value mappings, the evaluation used a different set of metrics:
+
+\begin{itemize}
+    \item \textbf{Accuracy}: Measures whether the expected value is present in the OCR output.
+    \item \textbf{N-gram Accuracy}: Determines if an n-gram substring of the expected value exists in the OCR output, computed for $n \in \left[\frac{|v|}{2}, |v| - 1\right]$, where $|v|$ represents the string length of the ground truth entity value.
+\end{itemize}
+
+Given that language-specific OCR errors are common, the evaluation was conducted at different levels of normalization to improve comparability. The text normalization included the following layers:
+\begin{itemize}
+    \item \textbf{Level 1:} Text stripping and string conversion.
+    \item \textbf{Level 2:} Lowercasing and basic replacements.
+    \item \textbf{Level 3:} Use-case specific replacements.
+    \item \textbf{Level 4:} Punctuation and whitespace removal.
+\end{itemize}
+Each level includes the normalization steps of the previous levels.
+Therefore, the normalization procedure can be thought of as a gradual alignment of the OCR output to the ground truth to investigate the OCR model's robustness to different normalization levels.
+The reader is referred to \secref{app:ocr_normalization} for a detailed description of the normalization procedure.
+
+\indent{\textbf{Results}.} Figure \ref{fig:eval_ocr_accuracies} presents a comparative analysis of various OCR models and normalization levels based on per-entity accuracy.
+The results highlight several key trends regarding the recognition performance of different entities.
+
+\begin{figure*}
+    \begin{tabular}{cc}
+      \includegraphics[width=0.5\linewidth]{figures/accuracy_level_1.png} &   \includegraphics[width=0.5\linewidth]{figures/accuracy_level_2.png} \\
+    (a) Level 1 & (b) Level 2 \\[6pt]
+     \includegraphics[width=0.5\linewidth]{figures/accuracy_level_3.png} &   \includegraphics[width=0.5\linewidth]{figures/accuracy_level_4.png} \\
+    (c) Level 3 & (d) Level 4 \\[6pt]
+    \end{tabular}
+    \caption{Per-Entity Accuracy of OCR Models at Different Normalization Levels.}
+    \label{fig:eval_ocr_accuracies}
+    \end{figure*}
+
+In general, the OCR models exhibit superior performance in extracting words compared to numerical values.
+This discrepancy is particularly evident in entity-wise accuracy variations.
+At the baseline level (normalization level 1), the deal price entity consistently shows the lowest accuracy, whereas the brand entity achieves the highest.
+The accuracy of other entities varies significantly, with PaddleOCR, EasyOCR, and docTR displaying comparable performance, while Tesseract lags behind.
+
+The overall accuracy improves with increasing normalization levels, with normalization level 4 yielding the highest accuracy gains.
+At this level, Tesseract continues to struggle with deal price recognition, failing in over 90\% of cases.
+In contrast, the other OCR models achieve accuracies exceeding 70\% across nearly all entity types.
+
+Among the different entities, brand names are consistently recognized with the highest accuracy.
+This can be attributed to their simpler linguistic structure and distinct visual presentation, as brand names are often bolded or highlighted in promotional material.
+In contrast, product names tend to have more complex linguistic structures, making exact string matching more challenging.
+
+The recognition of unit information lags behind brand names but remains more accurate than deal prices.
+The reduced accuracy can be explained by the smaller font size of unit labels, their less prominent placement, and the high variability in unit measurements (e.g., "kg", "g", "Stück"), which complicates recognition.
+
+A significant gap is observed between deal price and original price accuracy.
+This can be attributed to the typographic differences between the two: deal prices are often emphasized using distinctive fonts and superscripted decimals, making them harder for OCR models to interpret correctly.
+In contrast, original prices are typically displayed in a standard inline format, which is easier to recognize.
+
+\begin{figure*}[h!]
+    \begin{tabular}{cc}
+      \includegraphics[width=0.5\linewidth]{figures/ngram_accuracy_level_1.png} &   \includegraphics[width=0.5\linewidth]{figures/ngram_accuracy_level_2.png} \\
+    (a) Level 1 & (b) Level 2 \\[6pt]
+        \includegraphics[width=0.5\linewidth]{figures/ngram_accuracy_level_3.png} &   \includegraphics[width=0.5\linewidth]{figures/ngram_accuracy_level_4.png} \\
+    (c) Level 3 & (d) Level 4 \\[6pt]
+    \end{tabular}
+    \caption{Per-Entity N-Gram Accuracy of OCR Models at Different Normalization Levels.}
+    \label{fig:eval_ocr_ngram_accuracies}
+\end{figure*}
+
+When evaluating n-gram accuracy per-entity in \figref{fig:eval_ocr_ngram_accuracies}, the results reveal a similar trend to per-entity accuracy.
+When comparing the OCR models, PaddleOCR consistently outperforms the other models especially in the price extractions while Tesseract lacks behind in all entities.
+
+The most significant observation is that the deal price and original price exhibit in lower normalization levels significantly worse accuracies.
+Since the length of n-gram sequences increase superlinearly, longer entity values, precisely the brand and product name, more likely achieve higher accuracies, which is also reflected in the results.
+
+At the highest normalization level, most models achieve 100\% or close to 100\% n-gram accuracy in the majority of entites.
+Additionally, here the discrepancy of Tesseract is most visible, where it cannot nearly achieve comparable scores.
+Also, one can observe that the unit entity drops significantly at level 4 across all models.
+This can be attributed to the high variability in unit measurements, which makes it challenging to match the exact n-grams.
+
+% EXPERIMENT: OCR+LLM
+\subsubsection{Hybrid-OCR+LLM Performance}
+
+In addition to evaluating the OCR capabilities, the performance of OCR models was assessed in conjunction with large language models (LLMs). The primary questions addressed were:
+\begin{itemize}
+    \item Which LLM is best suited to work with these OCR outputs?
+    \item Which OCR and LLM combination works best for information extraction (IE)?
+\end{itemize}
+
+All 372 samples of the Leaflet-IE dataset were used for evaluation.
+It is assumed that neither the OCR models nor the LLMs have previously encountered this data, similar to the OCR evaluation.
+Since the task is to extract structured information, the evaluation metrics were adapted to reflect the performance of the OCR-LLM combination in generating key-value mappings.
+The evaluation metrics include:
+\begin{itemize}
+    \item \textbf{Accuracy (Per Entity):} Measures the accuracy (of each extracted entity).
+    \item \textbf{Levenshtein Distance:} Calculates the distance between the prediction and the ground truth.
+\end{itemize}
+
+The LLMs were prompted to extract entities from the OCR output. The specific prompt used can be found in \secref{app:llm_prompt}.
+
+\paragraph{Models Evaluated:}
+\begin{itemize}
+    \item \textbf{Llama 3.1 [8b, Q4]}: \texttt{llama3.1\_8b} \cite{touvron2023},
+    \item \textbf{Qwen 2.5 [1.5b, Q8]}: \texttt{qwen2.5\_1.5b-instruct-q8\_0} \cite{qwen2025},
+    \item \textbf{Llama 3.2 [3b, Q8]}: \texttt{llama3.2\_3b-instruct-q8\_0} \cite{touvron2023},
+    \item \textbf{Qwen 2.5 [7b, Q4]}: \texttt{qwen2.5\_7b} \cite{qwen2025}.
+\end{itemize}
+where the LLM name and version is additionally specified through the model size (in billions of parameters) and the quantization level.
+
+To avoid confusion with the normalization used in the OCR experiment, the OCR results were kept raw, as normalization may remove valuable information.
+The LLMs are expected to handle such inconsistencies and errors in the input.
+Instead, here the entity values were evaluated in both raw form and with a normalization applied for the comparability between the LLM prediction and the ground truth value .
+The normalization procedure includes usual character replacements and filtering based on linguistic artifacts commonly encountered in OCR errors.
+The specific normalization procedure can be found in \secref{app:ocr_llm_normalization}.
+\paragraph{Results:}
+The entity-averaged accuracies and Levenshtein distances for the raw OCR output are depicted in Figures \ref{fig:eval_ocr_llm_accuracies_avg} and \ref{fig:eval_ocr_llm_levdist_avg}, respectively.
+
+\begin{figure*}[h!]
+    \centering
+    \includegraphics[width=0.8\linewidth]{figures/avg_accuracies.png}
+    \caption{Entity-Averaged Accuracy of LLM Models per Raw OCR Output. a: Llama 3.1 [8b, Q4], b: Qwen 2.5 [1.5b, Q8], c: Llama 3.2 [3b, Q8], d: Qwen 2.5 [7b, Q4].}
+    \label{fig:eval_ocr_llm_accuracies_avg}
+\end{figure*}
+
+The averaged accuracies reveal that a higher number of parameters is more beneficial for the LLMs in this task than a higher quantization level.
+Specifically, the Llama 3.1:8b and Qwen 2.5:7b models achieve significantly higher accuracy scores than their counterparts with a lower number of parameters.
+Qwen 2.5:1.5b in Q8 performs worse than Llama 3.2:3b in Q8, but Qwen 2.5:7b in Q4 is overall the best.
+These differences can be attributed to multiple factors, such as the pre-training data of the models, the model architecture, or the prompt used to extract the entities.
+DocTR and PaddleOCR achieve equal or better results than Tesseract and EasyOCR.
+Specifically, Tesseract consistently performs the worst among the evaluated models.
+
+\begin{figure*}[h!]
+    \centering
+    \includegraphics[width=0.7\linewidth]{figures/avg_levdistances.png}
+    \caption{Entity-Averaged Levenshtein Distance of OCR-LLM Models (Raw OCR Output). a: Llama 3.1 [8b, Q4], b: Qwen 2.5 [1.5b, Q8], c: Llama 3.2 [3b, Q8], d: Qwen 2.5 [7b, Q4].}
+    \label{fig:eval_ocr_llm_levdist_avg}
+\end{figure*}
+
+When regarding the levenshtein distances, the results show similar trends.
+DocTR delivers by far the best OCR input across all OCR models.
+Suprisingly, Tesseract achieves lower levenshtein distances than PaddleOCR and EasyOCR, with EasyOCR being the worst across all models.
+This could be due to the fact that Tesseract delivers more often slightly wrong but still similar results, while EasyOCR delivers less often wrong but more different results.
+The LLMs show similar trends as in the accuracy evaluation, but Llama 3.1:8b now slightly outperforms Qwen 2.5:7b.
+The differences between the LLMs are less pronounced than in the accuracy evaluation, which can be attributed to the unnormalized levenshtein distance calculation used.
+\secref{app:ocr_llm_results} provides further results on entity-level accuracies and levenshtein distances for each OCR-LLM combination.
+
+\subsection{Donut Fine-Tuning Performance}
+The experiment aims to evaluate the fine-tuning performance of the Vision Encoder-Decoder model, Donut, pretrained on the CORD dataset, to determine its capability in extracting end-to-end information from supermarket leaflet deal images.
+Conducted on an NVIDIA RTX 4080 (Station 1), the model has a vocabulary size of 57,580 and 201M parameters.
+The training configuration includes 70 epochs, validation performed every epoch, gradient clipping at 2.0, 800 training samples per epoch, a learning rate of 8e-6, batch sizes of 16 for both training and validation, 400 warmup steps, and 16-bit mixed precision.
+
+Results:
+
+\subsection{Comparison of Hybrid OCR+LLM, Donut, and LVLM}
+
+This section presents a comparative evaluation of a hybrid OCR+LLM pipeline against end-to-end models, specifically Donut and Large Vision-Language Models (LVLMs), for information extraction (IE) from supermarket leaflets.
+The assessment focuses on model performance using the best OCR+LLM configuration and two end-to-end approaches.
+
+\subsubsection{Experimental Setup}
+
+The evaluation framework was designed to compare the performance of three distinct model categories: OCR+LLM pipelines, end-to-end Vision Encoder-Decoder models, and large vision-language models (LVLMs).
+For the OCR+LLM approach, DocTR served as the OCR engine, paired with Qwen 2.5-7B and LLaMA 3.1-8B as the large language models, selected for their comparable performance.
+The Donut model, an end-to-end Vision Encoder-Decoder architecture optimized for document understanding, was included to assess its capabilities in handling structured document data.
+Additionally, MiniCPM-V \cite{yao2024} and LLaMA 3.2-Vision \cite{touvron2023} were chosen as representative LVLMs to evaluate their multimodal reasoning abilities.
+
+The evaluation was conducted on the Leaflet-IE validation subset, as Donut had already been trained on the training subset, ensuring a fair comparison across models.
+Performance was measured using two key metrics: (1) \textbf{Accuracy}, defined as the percentage of correctly extracted entity values, and (2) \textbf{Levenshtein Distance}, which quantifies the edit distance between predicted and ground truth values at the entity level.
+To maintain consistency, the same normalization approach employed in the OCR+LLM evaluation was applied uniformly to both model predictions and ground truth values.
+This setup ensured a rigorous and standardized comparison of model performance across the selected metrics.
+
+\paragraph{Per-Entity Accuracy and Levenshtein Distance}  
+The evaluation of per-entity accuracy and Levenshtein distance reveals distinct performance patterns across models, as illustrated in \figref{fig:eval_final_acc_raw} and \figref{fig:eval_final_levdis_raw}.
+Without normalization, the OCR+LLM pipeline performed significantly worse than Donut and LVLMs, achieving near 0\% accuracy for original and deal price entities, while LVLMs outperformed all models, particularly in price extraction, due to their ability to leverage spatial and contextual cues.
+Donut trailed closely but showed a notable drop in brand recognition accuracy.
+Levenshtein distance metrics mirrored these trends, with LVLMs and Donut exhibiting low distances, indicating high precision, while OCR+LLM struggled, especially with brand names, which consistently had the highest distances across models.
+
+\begin{figure*}[h!]
+    \centering
+    \includegraphics[width=0.8\linewidth]{figures/accuracies_raw.png}
+    \caption{Per-Entity Accuracy without normalization. a: Donut, b: docTR + Qwen 2.5 [7b, Q4], c: docTR + Llama 3.1 [8b, Q4], d: MiniCPM-V, e: Llama3.2-Vision.}
+    \label{fig:eval_final_acc_raw}
+\end{figure*}
+
+\begin{figure*}[h!]
+    \centering
+    \includegraphics[width=0.8\linewidth]{figures/levdistances_raw.png}
+    \caption{Per-Entity Levenshtein Distance without normalization. a: Donut, b: docTR + Qwen 2.5 [7b, Q4], c: docTR + Llama 3.1 [8b, Q4], d: MiniCPM-V, e: Llama3.2-Vision.}
+    \label{fig:eval_final_levdis_raw}
+\end{figure*}
+
+Normalization significantly improved results, as shown in \figref{fig:eval_final_acc_norm} and \figref{fig:eval_final_levdis_norm}, particularly for OCR+LLM, which saw its price detection accuracy surpass Donut in some cases.
+However, OCR+LLM remained inferior to LVLMs and Donut overall.
+Donut displayed stable and balanced accuracy across entities, while LVLMs, despite higher variance, maintained their lead, excelling in price extraction.
+Post-normalization, Levenshtein distances decreased across all models, with OCR+LLM showing the most substantial reduction.
+LVLMs achieved the lowest distances but with higher variance, whereas Donut demonstrated remarkable consistency.
+Despite these improvements, brand names continued to exhibit the highest Levenshtein distances, highlighting the persistent challenge of accurately extracting this entity even after normalization.
+These results, visualized in the referenced figures, underscore the strengths of LVLMs in leveraging multimodal cues and the robustness of Donut, while revealing the limitations of OCR+LLM pipelines in handling complex, noisy leaflet data.
+
+\begin{figure*}[h!]
+    \centering
+    \includegraphics[width=0.8\linewidth]{figures/accuracies_norm.png}
+    \caption{Per-Entity Accuracy with normalization. a: Donut, b: docTR + Qwen 2.5 [7b, Q4], c: docTR + Llama 3.1 [8b, Q4], d: MiniCPM-V, e: Llama3.2-Vision.}
+    \label{fig:eval_final_acc_norm}
+\end{figure*}
+
+\begin{figure*}[h!]
+    \centering
+    \includegraphics[width=0.8\linewidth]{figures/levdistances_norm.png}
+    \caption{Per-Entity Levenshtein Distance with normalization. a: Donut, b: docTR + Qwen 2.5 [7b, Q4], c: docTR + Llama 3.1 [8b, Q4], d: MiniCPM-V, e: Llama3.2-Vision.}
+    \label{fig:eval_final_levdis_norm}
+\end{figure*}
+
+\indent{\textbf{Dicussion.}} The evaluation highlights distinct strengths and limitations across the tested models.
+LVLMs emerged as the most effective for information extraction (IE) tasks, particularly when spatial and visual context is critical.
+However, their superior performance comes at the cost of significantly higher computational requirements, making them less practical for resource-constrained environments.
+Donut offers a compelling trade-off between accuracy and efficiency, demonstrating strong performance despite limited training resources.
+With further optimization, Donut has the potential to surpass LVLMs for this specific task, though its generalization ability remains narrower compared to LVLMs, which excel across a broader range of tasks.
+
+In contrast, the OCR+LLM pipeline proved considerably weaker than both LVLMs and Donut.
+This performance gap stems from several factors: (1) the lack of spatial and visual information, which limits its ability to resolve ambiguities; (2) error propagation from the OCR stage to the LLM, compounding inaccuracies; and (3) insufficient training data to achieve robust IE performance.
+Despite these limitations, OCR+LLM remains a viable option for scenarios with constrained computational resources and moderate task complexity, where its simplicity and lower resource demands may outweigh its performance drawbacks.
 
 \section{Application}
+
 \subsection{Database}
-
-\subsection{Optical Character Recognition}
-
-    \subsection{Experiments}
-    \indent{\textbf{Setup}.}
-    - Common OCR solutions: Tesseract, EasyOCR, PaddleOCR, DocTR
-    - Goal: Which OCR solution is the best for our task?
-    -
-
-    \subsection{Evaluation}
-    - LVLM, OCR+LLM, Donut
-    - OCR + LLM Vergleich
 
@@
     \subsection{Future Work}
-    ww
 
-% Bibliography entries for the entire Anthology, followed by custom entries
-%\bibliography{anthology,custom}
-% Custom bibliography entries only
 \bibliography{references}
 
+\appendix
+\section{Appendices}
+\subsection{OCR Evaluation: Normalization Procedure}
+\label{app:ocr_normalization}
+The procedure is implemented as a multi-level function, where each level applies increasingly rigorous transformations.
+Below, we provide a detailed explanation of the normalization steps and present the procedure in pseudocode.
+
+\begin{algorithm}[H]
+\caption{Text Normalization Function}
+\label{alg:normalization}
+\begin{algorithmic}[1]
+\Require Input text $text$, normalization level $level$ (default: 6)
+\Ensure Normalized text
+\State \textbf{Initialize}: If $text$ is empty, null, or an empty string, return an empty string.
+\If{$level \geq 1$}
+    \State Strip leading and trailing whitespace from $text$.
+\EndIf
+\If{$level \geq 2$}
+    \State Convert $text$ to lowercase.
+    \State Replace newline, tab, and carriage return characters with spaces.
+    \State Normalize German characters: "ö" $\rightarrow$ "o", "ä" $\rightarrow$ "a", "ü" $\rightarrow$ "u", "ß" $\rightarrow$ "ss".
+\EndIf
+\If{$level \geq 3$}
+    \State Replace hyphens and dashes  with spaces.
+    \State Remove all non-alphanumeric characters except periods and spaces.
+    \State Collapse multiple spaces into a single space.
+\EndIf
+\If{$level \geq 4$}
+    \State Remove all spaces and periods from $text$.
+\EndIf
+\State \textbf{Return} normalized $text$.
+\end{algorithmic}
+\end{algorithm}
+
+The normalization function is applied to both OCR outputs and ground truth texts before evaluation.
+By standardizing the text at various levels, we ensure that the evaluation metrics are robust to minor formatting differences and focus on the semantic accuracy of the OCR system.
+
+\subsection{LLM Prompt for Structured Information Extraction}
+\label{app:llm_prompt}
+
+This appendix details the prompt template used to guide the Large Language Model (LLM) in extracting structured information from OCR text.
+The prompt is designed to ensure consistent and accurate extraction of supermarket deal information, including fields such as brand name, product name, original price, reduced price, and weight.
+Below, we provide the system template, instructions, and an example of the prompt in action.
+
+The system template defines the context, extraction requirements, and instructions for the LLM. It is structured as follows:
+
+\begin{verbatim}
+**Context:**  
+You are an advanced language model specializing in extracting 
+structured information from OCR text. 
+Your task is to extract one supermarket deal from the given OCR result.
+
+**Extraction Requirements:**  
+- **Fields:**  
+  - "Marke": Brand name (if explicitly mentioned)  
+  - "Produktname": Product name  
+  - "Original Preis": Original price  
+  - "Reduzierter Preis": Reduced price  
+  - "Gewicht": Weight (if available; otherwise, use null)
+
+- **Instructions:**  
+  - Return a single JSON object containing exactly one deal.
+  - Use JSON only—no additional text.
+  - If a field is missing, assign a null value.
+  - Correct OCR errors such as missing decimals (e.g., "229" → "2.29"), 
+    incorrect spellings, and OCR noise.
+  - Use contextual cues (e.g., euro symbols) to infer and correct pricing.
+
+**Example:**  
+OCR Input:                     
+Dallmayr Prodomo Kaffee gemahlen 500g 1kg=51.73 Dallmayr -24% prodomo 5 69 UVP7,49
+
+JSON OUTPUT:
+{
+    "Marke": "Dallmayr",
+    "Produktname": "Prodomo Kaffee gemahlen",
+    "Original Preis": "UVP7,49",
+    "Reduzierter Preis": "3,99 €",
+    "Gewicht": null
+}
+
+IMPORTANT: Return the JSON object in the above format only once.
+\end{verbatim}
+
+The prompt is constructed by combining the system template with the OCR input provided by the user. The structure of the prompt is as follows:
+
+\begin{verbatim}
+messages = [
+    SYSTEM_TEMPLATE,
+    {
+        "role": "user",
+        "content": f"OCR Input: {ocr_res}\nJSON OUTPUT:"
+    }
+]
+\end{verbatim}
+
+Here, \texttt{ocr\_res} represents the OCR output text, which is dynamically inserted into the prompt.
+
+\subsection{OCR + LLM Evaluation: Normalization Procedure}
+\label{app:ocr_llm_normalization}
+
+This appendix describes the normalization procedure applied to LLM-extracted data during evaluation.
+The normalization process ensures consistency by standardizing text formats, removing special characters, and correcting common OCR errors.
+Below, we provide a detailed explanation of the procedure and present the implementation in pseudocode.
+
+The normalization procedure is implemented as a Python function that performs the following steps:
+
+\begin{algorithm}[H]
+\caption{Text Normalization Procedure}
+\label{alg:final_normalization}
+\begin{algorithmic}[1]
+\Require Input text $text$
+\Ensure Normalized text
+\State \textbf{Initialize}: Define a dictionary $REPLACEMENTS$ for character replacements.
+\State $REPLACEMENTS \gets \{
+    \text{"ä"} \rightarrow \text{"a"}, \text{"ö"} \rightarrow \text{"o"}, \text{"ü"} \rightarrow \text{"u"}, 
+    \text{"ß"} \rightarrow \text{"ss"}, \text{","} \rightarrow \text{"."}, \text{"€"} \rightarrow \text{""}, 
+    \text{"ô"} \rightarrow \text{"o"}, \text{"é"} \rightarrow \text{"e"}, \text{"ç"} \rightarrow \text{"c"}, 
+    \text{"è"} \rightarrow \text{"e"}, \text{"à"} \rightarrow \text{"a"}, \text{"ê"} \rightarrow \text{"e"}, 
+    \text{"â"} \rightarrow \text{"a"}, \text{"û"} \rightarrow \text{"u"}, \text{"î"} \rightarrow \text{"i"}, 
+    \text{"ë"} \rightarrow \text{"e"}, \text{"ï"} \rightarrow \text{"i"}, \text{"œ"} \rightarrow \text{"oe"}, 
+    \text{"æ"} \rightarrow \text{"ae"}, \text{"ù"} \rightarrow \text{"u"}
+\}$
+\For{each $(key, value)$ in $REPLACEMENTS$}
+    \State Replace occurrences of $key$ with $value$ in $text$.
+\EndFor
+\State Filter $text$ to retain only alphanumeric characters, periods, and spaces.
+\State Remove all whitespace from $text$.
+\State Convert $text$ to lowercase.
+\State \textbf{Return} normalized $text$.
+\end{algorithmic}
+\end{algorithm}
+
+\subsection{OCR + LLM Evaluation: Entity-specific results per OCR model}
+\label{app:ocr_llm_results}
+
+This section collects further detailed results for the OCR + LLM evaluation for interested readers.
+The results are presented in the form of per-entity accuracies and Levenshtein distances for each OCR model used in the evaluation.
+The figures provide insights into the performance of each OCR model in extracting structured information from supermarket leaflets, highlighting the strengths and weaknesses of individual models across different entities.
+
+\begin{figure*}[h!]
+    \begin{tabular}{cc}
+      \includegraphics[width=0.5\linewidth]{figures/doctr_ocr_accuracies.png} &   \includegraphics[width=0.5\linewidth]{figures/tesseract_ocr_accuracies.png} \\
+    docTR & Tesseract \\[6pt]
+        \includegraphics[width=0.5\linewidth]{figures/easyocr_ocr_accuracies.png} &   \includegraphics[width=0.5\linewidth]{figures/ppocr_ocr_accuracies.png} \\
+    EasyOCR & PaddleOCR \\[6pt]
+    \end{tabular}
+    \caption{LLM accuracies per Entity for different OCR models. a: Llama 3.1 [8b, Q4], b: Qwen 2.5 [1.5b, Q8], c: Llama 3.2 [3b, Q8], d: Qwen 2.5 [7b, Q4].}
+    \label{fig:eval_ocr_llm_accuracies}
+\end{figure*}
+
+\begin{figure*}[h!]
+    \begin{tabular}{cc}
+        \includegraphics[width=0.5\linewidth]{figures/doctr_ocr_levdistances.png} &   \includegraphics[width=0.5\linewidth]{figures/tesseract_ocr_levdistances.png} \\
+    docTR & Tesseract \\[6pt]
+        \includegraphics[width=0.5\linewidth]{figures/easyocr_ocr_levdistances.png} &   \includegraphics[width=0.5\linewidth]{figures/ppocr_ocr_levdistances.png} \\
+    EasyOCR & PaddleOCR \\[6pt]
+    \end{tabular}
+    \caption{LLM Levenshtein Distances per Entity for different OCR models. a: Llama 3.1 [8b, Q4], b: Qwen 2.5 [1.5b, Q8], c: Llama 3.2 [3b, Q8], d: Qwen 2.5 [7b, Q4].}
+    \label{fig:eval_ocr_llm_levdistances}
+\end{figure*}
+
 \end{document}

### 2025-02-22 src/extraction/evaluation/evaluate_ocr-llm_donut_lvlm.py

@@ -156,7 +156,7 @@ def final_normalize_text(text):
 def final_normalize_prices(price_text):
     # Replace commas with dots
     price_text = price_text.replace(",", ".")
-    # Only keep numbers and dots
+    # # Only keep numbers and dots
     price_text = "".join([char for char in price_text if char.isdigit() or char == "."])
     
     return price_text
@@ -474,47 +474,82 @@ def main(level=1,
     }
 
     def visualize_accuracies_comparsion(model_list, accuracies_results_dict, outname):
-        sns.set_theme(style="whitegrid")
+        FONTSIZE = 28
+        # Set plot style for scientific papers
+        plt.style.use('seaborn-v0_8-paper')
+        plt.rcParams.update({
+            'font.size': FONTSIZE,
+            'font.family': 'serif',
+            'font.serif': 'Palatino',
+            'axes.titlesize': 'medium',
+            'figure.titlesize': 'medium',
+            'text.usetex': True,
+            'text.latex.preamble': r'\usepackage{amsmath}\usepackage{amssymb}\usepackage{siunitx}[=v2]',
+            'figure.figsize': (16, 9),
+            'xtick.labelsize': FONTSIZE,
+            'ytick.labelsize': FONTSIZE,
+            'legend.fontsize': FONTSIZE,
+            'figure.dpi': 300
+        })
         data = []
         for model in model_list:
             for entity, acc in accuracies_results_dict[model].items():
                 data.append((model, entity, np.mean(acc)))
         df = pd.DataFrame(data, columns=["Model", "Entity", "Accuracy"])
-        fig, ax = plt.subplots(figsize=(14, 10))
+        fig, ax = plt.subplots()
         sns.barplot(data=df, x="Model", y="Accuracy", hue="Entity", ax=ax, palette="Set2")
-        ax.set_title("Accuracy per Model and Entity", fontsize=14, fontweight="bold")
-        ax.set_ylabel("Accuracy", fontsize=12)
-        ax.set_xlabel("Models", fontsize=12)
-        ax.set_xticklabels([MODELS[model] for model in model_list], ha="center", fontsize=10)
+        ax.set_ylabel("Accuracy", fontsize=FONTSIZE)
+        ax.set_xlabel("Models", fontsize=FONTSIZE)
[…]

### 2025-02-22 src/extraction/evaluation/evaluate_ocr.py

@@ -244,9 +244,27 @@ def evaluate(pred_df, target_df):
     return accuracies, ngram_accuracies, sample_sizes
 
 
+
 def visualize_accuracies(accuracies, out_name):
-    sns.set_theme(style="whitegrid")
-    
+    FONTSIZE = 28
+    # Set plot style for scientific papers
+    plt.style.use('seaborn-v0_8-paper')
+    plt.rcParams.update({
+        'font.size': FONTSIZE,
+        'font.family': 'serif',
+        'font.serif': 'Palatino',
+        'axes.titlesize': 'medium',
+        'figure.titlesize': 'medium',
+        'text.usetex': True,
+        'text.latex.preamble': r'\usepackage{amsmath}\usepackage{amssymb}\usepackage{siunitx}[=v2]',
+        'figure.figsize': (16, 9),
+        'xtick.labelsize': FONTSIZE,
+        'ytick.labelsize': FONTSIZE,
+        'legend.fontsize': FONTSIZE,
+        'figure.dpi': 300
+    })
+
+    # Prepare data
     data = []
     for model, entity_acc in accuracies.items():
         for entity, acc in entity_acc.items():
@@ -255,24 +273,26 @@ def visualize_accuracies(accuracies, out_name):
     df = pd.DataFrame(data, columns=["Model", "Entity", "Accuracy"])
     
     # Create grouped bar plot
-    fig, ax = plt.subplots(figsize=(14, 10))
+    fig, ax = plt.subplots(figsize=(16,9))
     sns.barplot(data=df, x="Model", y="Accuracy", hue="Entity", ax=ax, palette="Set2")
     
-    ax.set_title("Accuracy per Model and Entity", fontsize=14, fontweight="bold")
-    ax.set_ylabel("Accuracy", fontsize=12)
-    ax.set_xlabel("Models", fontsize=12)
+    # Set titles and labels
+    # ax.set_title("Accuracy per Model and Entity", fontsize=12)
+    ax.set_ylabel("Accuracy", fontsize=FONTSIZE)
+    ax.set_xlabel("OCR Models", fontsize=FONTSIZE)
+
     # Update xtick labels
-    ax.set_xticklabels([MODELS[model] for model in df["Model"].unique()], ha="center", fontsize=10)
+    ax.set_xticklabels([MODELS[model] for model in df["Model"].unique()], ha="center", fontsize=FONTSIZE)
 
     # Update legend labels
[…]

### 2025-02-22 src/extraction/evaluation/evaluate_ocr_llm.py

@@ -363,7 +363,7 @@ def evaluate_entity_per_llm(pred_df, target_df, preprocessing_level=3):
                         pred_value = ""
                     pred_value = final_normalize_text(str(pred_value))
                     
-                    print("Target:", target_value, "Pred:", pred_value)
+                    # print("Target:", target_value, "Pred:", pred_value)
                     accuracies[model][entity].append(1 if pred_value == target_value else 0)
                     levdistances[model][entity].append(jellyfish.levenshtein_distance(str(pred_value), str(target_value)))
                 else:
@@ -374,7 +374,22 @@ def evaluate_entity_per_llm(pred_df, target_df, preprocessing_level=3):
 
 
 def visualize_accuracies(accuracies, outname):
-    sns.set_theme(style="whitegrid")
+    FONTSIZE = 28
+    plt.style.use('seaborn-v0_8-paper')
+    plt.rcParams.update({
+        'font.size': FONTSIZE,
+        'font.family': 'serif',
+        'font.serif': 'Palatino',
+        'axes.titlesize': 'medium',
+        'figure.titlesize': 'medium',
+        'text.usetex': True,
+        'text.latex.preamble': r'\usepackage{amsmath}\usepackage{amssymb}\usepackage{siunitx}[=v2]',
+        'figure.figsize': (4.9, 3.5),
+        'xtick.labelsize': FONTSIZE,
+        'ytick.labelsize': FONTSIZE,
+        'legend.fontsize': FONTSIZE,
+        'figure.dpi': 300
+    })
     
     data = []
     for model, entity_acc in accuracies.items():
@@ -384,29 +399,45 @@ def visualize_accuracies(accuracies, outname):
     df = pd.DataFrame(data, columns=["Model", "Entity", "Accuracy"])
     
     # Create grouped bar plot
-    fig, ax = plt.subplots(figsize=(14, 10))
+    fig, ax = plt.subplots(figsize=(16,9))
     sns.barplot(data=df, x="Model", y="Accuracy", hue="Entity", ax=ax, palette="Set2")
     
     # ax.set_title("Accuracy per Model and Entity", fontsize=14, fontweight="bold")
-    ax.set_ylabel("Accuracy", fontsize=12)
-    ax.set_xlabel("Models", fontsize=12)
+    ax.set_ylabel("Accuracy", fontsize=FONTSIZE)
+    ax.set_xlabel("Models", fontsize=FONTSIZE)
[…]

### 2025-02-22 paper/main_ilyi.tex
Pre-final paper version of ilyi.

@@
 Conducted on an NVIDIA RTX 4080 (Station 1), the model has a vocabulary size of 57,580 and 201M parameters.
-The training configuration includes 70 epochs, validation performed every epoch, gradient clipping at 2.0, 800 training samples per epoch, a learning rate of 8e-6, batch sizes of 16 for both training and validation, 400 warmup steps, and 16-bit mixed precision.
+The training configuration includes 10 epochs, validation performed every epoch, gradient clipping at 2.0, 800 training samples per epoch, a learning rate of 8e-6, batch sizes of 16 for both training and validation, 400 warmup steps, and 16-bit mixed precision.
 
-Results:
+\indent{\textbf{Results}.} The training and validation losses of Donut during fine-tuning are depicted in \figref{fig:donut_loss}.
+The training loss decreases rapidly, while the validation loss remains high, indicating overfitting.
+The overfitting is likely due to the limited number of leaflet layouts in the training data, which restricts the model's ability to generalize to unseen layouts.
+This issue is visually less pronounced, as the text is relatively consistent across leaflets, but textually, the model struggles to generalize due to the diverse language and layout variations.
+
+\begin{figure*}
+    \begin{tabular}{cc}
+    \includegraphics[width=0.5\linewidth]{figures/donut_train_loss.png} &   \includegraphics[width=0.5\linewidth]{figures/donut_val_loss.png} \\
+    (a) Training Loss & (b) Validation Loss \\[6pt]
+    % \caption{Training and Validation Loss of Donut during Fine-Tuning.}
+    \label{fig:donut_loss}
+    \end{tabular}
+\end{figure*}
 

### 2025-02-23 paper/main_ilyi.tex
Add deal detection and application to paper

@@
 % Change to "preprint" to generate a non-anonymous version with page numbers.
-\usepackage{lib}
+\RequirePackage{lib}
 
 % Standard package includes
-\usepackage{times}
-\usepackage{latexsym}
+\RequirePackage{times}
+\RequirePackage{latexsym}
 
 % For proper rendering and hyphenation of words containing Latin characters (including in bib files)
-\usepackage[T1]{fontenc}
+\RequirePackage[T1]{fontenc}
 
 % This assumes your files are encoded as UTF8
-\usepackage[utf8]{inputenc}
+\RequirePackage[utf8]{inputenc}
 
-\usepackage{microtype}
+\RequirePackage{microtype}
 
-\usepackage{inconsolata}
+\RequirePackage{inconsolata}
 
-\usepackage{graphicx}
-\usepackage{amsmath}
-\usepackage{multirow}
-\usepackage{booktabs}
-\usepackage{amssymb}
-\usepackage{hyperref}
-\usepackage{subfig}
+\RequirePackage{graphicx}
+\RequirePackage{amsmath}
+\RequirePackage{multirow}
+\RequirePackage{booktabs}
+\RequirePackage{amssymb}
+\RequirePackage{hyperref}
+\RequirePackage{subfig}
 
-\usepackage{algorithm}
-\usepackage{algpseudocode}
-\usepackage{verbatim}
+\RequirePackage{algorithm}
+\RequirePackage{algpseudocode}
+\RequirePackage{verbatim}
 
@@
 \indent{\textbf{Deal Detection}.}
+There are no direct approaches for detecting deals, including product image, price, name and more, in supermarket leaflets.
+However, the detection of specific elements in documents, or more generally, the detection of objects in images, is a widely researched area.
+When it comes to just the actual detection of these elements without understanding the semantic meaning, models such as YOLO or Faster R-CNN prove to be effective.
+These models are able to recognize objects in images and mark them with bounding boxes and further classify them.
+But because there is no direct research on the detection of deals in supermarket leaflets, the research has to be done in this area.
 
@@
 This multifaceted nature demands architectures that jointly optimize for visual-textual alignment, error-resilient parsing, and contextual plausibility.
+
 \section{Deal Detection}
-    \subsection{Datasets}
+Detecting deals within supermarket leaflets is a crucial step in the process of extracting structured  data.
+The ultimate end-to-end goal of deal detection is to accurately identify and separate individual deals from digital supermarket leaflets, enabling further analysis and integration into a structured database for an application.
+This step is fundamental for creating a comprehensive, queryable system that allows users to compare deals across different retailers efficiently.
+Directly detecting deals within leaflets is necessary because supermarket deals are not standardized, and each leaflet can contain multiple overlapping deals, diverse layouts, and varying fonts, making simple text-based extraction approaches insufficient.
+
+\subsection{Dataset}
+An approach to obtaining deal data would be direct web scraping from supermarket websites, as these days they present their deals digitally in a structured way.
+However, this method is highly error-prone and difficult to generalize due to the distinct and frequently changing layouts of different supermarket websites.
+Additionally, many retailers do not provide direct, easily scrappable structured deal data.
+Instead, an alternative source has been identified.
+Websites that aggregate and upload full promotional leaflets from various German supermarkets on a weekly basis.
+These leaflets provide a more standardized input format and can be systematically downloaded using an automated script.
+
+The collected dataset consists of approximately 13,000 images from a diverse range of supermarket chains, including well-known retailers such as Penny, Aldi, and Kaufland, as well as less conventional ones like Metro.
+The primary focus remains on supermarkets that sell groceries and drugstore products, as these are the most relevant for the intended applications.
+Each leaflet page contains multiple distinct offers, which must be individually detected.
+This is achieved through object detection techniques, which can either utilize bounding boxes or instance segmentation.
+While bounding box detection provides a straightforward way to localize deals, it often struggles with overlapping offers, leading to incorrect classifications.
+Instance segmentation is therefore the preferred approach, as it allows for more precise extraction of deal regions without interference from neighboring offers.
+Deals in the dataset are categorized into four main classes:
+
+\begin{itemize}
+    \item Standard Deal: A regular product discount.
+    \item Product Category Deal: A discount on an entire product category (e.g., "20\% off all canned goods").
+    \item Coupon Deal: Special offers requiring the use of coupons (e.g., Payback).
+    \item Miscellaneous: Deals outside the primary categories, such as travel promotions.
+\end{itemize}
+
+\begin{figure*}[h!]
+    \centering
+    \includegraphics[width=0.7\linewidth]{figures/deal_detection/dataset_count.png}
+    \caption{Distribution of labeled leaflet pages and deals in training and validation sets.}
+    \label{fig:ddetect_dataset_count}
+\end{figure*}
+
+The primary focus is on standard deals, as they are the most common and directly useful for consumers.
+No publicly available dataset fully aligns with this task as it involves both instance segmentation and deal categorization, specifically in the context of German supermarkets.
+So, a subset of the collected pages was manually annotated.
+The result is a dataset of 672 annotated leaflet pages, with 4,675 individual deals in training and 75 pages with 523 deals in the validation set as shown in \figref{fig:ddetect_dataset_count}.
+In cases where no overlapping elements were present, bounding boxes were used.
+For overlapping offers, instance segmentation masks were created.
+Depending on the training requirements, annotations can be converted between bounding boxes and segmentation masks, although segmentation masks provide a more granular representation.
+
+\begin{figure*}[h!]
+    \centering
+    \includegraphics[width=0.6\linewidth]{figures/deal_detection/bbox_page.png}
+    \caption{Bounding box detection results on a leaflet page resulting in overlapping bounding boxes.}
+    \label{fig:ddetect_bbox_page}
+\end{figure*}
+
+\begin{figure*}[h!]
+    \centering
+    \includegraphics[width=0.6\linewidth]{figures/deal_detection/mask_page.png}
+    \caption{Instance segmentation results on a leaflet page showing precise deal separation.}
+    \label{fig:ddetect_mask_page}
+\end{figure*}
+
 \subsection{Model}
+Object detection and segmentation tasks require identifying objects within an image while determining their locations.
+The simplest form of image analysis, image classification, assigns a single label to an entire image, providing no information about object positions.
+However, multiple deal detection in supermarket leaflets demands the identification of multiple deals, whose number is unknown beforehand, along with their precise locations to extract them later.
+
+Object detection models can be broadly categorized into multi-stage (multi-shot) detectors and single-stage (single-shot) detectors.
+Multi-stage detectors, such as the R-CNN family (R-CNN, Fast R-CNN, Faster R-CNN, Mask R-CNN), follow a sequential process.
+First, they generate a set of region proposals, indicating potential object locations.
+These proposals are then classified in a second stage.
+While this method achieves high accuracy, it introduces significant computational overhead.
+Earlier versions, such as R-CNN, even relied on separate, non-learnable algorithms for proposal generation.
+Faster R-CNN improved efficiency by integrating the Region Proposal Network (RPN) directly into the model, eliminating the need for external proposal algorithms.
+However, even this approach remains computationally demanding.
+In contrast, single-stage detectors, such as YOLO (You Only Look Once), perform detection in a single forward pass, predicting object locations and classifications simultaneously.
+This significantly reduces inference time, making these models well-suited for real-time applications.
+YOLO, in particular, has established itself as one of the most widely used architectures due to its speed and competitive accuracy.
+Given the requirement of processing thousands of leaflet pages efficiently, a single-stage detector was chosen for deal detection, with a particular focus on YOLO-based architectures.
+
+The YOLO model follows a grid-based detection approach, where the input image is divided into an SxS grid.
+Each grid cell is processed for predicting objects whose centers fall within it.
+Instead of relying on separate region proposal mechanisms, YOLO processes the image in a single forward pass, directly predicting bounding box coordinates, confidence scores, and class probabilities per grid cell.
+The bounding boxes are parameterized by their center coordinates, width, and height, while the confidence scores indicate the model’s certainty that a given bounding box contains an object.
+The class probabilities further specify which category the detected object belongs to.
+Traditional object detection frameworks like YOLO produce bounding boxes that encapsulate detected objects in rectangular shapes.
+However, supermarket leaflets contain deals that frequently overlap or feature irregular layouts, making bounding box-based detection less effective.
+Instance segmentation extends YOLO by incorporating an additional segmentation head that predicts pixel-level masks for each detected object.
+This approach enables the model to distinguish individual deals more precisely, reducing the risk of grouping multiple offers within a single bounding box.
+The segmentation mechanism operates by first detecting objects using the standard YOLO pipeline.
+Once a bounding box is identified, the model refines its prediction by generating a binary mask that determines which pixels within the bounding box belong to the detected object.
+The segmentation head shares feature representations with the object detection components, ensuring efficient training and inference.
+This method enhances the model’s ability to isolate individual deals even in cluttered layouts, making it particularly suited for supermarket leaflets where offers frequently overlap or appear with complex backgrounds.
+
 \subsection{Experiments}
+Evaluating the performance of instance segmentation models requires an analysis of how well detected objects align with ground-truth annotations.
+The primary metric used in this assessment is **Mean Average Precision (mAP)**, which quantifies detection accuracy at different levels of overlap between predicted and actual objects.
+The core component of mAP is Intersection over Union (IoU).
+IoU is defined as the ratio of the intersection area between the predicted and ground-truth segmentation masks to their union.
+A higher IoU indicates a better match between the prediction and the actual object, while a lower IoU suggests that the detected region is misaligned or includes excessive background.
+In the case of bounding boxes, IoU is calculated based on the overlap of rectangular regions, whereas for instance segmentation, it is computed on a pixel level, capturing the true shape of the detected objects.
+To evaluate model performance, different IoU thresholds are applied.
+A commonly used metric is mAP@50, which considers a detection correct if the IoU between the predicted and ground-truth mask exceeds 50\%.
+This threshold provides insight into how well a model identifies objects in general but does not strictly enforce precision in localization.
+A more comprehensive metric is mAP@50-95, which averages precision across multiple IoU thresholds, ranging from 50\% to 95\% in increments of 5\%.
+This approach penalizes models that fail to produce accurate segmentations and is particularly useful for assessing how well the model distinguishes closely packed or irregularly shaped deals.
+
+\begin{figure*}[h!]
+    \centering
+    \begin{tabular}{cc}
+    \includegraphics[width=0.5\linewidth]{figures/deal_detection/map50_all_yolo.png} &   \includegraphics[width=0.5\linewidth]{figures/deal_detection/map50_95_all_yolo.png} \\
+    (a) Results for mAP50 & (b) Results for mAP50-95 \\[2pt]
+    \end{tabular}
+    \caption{Performance comparison of YOLOv8 and YOLOv11 models on the deal detection validation set.}
+    \label{fig:all_yolo_results}
+\end{figure*}
+
+The first set of experiments focused on comparing different YOLO variants trained on the dataset.
+Each model was trained for 20 epochs without additional data augmentation.
+The results, shown in Figure \ref{fig:all_yolo_results} (a), present the mAP50 (mask) scores for YOLOv8 and YOLOv11 in their small, medium, and large configurations.
+The findings indicate that the smallest version of YOLOv8 achieved the highest validation mAP50, outperforming larger models in this setting.
+A second analysis, visualized in Figure \ref{fig:all_yolo_results} (b), examines mAP50-95 scores for the same models, reinforcing the observation that a lightweight YOLO model is sufficient for this particular task.
+The lower performance of larger models suggests that the dataset’s structure, with relatively uniform layouts, does not require highly complex architectures to achieve strong results.
+
+\begin{figure*}[h!]
+    \centering
+    \begin{tabular}{cc}
+    \includegraphics[width=0.5\linewidth]{figures/deal_detection/map50_yolo8.png} &   \includegraphics[width=0.5\linewidth]{figures/deal_detection/map50_95_yolo8.png} \\
+    (a) Results for mAP50 & (b) Results for mAP50-95 \\[2pt]
+    \end{tabular}
+    \caption{Performance comparison of YOLOv8s models with and without data augmentation on the deal detection validation set.}
+    \label{fig:yolo8_results}
+\end{figure*}
+
+Following this baseline evaluation, additional experiments investigated the impact of data augmentation on segmentation performance.
+Various augmentation strategies were applied, including translation, scaling, horizontal flipping, and color transformations.
+The goal was to determine whether these transformations improved the model’s ability to generalize across different leaflet layouts.
+Each augmented model was trained for ten additional epochs, and the results are displayed in Figure \ref{fig:yolo8_results}.
+While certain augmentation techniques led to slight improvements in segmentation accuracy, particularly for models trained with random translations, the overall best-performing model remained the one trained without any augmentation.
+This outcome suggests that the dataset already contains sufficient variation to ensure robust generalization without the need for extensive artificial augmentations.
+
+The final model selection was based on the combination of high segmentation accuracy and computational efficiency.
+Given the results, YOLOv8s was chosen as the preferred model, as it consistently outperformed more complex variants while maintaining a lower computational cost.
+The model’s ability to detect deals with high precision makes it a strong candidate for further applications.
+And this is particularly important because everything else builds on it.
 
@@
 \section{Application}
+The ability to detect deals from a wide range of supermarket leaflets provides the foundation for extracting structured information and building a centralized deal database.
+If all components, from deal detection to information extraction, function reliably, this enables the creation of a comprehensive repository containing deals from various supermarkets, based solely on the content of their weekly unstructured leaflets.
+Such a structured database allows for numerous applications, including price trend analysis, intelligent shopping list generation and deal comparison across stores.
+The immediate objective of this project was to develop a system that could automatically collect, process and present extracted deals in a structured manner.
+The resulting application is designed to scrape supermarket leaflets weekly, detect deals using the trained YOLO-based model and extract relevant metadata, including product names and prices.
+These extracted deals are then stored in a structured format within a database and made accessible through a web-based interface.
 
 \subsection{Database}
+\begin{figure*}[h!]
+    \centering
+    \includegraphics[width=0.8\linewidth]{figures/application/db_uml.png}
+    \caption{Database schema for storing metadata for supermarket leaflets and extracted deals.}
+    \label{fig:application_db_uml}
+\end{figure*}
+For storing the extracted deals, a lightweight and efficient solution was required.
+SQLite was chosen due to its simplicity and fast performance, making it well-suited for handling the structured but relatively small-scale dataset.
+After several weeks of scraping supermarket leaflets, the dataset grew to include 540 leaflets from 20 different supermarkets.
+The database is structured into three primary tables (cf.
+Figure \ref{fig:application_db_uml}): one for supermarket metadata, one for storing the leaflets and one containing the extracted deals.
+The total number of extracted deals in the database adds up to 47,829.
+Among these, the vast majority (46,869) are classified as standard deals, while 607 fall under product category deals, 144 correspond to coupons and 208 belong to miscellaneous categories.
+Since the structure and content of non-standard deals often differ significantly from regular deals featuring loyalty points, bulk discounts, or percentage-based reductions across entire product groups, the primary focus remains on standard deals.
+By structuring the data efficiently, the database serves as a robust backend for the subsequent web application, facilitating fast queries and scalable deal retrieval.
 
-\section{Application}
-    \section{Database}
-    \section{Front End / Webapp}
+\subsection{Web User Interface}
+\begin{figure*}[h!]
+    \centering
+    \includegraphics[width=0.8\linewidth]{figures/application/deals_overview.png}
+    \caption{Web-based application interface for browsing all extracted supermarket deals with search and filter functionality.}
+    \label{fig:application_web_overview}
+\end{figure*}
+
+Building on the database, a web-based application was developed to provide users with an interactive way to explore supermarket deals, which is shown in Figure \ref{fig:application_web_overview}.
+The core functionality centers around an intuitive search system that allows users to find deals based on specific product names.
+Additionally the interface supports filtering options, enabling users to refine searches by supermarket chain or deal validity period.
+Each deal is displayed with its corresponding image snippet, extracted metadata, and pricing information, making it easy to compare offers across different retailers.
+
+\begin{figure*}[h!]
+    \centering
+    \begin{tabular}{cc}
+    \includegraphics[width=0.45\linewidth]{figures/application/leaflet_segmentations.png} &   \includegraphics[width=0.45\linewidth]{figures/application/single_deal.png} \\
+    (a) Interactive leaflet segmentation & (b) Detailed view of a single deal \\[2pt]
+    \end{tabular}
+    \caption{Additional features of the web application, including interactive uploading of pdf leaflets and detailed deal views by clicking on individual deals.}
+    \label{fig:application_combined}
+\end{figure*}
+
+Beyond static deal browsing, the application also incorporates an upload feature that enables users to submit entire supermarket leaflets for processing.
+When a leaflet is uploaded, the system applies the full processing pipeline, from deal detection using YOLO to information extraction.
+The processed leaflet can then be browsed interactively, displaying detected deals with their segmentation masks overlaid on the original pages.
+This feature provides direct insights into the model’s performance, allowing users to verify the accuracy of detected promotions and extracted information.
+The efficiency of the application benefits from YOLO’s lightweight architecture, ensuring that leaflet processing remains fast and responsive.
+After a short processing time, users can navigate through detected deals and inspect the segmentation masks applied to the leaflet images.
+Clicking on an individual deal reveals extracted details such as the product name, price, and other metadata.
+The combination of automated deal extraction and interactive visualization makes the web application a practical tool for structured deal exploration and comparison.
 

### 2025-02-25 paper/main.tex
Add recent changes.
Ilyi: Final Version.

@@
-% This must be in the first 5 lines to tell arXiv to use pdfLaTeX, which is strongly recommended.
-\pdfoutput=1
-% In particular, the hyperref package requires pdfLaTeX in order to break URLs across lines.
+% !TEX root = main_ilyi.tex
+
+% for pdfLaTeX
+% \pdfoutput=1
 
@@
 % Change to "preprint" to generate a non-anonymous version with page numbers.
-\usepackage[preprint]{coling}
+\RequirePackage{lib}
 
 % Standard package includes
-\usepackage{times}
-\usepackage{latexsym}
+\RequirePackage{times}
+\RequirePackage{latexsym}
 
 % For proper rendering and hyphenation of words containing Latin characters (including in bib files)
-\usepackage[T1]{fontenc}
-% For Vietnamese characters
-% \usepackage[T5]{fontenc}
-% See https://www.latex-project.org/help/documentation/encguide.pdf for other character sets
+\RequirePackage[T1]{fontenc}
 
 % This assumes your files are encoded as UTF8
-\usepackage[utf8]{inputenc}
+\RequirePackage[utf8]{inputenc}
 
-% This is not strictly necessary, and may be commented out,
-% but it will improve the layout of the manuscript,
-% and will typically save some space.
-\usepackage{microtype}
+\RequirePackage{microtype}
 
-% This is also not strictly necessary, and may be commented out.
-% However, it will improve the aesthetics of text in
-% the typewriter font.
-\usepackage{inconsolata}
+\RequirePackage{inconsolata}
 
-%Including images in your LaTeX document requires adding
-%additional package(s)
-\usepackage{graphicx}
-\usepackage{amsmath}
-\usepackage{multirow}
-\usepackage{booktabs}
-\usepackage{amssymb}
-\usepackage{hyperref}
+\RequirePackage{graphicx}
+\RequirePackage{amsmath}
+\RequirePackage{multirow}
+\RequirePackage{booktabs}
+\RequirePackage{amssymb}
+\RequirePackage{hyperref}
+\RequirePackage{subfig}
+
+\RequirePackage{algorithm}
+\RequirePackage{algpseudocode}
+\RequirePackage{verbatim}
 
@@
 \begin{abstract}
-TODO
+Supermarket leaflets are a valuable source of information for consumers, offering insights into product deals, discounts, and promotions.
+However, extracting structured information from these leaflets is a challenging task due to their unstructured nature and layout variability.
+In this work, we present an intelligent system for extracting, structuring, and utilizing information from supermarket leaflets in a digital format.
+Our approach leverages advanced computer vision, Optical Character Recognition (OCR), and language models to detect and extract deals from these leaflets.
+We propose a modular pipeline for deal detection and information extraction, develop an interactive application for browsing and comparing deals, and introduce Leaflet-IE, a benchmark dataset for evaluating information extraction models.
+Our system aims to enhance the digital transformation of supermarket leaflets, providing consumers with a more efficient and data-driven shopping experience.
 \end{abstract}
@@
 \section{Introduction}
+
 \subsection{Motivation}
+When one thinks of a paper-heavy country, Germany is likely to come to mind.
+The country's affinity for printed materials is deeply ingrained in its culture, with activities such as browsing through supermarket leaflets serving as a familiar ritual for many individuals.
+These leaflets have long been an essential medium for consumers to plan their purchases, discover special offers, and compare prices.
+The rapid advancement of digital technology is transforming consumer behavior.
+While some individuals still find browsing through physical leaflets a nostalgic and even relaxing experience, younger generations are increasingly turning to digital alternatives for their shopping needs.
+The modern shopper expects convenience, efficiency, and instant access to information, yet the digital transformation of supermarket leaflets in Germany lags significantly behind, even despite the existence of applications that centralize digital versions of these leaflets.
+The majority of these applications' digital leaflets are plain documents, failing to leverage the full potential of interactivity, searchability, and intelligent recommendation systems.
+
+Furthermore, while price comparison websites and applications have become commonplace for electronics, fashion, and travel, the grocery sector remains an overlooked frontier.
+Consumers are often left navigating multiple supermarket websites or manually cross-referencing prices to find the best deals—a tedious and inefficient process.
+A comprehensive digital ecosystem that integrates grocery price comparisons, personalized discounts, and AI-driven shopping assistants could bridge this gap and act as a workaround, offering an enhanced, data-driven shopping experience and a tool that allows consumers to create a dynamic shopping list, track price trends over time, and receive real-time updates on the best deals.
+
 \subsection{Problem Statement}
-\subsection{Structure of Paper}
+The primary objective of this research is to develop an intelligent system for extracting, structuring, and utilizing information from supermarket leaflets in a digital format.
+Given a set of supermarket leaflets $\mathbf{L} = \{L_1, L_2, ..., L_n\}$, where each $L_i$ contains a set ofproduct deals $\{p_j\}_{j=1}^{m} \in P_{L_i}$, the goal is to extract and normalize these attributes to enable efficient querying and comparison across multiple supermarket chains.
+
+Each product deal $p_j$ is represented by a set of attributes $\{y_1, y_2, ..., y_k\} \subset p_j$, where each attribute $y_k$ represents a specific entity.
+Common attributes include the name and brand of the product, the original and deal prices, the unit (e.g., weight, volume), and the product image.
+The challenge lies in detecting and separating deals from the leaflet, extracting structured information from the detected deals, normalizing the extracted information to ensure consistency and comparability, and validating the extracted information to ensure accuracy.
+
+To enable advanced applications such as the abovementioned, one has to tackle different challenges, such as:
+\begin{enumerate}
+    \item Detecting and separating deals $p$ from the leaflet $L$.
+    \item Extracting structured information from the detected deals.
+    \item Normalizing the extracted information to ensure consistency and comparability.
+    \item Validating the extracted information to ensure accuracy.
+\end{enumerate}
+
+Therefore, a function $f: \mathcal{L} \to \mathcal{D}$ has to be designed, that maps a set of leaflets $\mathcal{L}$ to a set of structured deals $\mathcal{D}$, where each deal $d \in \mathcal{D}$ is represented by a set of attributes $\{y_1, y_2, ..., y_k\}$.
+
+\subsection{Contributions}
+To build this mapping, this work presents the conducted research and the practical result of a comprehensive approach to digitalizing and structuring supermarket leaflet information by leveraging advanced computer vision, Optical Character Recognition (OCR), and language models, depicted in \figref{fig:overview}.
+A \emph{modular pipeline} is proposed that encompasses deal detection, information extraction and normalization to transform raw leaflet data into structured, actionable insights.
+
+\begin{figure*}
+    \centering
+    \includegraphics[width=0.8\linewidth]{figures/overview.png}
+    \caption{Overview of the proposed approach to digitalizing and structuring supermarket leaflet information.}
+    \label{fig:overview}
+\end{figure*}
+
+To enhance usability, an \emph{interactive application} is developed that allows consumers to browse, filter, and compare deals across multiple supermarket chains.
+It provides essential search, tracking, and comparison features for improved deal discovery.
+
+To facilitate research and development in this domain, \emph{Leaflet-IE}, an end-to-end benchmark dataset for information extraction from supermarket leaflets, is introduced.
+This dataset stands as a valuable resource for evaluating and comparing different models and approaches in the field.
+
+\subsection{Structure}
+This work is structured to systematically address supermarket deal detection and information extraction, beginning with a scientific overview of related works in \secref{sec:related_works}.
+The nature of supermarket leaflet data is analyzed in \secref{sec:leaflets_data}, formalizing challenges such as layout variability, OCR noise, and multimodal fusion.
+Deal detection is covered in \secref{sec:deal_detection}, detailing an own dataset creation, instance segmentation model selection, and experimental results for identifying promotional content.
+Information extraction is extended in \secref{sec:information_extraction}, detailing an own benchmark dataset construction, popular architectural approach and their performance evaluation for extracting structured product and pricing information.
+Thereafter, the proposed interactive application is introduced in \secref{sec:application}, outlining its features, design, and user interface.
+The work concludes with a summary of contributions and future research directions in \secref{sec:conclusion}.
 
 \section{Related Works}
+\label{sec:related_works}
+
+\indent{\textbf{Supermarket Leaflet Analysis}.}
+The field of supermarket leaflet analysis has evolved to tackle key challenges such as product classification, promotion identification, and customer interaction.
+Recent studies have leveraged AI-driven techniques to enhance efficiency and accuracy in this domain.
+For instance, cite{ladwig2023} explore fine-grained product classification in leaflet advertisements, while \cite{arroyo2020} employ multi-label classification methods to analyze promotions using both textual and visual information.
+Additionally, Zhang et al.
+\cite{zhang2024} introduce PKU-GoodsAD, a dataset designed for unsupervised anomaly detection and segmentation of supermarket goods.
+Complementing these efforts,\cite{nandkumar2024} propose a multi-level Large Language Model (LLM) conversational interface to enhance supermarket robot interactions by handling diverse customer intents.
+
 \indent{\textbf{Deal Detection}.}
-\indent{\textbf{Optical Character Recognition}.}
-OCR-Model-Driven methods use OCR tools to acquire text
-and bounding box information. Subsequently, they rely
-on the models to integrate text, layout, and visual data.
+There are no direct approaches for detecting deals, including product image, price, name and more, in supermarket leaflets.
+However, the detection of specific elements in documents, or more generally, the detection of objects in images, is a widely researched area.
+When it comes to just the actual detection of these elements without understanding the semantic meaning, models such as YOLO or Faster R-CNN prove to be effective.
+These models are able to recognize objects in images and mark them with bounding boxes and further classify them.
+But because there is no direct research on the detection of deals in supermarket leaflets, the research has to be done in this area.
 
 \indent{\textbf{Information Extraction}.}
+Recent advancements in OCR, LLMs, and end-to-end multimodal architectures have significantly refined the landscape of document information extraction.
+These improvements have led to increased accuracy, efficiency, and versatility in processing structured and unstructured text from diverse document formats.
 
-\section{Methodological Overview}
+OCR technology has evolved from traditional rule-based approaches to sophisticated deep learning-driven systems.
+Open-source OCR frameworks such as Tesseract \cite{tesseract}, PaddleOCR \cite{ppocrv2}, EasyOCR \cite{easyocr}, and DocTR \cite{doctr} integrate state-of-the-art methodologies to enhance both text detection \cite{liao2019, liao2022} and recognition \cite{shi2015, li2022}.
+These systems employ deep neural networks to improve accuracy in complex document layouts, including distorted and low-quality images.
+Preprocessing techniques play a crucial role in optimizing OCR performance.
+Methods such as rectification \cite{shi2019}, deskewing \cite{pham2022}, and denoising \cite{zhao2018} significantly enhance text clarity by mitigating distortions, reducing noise, and improving alignment.
+These preprocessing steps are especially useful in real-world scenarios where scanned or photographed documents contain various inconsistencies.
+LLMs have emerged as powerful tools for refining OCR outputs through context-aware reasoning and semantic corrections.
+Models like GPT-3 \cite{brown2020} and LLaMA \cite{touvron2023} demonstrate their performance in natural language understanding, enabling improved entity recognition and post-processing of extracted text \cite{yenduri2023}.
+These models enhance the reliability of OCR by resolving ambiguities, correcting misinterpretations, and providing structured outputs in diverse domains such as finance, healthcare, and legal documentation.
+
+Transformer-based architectures \cite{vaswani2017, dosovitskiy2021} have also revolutionized document understanding by integrating vision and language processing into unified frameworks.
+These models leverage attention mechanisms to jointly process textual and visual cues, achieving state-of-the-art performance in document analysis \cite{kim2022,appalaraju2021}.
+These models are particularly effective in handling complex layouts, handwriting recognition, and tabular data extraction.
+Furthermore, multimodal approaches \cite{peng2022, li2021} introduce hybrid learning techniques that enhance information retrieval from scanned documents and digital forms.
+
+The integration of large vision-language models (LVLMs) has further expanded the capabilities of document intelligence since they utilize large-scale multimodal training to perform sophisticated image-text reasoning \cite{touvron2023,qwen2025,dai2023}.
+These advancements enable robust document understanding, particularly in scenarios where textual information is closely intertwined with graphical elements.
+Recent contributions \cite{li2024, wei2024} emphasize the growing potential of LVLMs.
+
+\section{The Nature of Supermarket Leaflet Data}  
+\label{sec:leaflets_data}
+Supermarket leaflets constitute a complex multimodal data domain characterized by heterogeneous layouts, ambiguous associations, and noisy signal extraction.
+As illustrated in \figref{fig:leaflet_data_samples}, these documents present unique computational challenges that demand joint reasoning over visual, textual, and contextual modalities.
+We formalize the key obstacles below.
+
+Leaflets exhibit extreme variability in design elements that impede automated parsing.
+The spatial heterogeneity, thus the non-standardized arrangements of product images, prices, and promotions across retailers, is a primary concern.
+The layout of leaflets can vary significantly, with product images, prices, and promotional text appearing in diverse configurations.
+Additionally, typography challenges, such as superscripted decimals, struck-through original prices, and font inconsistencies between deals and regular text, further complicate the extraction process.
+Overlapping elements, where text is occluded by product images or graphical overlays, violate the assumptions of Optical Character Recognition (OCR) systems, which assume planar text.
+
+\begin{figure}[h!]
+    \centering
+    \includegraphics[width=0.8\linewidth]{figures/samples.png}
+    \caption{Common German supermarket deals.}
+    \label{fig:leaflet_data_samples}
+\end{figure}
+
+Inherently, these leaflets contain both textual and visual information, which must be jointly processed to extract meaningful insights.
+The textual elements include product names, brands, prices, and units, while the visual components consist of product images, logos, and promotional graphics.
+The challenge lies in aligning these modalities to extract structured information accurately.
+Furthermore, the multimodal nature of the data introduces semantic ambiguities, where textual and visual elements maintain non-strict correspondences.
+For instance, a product image may correspond to multiple text entries, or price interpretation may require visual grounding.
+
+Due to these characteristics, leaflets are prone to linguistic ambiguities, conversion errors and cultural-specific semantics.
+The German language, with its compound nouns, specific punctuation conventions, and diverse word forms, poses unique challenges for text extraction.
+OCR errors, such as glyph confusion and tokenization failures, are common due to font artifacts and compound nouns.
+Multilingual mix, where English promotion terms appear alongside German body text, further complicates the parsing process.
+Price disambiguation, distinguishing unit prices from total prices without weight references, is a critical challenge.
+Additionally, more complex offer strategies, such as buy-one-get-one-free, coupon-based discounts, and permanent price reductions, require nuanced interpretation beyond simple text extraction.
+
+Additionally, supermarket leaflets are commonly scheduled for a weekly release, with each leaflet containing a set of deals that are valid for a specific period.
+However, not every supermarket chain follows this pattern, and some may release leaflets bi-weekly, monthly or even irregularly.
+This temporal grounding problem requires associating each deal with an expiry time, which is often implicit in the leaflet text.
+For instance, a deal may be valid only in specific store branches or for a limited time, indicated by small print codes or context clues.
+
+This multifaceted nature demands architectures that jointly optimize for visual-textual alignment, error-resilient parsing, and contextual plausibility.
 
 \section{Deal Detection}
-    \subsection{Datasets}
+\label{sec:deal_detection}
+Detecting deals within supermarket leaflets is a crucial step in the process of extracting structured  data.
+The ultimate end-to-end goal of deal detection is to accurately identify and separate individual deals from digital supermarket leaflets, enabling further analysis and integration into a structured database for an application.
+This step is fundamental for creating a comprehensive, queryable system that allows users to compare deals across different retailers efficiently.
+Directly detecting deals within leaflets is necessary because supermarket deals are not standardized, and each leaflet can contain multiple overlapping deals, diverse layouts, and varying fonts, making simple text-based extraction approaches insufficient.
+
+\subsection{Dataset}
+An approach to obtaining deal data would be direct web scraping from supermarket websites, as these days they present their deals digitally in a structured way.
+However, this method is highly error-prone and difficult to generalize due to the distinct and frequently changing layouts of different supermarket websites.
+Additionally, many retailers do not provide direct, easily scrappable structured deal data.
+Instead, an alternative source has been identified.
+Websites that aggregate and upload full promotional leaflets from various German supermarkets on a weekly basis.
+These leaflets provide a more standardized input format and can be systematically downloaded using an automated script.
+
+The collected dataset consists of approximately 13,000 images from a diverse range of supermarket chains, including well-known retailers such as Penny, Aldi, and Kaufland, as well as less conventional ones like Metro.
+The primary focus remains on supermarkets that sell groceries and drugstore products, as these are the most relevant for the intended applications.
+Each leaflet page contains multiple distinct offers, which must be individually detected.
+This is achieved through object detection techniques, which can either utilize bounding boxes or instance segmentation.
+While bounding box detection provides a straightforward way to localize deals, it often struggles with overlapping offers, leading to incorrect classifications.
+Instance segmentation is therefore the preferred approach, as it allows for more precise extraction of deal regions without interference from neighboring offers.
+Deals in the dataset are categorized into four main classes:
+
+\begin{itemize}
+    \item Standard Deal: A regular product discount.
+    \item Product Category Deal: A discount on an entire product category (e.g., "20\% off all canned goods").
+    \item Coupon Deal: Special offers requiring the use of coupons (e.g., Payback).
+    \item Miscellaneous: Deals outside the primary categories, such as travel promotions.
+\end{itemize}
+
+\begin{figure*}[h!]
+    \centering
+    \includegraphics[width=0.7\linewidth]{figures/deal_detection/dataset_count.png}
+    \caption{Distribution of labeled leaflet pages and deals in training and validation sets.}
+    \label{fig:ddetect_dataset_count}
+\end{figure*}
+
+The primary focus is on standard deals, as they are the most common and directly useful for consumers.
+No publicly available dataset fully aligns with this task as it involves both instance segmentation and deal categorization, specifically in the context of German supermarkets.
+So, a subset of the collected pages was manually annotated.
+The result is a dataset of 672 annotated leaflet pages, with 4,675 individual deals in training and 75 pages with 523 deals in the validation set as shown in \figref{fig:ddetect_dataset_count}.
+In cases where no overlapping elements were present, bounding boxes were used.
+For overlapping offers, instance segmentation masks were created.
+Depending on the training requirements, annotations can be converted between bounding boxes and segmentation masks, although segmentation masks provide a more granular representation.
+
+\begin{figure*}[h!]
+    \centering
+    \includegraphics[width=0.6\linewidth]{figures/deal_detection/bbox_page.png}
+    \caption{Bounding box detection results on a leaflet page resulting in overlapping bounding boxes.}
+    \label{fig:ddetect_bbox_page}
+\end{figure*}
+
+\begin{figure*}[h!]
+    \centering
+    \includegraphics[width=0.6\linewidth]{figures/deal_detection/mask_page.png}
+    \caption{Instance segmentation results on a leaflet page showing precise deal separation.}
+    \label{fig:ddetect_mask_page}
+\end{figure*}
+
 \subsection{Model}
+Object detection and segmentation tasks require identifying objects within an image while determining their locations.
+The simplest form of image analysis, image classification, assigns a single label to an entire image, providing no information about object positions.
+However, multiple deal detection in supermarket leaflets demands the identification of multiple deals, whose number is unknown beforehand, along with their precise locations to extract them later.
+
+Object detection models can be broadly categorized into multi-stage (multi-shot) detectors and single-stage (single-shot) detectors.
+Multi-stage detectors, such as the R-CNN family (R-CNN, Fast R-CNN, Faster R-CNN, Mask R-CNN), follow a sequential process.
+First, they generate a set of region proposals, indicating potential object locations.
+These proposals are then classified in a second stage.
+While this method achieves high accuracy, it introduces significant computational overhead.
+Earlier versions, such as R-CNN, even relied on separate, non-learnable algorithms for proposal generation.
+Faster R-CNN improved efficiency by integrating the Region Proposal Network (RPN) directly into the model, eliminating the need for external proposal algorithms.
+However, even this approach remains computationally demanding.
+In contrast, single-stage detectors, such as YOLO (You Only Look Once), perform detection in a single forward pass, predicting object locations and classifications simultaneously.
+This significantly reduces inference time, making these models well-suited for real-time applications.
+YOLO, in particular, has established itself as one of the most widely used architectures due to its speed and competitive accuracy.
+Given the requirement of processing thousands of leaflet pages efficiently, a single-stage detector was chosen for deal detection, with a particular focus on YOLO-based architectures.
+
+The YOLO model follows a grid-based detection approach, where the input image is divided into an SxS grid.
+Each grid cell is processed for predicting objects whose centers fall within it.
+Instead of relying on separate region proposal mechanisms, YOLO processes the image in a single forward pass, directly predicting bounding box coordinates, confidence scores, and class probabilities per grid cell.
+The bounding boxes are parameterized by their center coordinates, width, and height, while the confidence scores indicate the model’s certainty that a given bounding box contains an object.
+The class probabilities further specify which category the detected object belongs to.
+Traditional object detection frameworks like YOLO produce bounding boxes that encapsulate detected objects in rectangular shapes.
+However, supermarket leaflets contain deals that frequently overlap or feature irregular layouts, making bounding box-based detection less effective.
+Instance segmentation extends YOLO by incorporating an additional segmentation head that predicts pixel-level masks for each detected object.
+This approach enables the model to distinguish individual deals more precisely, reducing the risk of grouping multiple offers within a single bounding box.
+The segmentation mechanism operates by first detecting objects using the standard YOLO pipeline.
+Once a bounding box is identified, the model refines its prediction by generating a binary mask that determines which pixels within the bounding box belong to the detected object.
+The segmentation head shares feature representations with the object detection components, ensuring efficient training and inference.
+This method enhances the model’s ability to isolate individual deals even in cluttered layouts, making it particularly suited for supermarket leaflets where offers frequently overlap or appear with complex backgrounds.
+
+\subsection{Experiments}
+Evaluating the performance of instance segmentation models requires an analysis of how well detected objects align with ground-truth annotations.
+The primary metric used in this assessment is \emph{Mean Average Precision (mAP)}, which quantifies detection accuracy at different levels of overlap between predicted and actual objects.
+The core component of mAP is Intersection over Union (IoU).
+IoU is defined as the ratio of the intersection area between the predicted and ground-truth segmentation masks to their union.
+A higher IoU indicates a better match between the prediction and the actual object, while a lower IoU suggests that the detected region is misaligned or includes excessive background.
+In the case of bounding boxes, IoU is calculated based on the overlap of rectangular regions, whereas for instance segmentation, it is computed on a pixel level, capturing the true shape of the detected objects.
+To evaluate model performance, different IoU thresholds are applied.
+A commonly used metric is mAP@50, which considers a detection correct if the IoU between the predicted and ground-truth mask exceeds 50\%.
+This threshold provides insight into how well a model identifies objects in general but does not strictly enforce precision in localization.
+A more comprehensive metric is mAP@50-95, which averages precision across multiple IoU thresholds, ranging from 50\% to 95\% in increments of 5\%.
+This approach penalizes models that fail to produce accurate segmentations and is particularly useful for assessing how well the model distinguishes closely packed or irregularly shaped deals.
+
+\begin{figure*}[h!]
+    \centering
+    \begin{tabular}{cc}
+    \includegraphics[width=0.5\linewidth]{figures/deal_detection/map50_all_yolo.png} &   \includegraphics[width=0.5\linewidth]{figures/deal_detection/map50_95_all_yolo.png} \\
+    (a) Results for mAP50 & (b) Results for mAP50-95 \\[2pt]
+    \end{tabular}
+    \caption{Performance comparison of YOLOv8 and YOLOv11 models on the deal detection validation set.}
+    \label{fig:all_yolo_results}
+\end{figure*}
+
+The first set of experiments focused on comparing different YOLO variants trained on the dataset.
+Each model was trained for 20 epochs without additional data augmentation.
+The results, shown in Figure \ref{fig:all_yolo_results} (a), present the mAP50 (mask) scores for YOLOv8 and YOLOv11 in their small, medium, and large configurations.
+The findings indicate that the smallest version of YOLOv8 achieved the highest validation mAP50, outperforming larger models in this setting.
+A second analysis, visualized in Figure \ref{fig:all_yolo_results} (b), examines mAP50-95 scores for the same models, reinforcing the observation that a lightweight YOLO model is sufficient for this particular task.
+The lower performance of larger models suggests that the dataset’s structure, with relatively uniform layouts, does not require highly complex architectures to achieve strong results.
+
+\begin{figure*}[h!]
+    \centering
+    \begin{tabular}{cc}
+    \includegraphics[width=0.5\linewidth]{figures/deal_detection/map50_yolo8.png} &   \includegraphics[width=0.5\linewidth]{figures/deal_detection/map50_95_yolo8.png} \\
+    (a) Results for mAP50 & (b) Results for mAP50-95 \\[2pt]
+    \end{tabular}
+    \caption{Performance comparison of YOLOv8s models with and without data augmentation on the deal detection validation set.}
+    \label{fig:yolo8_results}
+\end{figure*}
+
+Following this baseline evaluation, additional experiments investigated the impact of data augmentation on segmentation performance.
+Various augmentation strategies were applied, including translation, scaling, horizontal flipping, and color transformations.
+The goal was to determine whether these transformations improved the model’s ability to generalize across different leaflet layouts.
+Each augmented model was trained for ten additional epochs, and the results are displayed in Figure \ref{fig:yolo8_results}.
+While certain augmentation techniques led to slight improvements in segmentation accuracy, particularly for models trained with random translations, the overall best-performing model remained the one trained without any augmentation.
+This outcome suggests that the dataset already contains sufficient variation to ensure robust generalization without the need for extensive artificial augmentations.
+
+The final model selection was based on the combination of high segmentation accuracy and computational efficiency.
+Given the results, \emph{YOLOv8s} was chosen as the preferred model, as it consistently outperformed more complex variants while maintaining a lower computational cost.
+The model’s ability to detect deals with high precision makes it a strong candidate for further applications.
+And this is particularly important because everything else builds on it.
+
+\section{Information Extraction of Supermarket Deals}
+\label{sec:information_extraction}
+Subsequently to the detection and separation of supermarket deals, the overarching goal of using these in applications requires the extraction of the various useful information from these deals. 
+The task of extracting meaningful and structured information from supermarket deal images is a complex and multi-faceted problem, requiring the integration of various modalities, overcoming challenges posed by noisy data, and leveraging deep learning techniques.
+This section provides a detailed exploration of methodologies, as well as the theoretical and practical framework needed to perform such extraction.
+
+\subsection{Approaches to Information Extraction}
+Formally, the task of information extraction from a deal image can be defined as the identification of specific entities, including the product name, brand, original price, deal price, and unit.
+We define the following set of output labels:
+\begin{equation}
+\mathcal{Y} = \{y_{i}\}_{i=1}^{n},
+\end{equation}
+where $y_{i}$ represents the $i$-th entity in the deal image. In the following, the entities are defined as:
+\begin{itemize}
+    \item \code{$y_{\text{product\_name}}$}: The name of the product.
+    \item \code{$y_{\text{brand}}$}: The brand of the product.
+    \item \code{$y_{\text{original\_price}}$}: The original price of the product.
+    \item \code{$y_{\text{deal\_price}}$}: The deal price of the product.
+    \item \code{$y_{\text{unit}}$}: The unit of the product (e.g., weight, volume).
+\end{itemize}
+
+To extract these entities, one aims to learn a function $f(\cdot)$ that maps an input image $I$ to the desired outputs:
+\begin{equation}
+    f: I \to \mathcal{Y},
+\end{equation}
+where $ I $ is the deal image, and $ \mathcal{Y} $ represents the extracted entities.
+
+The choice of the function $ f(\cdot) $ is an architectural decision that depends on the specific requirements of the task, the nature of the data, the available resources, and the desired performance metrics.
+
+Among the various existing architectural approaches to learn $ f(\cdot) $ for information extraction, several methodologies have been developed to address the inherent complexities in supermarket deal images.
+These methods can be categorized into classical approaches, multi-stage traditional models, hybrid OCR-LLM systems, and end-to-end deep learning frameworks.
+Each paradigm offers distinct advantages, and their applicability depends on computational resources, dataset characteristics, and performance requirements.
+
+\subsubsection{Traditional and Hybrid Approaches for Supermarket Leaflet Information Extraction}  
+Information extraction from supermarket leaflets has traditionally been approached through a pipeline of sequential sub-tasks, each addressed by specialized systems.
+These methods, while extensively studied and methodologically diverse, are typically divided into three main stages: text detection, text recognition, and key-value pair extraction.
+Although effective in certain scenarios, these approaches suffer from inherent limitations, including computational overhead, error propagation, and suboptimal performance on edge cases.
+Recent advancements in large language models (LLMs) have led to the development of hybrid OCR-LLM architectures, which combine the precision of optical character recognition (OCR) with the contextual reasoning capabilities of LLMs.
+Below, we formalize these approaches and discuss their strengths and limitations.
+
+Traditional architectures decompose the problem into independent sub-tasks, each handled by specialized models.
+While this modularity allows for targeted optimization, it introduces complexity and inefficiencies due to the lack of end-to-end training and error propagation across stages.
+
+The first stage, \emph{text detection}, involves identifying regions in the image $ I \in \mathbb{R}^{H \times W \times 3} $ that contain textual information.
+This is typically achieved using rule-based systems or neural networks designed for small object detection.
+The output is a set of $ M $ bounding boxes $ \{b_i\}_{i=1}^{M} $, where each $ b_i = (x_{\text{min}}, y_{\text{min}}, x_{\text{max}}, y_{\text{max}}) $ defines the coordinates of a text region.
+
+Each detected bounding box $ b_i $ is cropped and processed by a \emph{text recognition} model to convert the visual representation into a textual one.
+This task is challenging due to decoding errors caused by noisy backgrounds, stylized fonts, and ambiguous characters.
+Given the set of bounding boxes $ \{b_i\}_{i=1}^{M} $, the goal is to predict the corresponding textual entities $ \{t_i\}_{i=1}^{M} $ as the maximum likelihood sequence.
+
+To use the recognized texts for information extraction, the final stage involves parsing the textual entities into structured outputs.
+This is typically achieved through rule-based systems or sequence-to-sequence models that generate key-value pairs from the recognized text.
+The output is a set of structured entities $ \{y_i\}_{i=1}^{N} $, where each $ y_i $ represents a specific entity (e.g., product name, price, unit).
+
+The rise of \emph{large language models }(LLMs) has enabled the development of hybrid OCR-LLM architectures, which combine the strengths of OCR tools with the linguistic and reasoning capabilities of LLMs.
+These approaches retain the traditional OCR pipeline for converting visual text into machine-readable form but leverage LLMs to enhance robustness through contextual reasoning and structured output generation.
+
+In a hybrid OCR-LLM system, the OCR stage processes the input image $ I $ to produce a set of unstructured text fragments $ T = \{t_i\}_{i=1}^{M} $ with associated spatial coordinates.
+These fragments are serialized into a prompt and fed into a pretrained LLM, which performs contextual parsing and generates some linguistic output that, in most cases, has to be somewhat postprocessed to extract the desired information.
+
+Hybrid OCR-LLM models offer several advantages over traditional pipelines.
+By integrating contextual reasoning, they reduce error propagation and improve robustness to noisy or ambiguous inputs.
+Additionally, the use of pretrained LLMs eliminates the need for task-specific training, simplifying system development.
+However, these models still rely on the accuracy of the OCR stage, and misrecognitions (e.g., "O" vs.
+"0") can propagate to the LLM.
+Furthermore, the computational cost of LLM inference can be prohibitive for large-scale applications.
+
+\subsubsection{End-to-End Models}  
+End-to-End (E2E) approaches unify document understanding by learning a direct mapping $ F: I \to \mathcal{D} $ and thus jointly optimize visual feature extraction and semantic parsing.
+We formalize two dominant paradigms: vision-encoder-decoder architectures and large vision-language models (LVLMs), which share foundational principles but diverge in scale and architectural complexity.
+
+Foundationally, all E2E models decompose into three components: a vision encoder, a representation projection, and a decoder.
+The vision encoder extracts hierarchical visual features $ \mathbf{Z} = \text{Enc}(I) $, which are then aligned with textual semantics through a representation projection.
+The decoder generates structured output $ \mathbf{Y} $ autoregressively.
+\figref{fig:e2e_arch} illustrates the unified architecture.
+
+\begin{figure}[h!]
+    \centering
+    \includegraphics[width=0.5\linewidth]{figures/vlm_arch.png}
+    \caption{End-to-End Vision-Encoder-Decoder Architecture.}
+    \label{fig:e2e_arch}
+\end{figure}
+
+\indent{\textbf{Donut \cite{kim2022}}.} This model employs a compact transformer-based encoder-decoder.
+Let $ I $ be partitioned into patches, each linearly projected to an encoded input $X$.
+The used vision encoder $E$ computes an encoded representation mainly through:
+\begin{equation}
+Z = E(I) = \text{FFN}(\text{MSA}(X) + X) + \text{MSA}(X)
+\end{equation}  
+where $\text{MSA}$ denotes multi-head self-attention and $\text{FFN}$ a feed-forward network. The hierarchical structure captures local textural patterns as well as global layout cues.
+
+Subsequently, a transformer decoder generates tokens $ Y = (y_1, \dots, y_T) $ using cross-attention over $ Z $:  
+\begin{equation}
+P(y_t | y_{<t}, Z) = \text{Softmax}(\text{FFN}(\text{MSA}(Y) + Z)),
+\end{equation}  
+where $ Y $ is the token sequence and $ Z $ the encoded image features. The model is trained end-to-end with a maximum likelihood objective \cite{vaswani2017}.
+
+\indent{\textbf{Large Vision-Language Models (LVLMs)}.} In the realm of upscaling language models into LLMs, computer vision utilizes this trend to process multimodal data.
+LVLMs like Llama 3.2 Vision \cite{touvron2023} scale this framework by integrating pretrained vision encoders with large language models (LLMs).
+These architectures utilize \emph{cross-modal projection}, which aligns visual features with the LLM's embedding space, and \emph{multimodal decoding}, which attends to both visual tokens and textual prompts.
+The LVLM's strength lies in zero-shot reasoning and leveraging pretrained knowledge for structured output generation.
+
+While smaller models like Donut offer efficiency and direct output generation, LVLMs provide zero-shot reasoning and open-world capabilities at increased computational cost.
+
+\subsection{Dataset Creation}
+
+\begin{table}[h!]
+    \centering
+    \caption{Leaflet-IE Dataset}
+    \label{tab:ie_dataset}
+    \begin{tabular}{lc}
+    \toprule
+    Entity           & Sample Size \\
+    \midrule
+    \code{image\_id}        & 372  \\
+    \code{brand}            & 357  \\
+    \code{product\_name}    & 370  \\
+    \code{original\_price}  & 286  \\
+    \code{deal\_price}      & 372  \\
+    \code{weight}           & 369  \\
+    \bottomrule
+    \end{tabular}
+    \end{table}
+
+Since the availability of German supermarket leaflet data is literally not findable, a custom dataset was created by manually annotating a collection of supermarket deal images.
+The dataset includes images from the most common supermarket chains, each with unique layout, fonts, and colors to, in general, ensure the highest diversity and robustness possible.
+Each image is annotated with a corresponding label file that includes the desired entities as well as the image identificator.
+The dataset is split into a training (\~{} 80\%) and a validation set (\~{} 20\%) for each model to be trained and evaluated on.
+\tabref{tab:ie_dataset} provides an overview of the dataset with the sample size for each entity and \figref{fig:ie_dataset_samples} shows some sample images with their annotations.
+
+Even though the Leaflet-IE dataset is relatively small, the reader will be able to see that the dataset is sufficient to evaluate the performance of different IE appraoches as well as to train an competitive end-to-end model.
+However, as the reader may notice, the dataset is solely focused on single product deals at this point and explicitly does not include
+
+\begin{figure*}[h!]
+\centering
+\includegraphics[width=0.5\linewidth]{figures/ie_samples.png}
+\caption{Sample images with annotations from the custom dataset.}
+\label{fig:ie_dataset_samples}
+\end{figure*}
+
 \subsection{Experiments}
 
-\section{Optical Character Recognition}
+The experiments aim to identify the most effective methodology for extracting structured information from supermarket leaflets by evaluating three candidate approaches: (1) Hybrid OCR + LLM pipelines, (2) end-to-end Vision-Encoder-Decoder models, and (3) Large Vision-Language Models (LVLMs).
+The evaluation is structured into four sequential phases to systematically assess performance and scalability.
 
-\section{Information Extraction}
+First, Plain Deal OCR Performance establishes a baseline by measuring the accuracy of standalone OCR systems in extracting textual content from leaflets, highlighting challenges such as font variability and noisy backgrounds.
+Second, OCR + LLM Performance evaluates the combined pipeline, where OCR outputs are processed by large language models to resolve ambiguities and extract structured information.
+Third, Donut Fine-Tuning Performance assesses the Vision-Encoder-Decoder model's effectiveness after fine-tuning on leaflet-specific data, focusing on its ability to handle multimodal inputs without intermediate OCR steps.
+Finally, the MAIN experiment conducts a comprehensive comparison of Hybrid OCR+LLM, Donut, and LVLM approaches, analyzing their accuracy, robustness, and computational efficiency in real-world leaflet data scenarios.
+
+\subsubsection{Implementation Details}
+The experiments were conducted on two distinct computational workstations - station 1 equipped with an NVIDIA RTX 4080 GPU and station 2 with an NVIDIA GTX 1080 GPU.
+Therefore, the experiments could be conducted in parallel, ensuring efficient model training and evaluation.
+
+The software stack includegraphics Python with PyTorch\footnote{\href{https://pytorch.org/}{https://pytorch.org/}} as the primary deep learning framework, HuggingFace Transformers \footnote{\href{https://huggingface.co/transformers/}{https://huggingface.co/transformers/}}
+for leveraging pre-trained models, ollama \footnote{\href{https://ollama.com/}{https://ollama.com/}}
+and lmstudio \footnote{\href{https://lmstudio.ai/}{https://lmstudio.ai/}} for large language models and large vision-language models, and OpenCV \footnote{\href{https://opencv.org/}{https://opencv.org/}} for image preprocessing and data augmentation, as well as various other libraries for data pre-and post-processing, visualization, data management and monitoring \footnote{The codebase is available at \href{https://github.com/ilyii/leaflets}{https://github.com/ilyii/leaflets}}.
+
+% SUB-STUDIES
+\subsubsection{Plain Deal OCR Performance}
+The aim of this experiment is to evaluate the performance of various OCR models in extracting text from supermarket leaflets.
+The evaluation focuses on the accuracies of the extracted entities from \tabref{tab:ie_dataset} and the impact of different normalization levels on the recognition performance.
+The results provide insights into the robustness and accuracy of different OCR models in handling the complexities of supermarket leaflet data.
+
+The most commonly used OCR models include:
+\begin{itemize}
+    \item Tesseract \footnote{\href{https://github.com/tesseract-ocr/tesseract}{https://github.com/tesseract-ocr/tesseract}},
+    \item EasyOCR \footnote{\href{https://github.com/JaidedAI/EasyOCR}{https://github.com/JaidedAI/EasyOCR}},
+    \item PaddleOCR \footnote{\href{https://github.com/PaddlePaddle/PaddleOCR}{https://github.com/PaddlePaddle/PaddleOCR}},
+    \item DocTR \footnote{\href{https://github.com/mindee/doctr}{https://github.com/mindee/doctr}}.
+\end{itemize}
+These models have been trained on a variety of datasets and are known for their robustness and accuracy in text extraction.
+Since it is likely that none of the OCR models have seen this data before, all 372 samples of the Leaflet-IE dataset were used for evaluation.
+While OCR alone is not capable of generating key-value mappings, the evaluation used a different set of metrics:
+
+\begin{itemize}
+    \item \textbf{Accuracy}: Measures whether the expected value is present in the OCR output.
+    \item \textbf{N-gram Accuracy}: Determines if an n-gram substring of the expected value exists in the OCR output, computed for $n \in \left[\frac{|v|}{2}, |v| - 1\right]$, where $|v|$ represents the string length of the ground truth entity value.
+\end{itemize}
+
+Given that language-specific OCR errors are common, the evaluation was conducted at different levels of normalization to improve comparability. The text normalization included the following layers:
+\begin{itemize}
+    \item \textbf{Level 1:} Text stripping and string conversion.
+    \item \textbf{Level 2:} Lowercasing and basic replacements.
+    \item \textbf{Level 3:} Use-case specific replacements.
+    \item \textbf{Level 4:} Punctuation and whitespace removal.
+\end{itemize}
+Each level includes the normalization steps of the previous levels.
+Therefore, the normalization procedure can be thought of as a gradual alignment of the OCR output to the ground truth to investigate the OCR model's robustness to different normalization levels.
+The reader is referred to \secref{app:ocr_normalization} for a detailed description of the normalization procedure.
+
+\indent{\textbf{Results}.} Figure \ref{fig:eval_ocr_accuracies} presents a comparative analysis of various OCR models and normalization levels based on per-entity accuracy.
+The results highlight several key trends regarding the recognition performance of different entities.
+
+\begin{figure*}
+    \begin{tabular}{cc}
+      \includegraphics[width=0.5\linewidth]{figures/accuracy_level_1.png} &   \includegraphics[width=0.5\linewidth]{figures/accuracy_level_2.png} \\
+    (a) Level 1 & (b) Level 2 \\[6pt]
+     \includegraphics[width=0.5\linewidth]{figures/accuracy_level_3.png} &   \includegraphics[width=0.5\linewidth]{figures/accuracy_level_4.png} \\
+    (c) Level 3 & (d) Level 4 \\[6pt]
+    \end{tabular}
+    \caption{Per-Entity Accuracy of OCR Models at Different Normalization Levels.}
+    \label{fig:eval_ocr_accuracies}
+    \end{figure*}
+
+In general, the OCR models exhibit superior performance in extracting words compared to numerical values.
+This discrepancy is particularly evident in entity-wise accuracy variations.
+At the baseline level (normalization level 1), the deal price entity consistently shows the lowest accuracy, whereas the brand entity achieves the highest.
+The accuracy of other entities varies significantly, with PaddleOCR, EasyOCR, and docTR displaying comparable performance, while Tesseract lags behind.
+
+The overall accuracy improves with increasing normalization levels, with normalization level 4 yielding the highest accuracy gains.
+At this level, Tesseract continues to struggle with deal price recognition, failing in over 90\% of cases.
+In contrast, the other OCR models achieve accuracies exceeding 70\% across nearly all entity types.
+
+Among the different entities, brand names are consistently recognized with the highest accuracy.
+This can be attributed to their simpler linguistic structure and distinct visual presentation, as brand names are often bolded or highlighted in promotional material.
+In contrast, product names tend to have more complex linguistic structures, making exact string matching more challenging.
+
+The recognition of unit information lags behind brand names but remains more accurate than deal prices.
+The reduced accuracy can be explained by the smaller font size of unit labels, their less prominent placement, and the high variability in unit measurements (e.g., "kg", "g", "Stück"), which complicates recognition.
+
+A significant gap is observed between deal price and original price accuracy.
+This can be attributed to the typographic differences between the two: deal prices are often emphasized using distinctive fonts and superscripted decimals, making them harder for OCR models to interpret correctly.
+In contrast, original prices are typically displayed in a standard inline format, which is easier to recognize.
+
+\begin{figure*}[h!]
+    \begin{tabular}{cc}
+      \includegraphics[width=0.5\linewidth]{figures/ngram_accuracy_level_1.png} &   \includegraphics[width=0.5\linewidth]{figures/ngram_accuracy_level_2.png} \\
+    (a) Level 1 & (b) Level 2 \\[6pt]
+        \includegraphics[width=0.5\linewidth]{figures/ngram_accuracy_level_3.png} &   \includegraphics[width=0.5\linewidth]{figures/ngram_accuracy_level_4.png} \\
+    (c) Level 3 & (d) Level 4 \\[6pt]
+    \end{tabular}
+    \caption{Per-Entity N-Gram Accuracy of OCR Models at Different Normalization Levels.}
+    \label{fig:eval_ocr_ngram_accuracies}
+\end{figure*}
+
+When evaluating n-gram accuracy per-entity in \figref{fig:eval_ocr_ngram_accuracies}, the results reveal a similar trend to per-entity accuracy.
+When comparing the OCR models, PaddleOCR consistently outperforms the other models especially in the price extractions while Tesseract lacks behind in all entities.
+
+The most significant observation is that the deal price and original price exhibit in lower normalization levels significantly worse accuracies.
+Since the length of n-gram sequences increase superlinearly, longer entity values, precisely the brand and product name, more likely achieve higher accuracies, which is also reflected in the results.
+
+At the highest normalization level, most models achieve 100\% or close to 100\% n-gram accuracy in the majority of entites.
+Additionally, here the discrepancy of Tesseract is most visible, where it cannot nearly achieve comparable scores.
+Also, one can observe that the unit entity drops significantly at level 4 across all models.
+This can be attributed to the high variability in unit measurements, which makes it challenging to match the exact n-grams.
+
+% EXPERIMENT: OCR+LLM
+\subsubsection{Hybrid-OCR+LLM Performance}
+
+In addition to evaluating the OCR capabilities, the performance of OCR models was assessed in conjunction with large language models (LLMs).
+The primary objectives were to determine the most effective OCR-LLM combination for information extraction and to evaluate the impact of different OCR models on the LLM's performance.
+
+All 372 samples of the Leaflet-IE dataset were used for evaluation.
+It is assumed that neither the OCR models nor the LLMs have previously encountered this data, similar to the OCR evaluation.
+Since the task is to extract structured information, the evaluation metrics were adapted to reflect the performance of the OCR-LLM combination in generating key-value mappings.
+The evaluation metrics include:
+\begin{itemize}
+    \item \textbf{Accuracy (Per Entity):} Measures the accuracy (of each extracted entity).
+    \item \textbf{Levenshtein Distance:} Calculates the distance between the prediction and the ground truth.
+\end{itemize}
+
+The LLMs were prompted to extract entities from the OCR output. The specific prompt used can be found in \secref{app:llm_prompt}.
+
+\paragraph{Models Evaluated:}
+\begin{itemize}
+    \item \textbf{Llama 3.1 [8b, Q4]}: \texttt{llama3.1\_8b} \cite{touvron2023},
+    \item \textbf{Qwen 2.5 [1.5b, Q8]}: \texttt{qwen2.5\_1.5b-instruct-q8\_0} \cite{qwen2025},
+    \item \textbf{Llama 3.2 [3b, Q8]}: \texttt{llama3.2\_3b-instruct-q8\_0} \cite{touvron2023},
+    \item \textbf{Qwen 2.5 [7b, Q4]}: \texttt{qwen2.5\_7b} \cite{qwen2025}.
+\end{itemize}
+where the LLM name and version is additionally specified through the model size (in billions of parameters) and the quantization level.
+
+To avoid confusion with the normalization used in the OCR experiment, the OCR results were kept raw, as normalization may remove valuable information.
+The LLMs are expected to handle such inconsistencies and errors in the input.
+Instead, here the entity values were evaluated in both raw form and with a normalization applied for the comparability between the LLM prediction and the ground truth value .
+The normalization procedure includes usual character replacements and filtering based on linguistic artifacts commonly encountered in OCR errors.
+The specific normalization procedure can be found in \secref{app:ocr_llm_normalization}.
+\paragraph{Results:}
+The entity-averaged accuracies and Levenshtein distances for the raw OCR output are depicted in Figures \ref{fig:eval_ocr_llm_accuracies_avg} and \ref{fig:eval_ocr_llm_levdist_avg}, respectively.
+
+\begin{figure*}[h!]
+    \centering
+    \includegraphics[width=0.8\linewidth]{figures/avg_accuracies.png}
+    \caption{Entity-Averaged Accuracy of LLM Models per Raw OCR Output. a: Llama 3.1 [8b, Q4], b: Qwen 2.5 [1.5b, Q8], c: Llama 3.2 [3b, Q8], d: Qwen 2.5 [7b, Q4].}
+    \label{fig:eval_ocr_llm_accuracies_avg}
+\end{figure*}
+
+The averaged accuracies reveal that a higher number of parameters is more beneficial for the LLMs in this task than a higher quantization level.
+Specifically, the Llama 3.1:8b and Qwen 2.5:7b models achieve significantly higher accuracy scores than their counterparts with a lower number of parameters.
+Qwen 2.5:1.5b in Q8 performs worse than Llama 3.2:3b in Q8, but Qwen 2.5:7b in Q4 is overall the best.
+These differences can be attributed to multiple factors, such as the pre-training data of the models, the model architecture, or the prompt used to extract the entities.
+DocTR and PaddleOCR achieve equal or better results than Tesseract and EasyOCR.
+Specifically, Tesseract consistently performs the worst among the evaluated models.
+
+\begin{figure*}[h!]
+    \centering
+    \includegraphics[width=0.8\linewidth]{figures/avg_levdistances.png}
+    \caption{Entity-Averaged Levenshtein Distance of OCR-LLM Models (Raw OCR Output). a: Llama 3.1 [8b, Q4], b: Qwen 2.5 [1.5b, Q8], c: Llama 3.2 [3b, Q8], d: Qwen 2.5 [7b, Q4].}
+    \label{fig:eval_ocr_llm_levdist_avg}
+\end{figure*}
+
+When regarding the levenshtein distances, the results show similar trends.
+DocTR delivers by far the best OCR input across all OCR models.
+Suprisingly, Tesseract achieves lower levenshtein distances than PaddleOCR and EasyOCR, with EasyOCR being the worst across all models.
+This could be due to the fact that Tesseract delivers more often slightly wrong but still similar results, while EasyOCR delivers less often wrong but more different results.
+The LLMs show similar trends as in the accuracy evaluation, but Llama 3.1:8b now slightly outperforms Qwen 2.5:7b.
+The differences between the LLMs are less pronounced than in the accuracy evaluation, which can be attributed to the unnormalized levenshtein distance calculation used.
+\secref{app:ocr_llm_results} provides further results on entity-level accuracies and levenshtein distances for each OCR-LLM combination.
+
+\subsection{Donut Fine-Tuning Performance}
+The experiment aims to evaluate the fine-tuning performance of the Vision Encoder-Decoder model, Donut, pretrained on the CORD dataset, to determine its capability in extracting end-to-end information from supermarket leaflet deal images.
+Conducted on an NVIDIA RTX 4080 (Station 1), the model has a vocabulary size of 57,580 and 201M parameters.
+The training configuration includes 10 epochs, validation performed every epoch, gradient clipping at 2.0, 800 training samples per epoch, a learning rate of 8e-6, batch sizes of 16 for both training and validation, 400 warmup steps, and 16-bit mixed precision.
+
+\indent{\textbf{Results}.} The training and validation losses of Donut during fine-tuning are depicted in \figref{fig:donut_loss}.
+The training loss decreases rapidly, while the validation loss remains high, indicating overfitting.
+The overfitting is likely due to the limited number of leaflet layouts in the training data, which restricts the model's ability to generalize to unseen layouts.
+This issue is visually less pronounced, as the text is relatively consistent across leaflets, but textually, the model struggles to generalize due to the diverse language and layout variations.
+
+\begin{figure*}[h!]
+    \begin{tabular}{cc}
+    \includegraphics[width=0.4\linewidth]{figures/donut_train_loss.png} &\includegraphics[width=0.4\linewidth]{figures/donut_val_loss.png} \\
+    (a) Training Loss & (b) Validation Loss \\[6pt]
+    \end{tabular}
+    \caption{Training and Validation Loss of Donut during Fine-Tuning.}
+    \label{fig:donut_loss}
+\end{figure*}
+
+\subsection{Comparison of Hybrid OCR+LLM, Donut, and LVLM}
+
+This section presents a comparative evaluation of a hybrid OCR+LLM pipeline against end-to-end models, specifically Donut and Large Vision-Language Models (LVLMs), for information extraction (IE) from supermarket leaflets.
+The assessment focuses on model performance using the best OCR+LLM configuration and two end-to-end approaches.
+
+\subsubsection{Experimental Setup}
+
+The evaluation framework was designed to compare the performance of three distinct model categories: OCR+LLM pipelines, end-to-end Vision Encoder-Decoder models, and large vision-language models (LVLMs).
+For the OCR+LLM approach, DocTR served as the OCR engine, paired with Qwen 2.5-7B and LLaMA 3.1-8B as the large language models, selected for their comparable performance.
+The Donut model, an end-to-end Vision Encoder-Decoder architecture optimized for document understanding, was included to assess its capabilities in handling structured document data.
+Additionally, MiniCPM-V \cite{yao2024} and LLaMA 3.2-Vision \cite{touvron2023} were chosen as representative LVLMs to evaluate their multimodal reasoning abilities.
+
+The evaluation was conducted on the Leaflet-IE validation subset, as Donut had already been trained on the training subset, ensuring a fair comparison across models.
+Performance was measured using two key metrics: (1) \textbf{Accuracy}, defined as the percentage of correctly extracted entity values, and (2) \textbf{Levenshtein Distance}, which quantifies the edit distance between predicted and ground truth values at the entity level.
+To maintain consistency, the same normalization approach employed in the OCR+LLM evaluation was applied uniformly to both model predictions and ground truth values.
+This setup ensured a rigorous and standardized comparison of model performance across the selected metrics.
+
+\paragraph{Per-Entity Accuracy and Levenshtein Distance}  
+The evaluation of per-entity accuracy and Levenshtein distance reveals distinct performance patterns across models, as illustrated in \figref{fig:eval_final_acc_raw} and \figref{fig:eval_final_levdis_raw}.
+Without normalization, the OCR+LLM pipeline performed significantly worse than Donut and LVLMs, achieving near 0\% accuracy for original and deal price entities, while LVLMs outperformed all models, particularly in price extraction, due to their ability to leverage spatial and contextual cues.
+Donut trailed closely but showed a notable drop in brand recognition accuracy.
+Levenshtein distance metrics mirrored these trends, with LVLMs and Donut exhibiting low distances, indicating high precision, while OCR+LLM struggled, especially with brand names, which consistently had the highest distances across models.
+
+\begin{figure*}[h!]
+    \centering
+    \includegraphics[width=0.8\linewidth]{figures/accuracies_raw.png}
+    \caption{Per-Entity Accuracy without normalization. a: Donut, b: docTR + Qwen 2.5 [7b, Q4], c: docTR + Llama 3.1 [8b, Q4], d: MiniCPM-V, e: Llama3.2-Vision.}
+    \label{fig:eval_final_acc_raw}
+\end{figure*}
+
+\begin{figure*}[h!]
+    \centering
+    \includegraphics[width=0.8\linewidth]{figures/levdistances_raw.png}
+    \caption{Per-Entity Levenshtein Distance without normalization. a: Donut, b: docTR + Qwen 2.5 [7b, Q4], c: docTR + Llama 3.1 [8b, Q4], d: MiniCPM-V, e: Llama3.2-Vision.}
+    \label{fig:eval_final_levdis_raw}
+\end{figure*}
+
+Normalization significantly improved results, as shown in \figref{fig:eval_final_acc_norm} and \figref{fig:eval_final_levdis_norm}, particularly for OCR+LLM, which saw its price detection accuracy surpass Donut in some cases.
+However, OCR+LLM remained inferior to LVLMs and Donut overall.
+Donut displayed stable and balanced accuracy across entities, while LVLMs, despite higher variance, maintained their lead, excelling in price extraction.
+Post-normalization, Levenshtein distances decreased across all models, with OCR+LLM showing the most substantial reduction.
+LVLMs achieved the lowest distances but with higher variance, whereas Donut demonstrated remarkable consistency.
+Despite these improvements, brand names continued to exhibit the highest Levenshtein distances, highlighting the persistent challenge of accurately extracting this entity even after normalization.
+These results, visualized in the referenced figures, underscore the strengths of LVLMs in leveraging multimodal cues and the robustness of Donut, while revealing the limitations of OCR+LLM pipelines in handling complex, noisy leaflet data.
+
+\begin{figure*}[h!]
+    \centering
+    \includegraphics[width=0.8\linewidth]{figures/accuracies_norm.png}
+    \caption{Per-Entity Accuracy with normalization. a: Donut, b: docTR + Qwen 2.5 [7b, Q4], c: docTR + Llama 3.1 [8b, Q4], d: MiniCPM-V, e: Llama3.2-Vision.}
+    \label{fig:eval_final_acc_norm}
+\end{figure*}
+
+\begin{figure*}[h!]
+    \centering
+    \includegraphics[width=0.8\linewidth]{figures/levdistances_norm.png}
+    \caption{Per-Entity Levenshtein Distance with normalization. a: Donut, b: docTR + Qwen 2.5 [7b, Q4], c: docTR + Llama 3.1 [8b, Q4], d: MiniCPM-V, e: Llama3.2-Vision.}
+    \label{fig:eval_final_levdis_norm}
+\end{figure*}
+
+\indent{\textbf{Dicussion.}} The evaluation highlights distinct strengths and limitations across the tested models.
+LVLMs emerged as the most effective for information extraction (IE) tasks, particularly when spatial and visual context is critical.
+However, their superior performance comes at the cost of significantly higher computational requirements, making them less practical for resource-constrained environments.
+Donut offers a compelling trade-off between accuracy and efficiency, demonstrating strong performance despite limited training resources.
+With further optimization, Donut has the potential to surpass LVLMs for this specific task, though its generalization ability remains narrower compared to LVLMs, which excel across a broader range of tasks.
+
+In contrast, the OCR+LLM pipeline proved considerably weaker than both LVLMs and Donut.
+This performance gap stems from several factors: (1) the lack of spatial and visual information, which limits its ability to resolve ambiguities; (2) error propagation from the OCR stage to the LLM, compounding inaccuracies; and (3) insufficient training data to achieve robust IE performance.
+Despite these limitations, OCR+LLM remains a viable option for scenarios with constrained computational resources and moderate task complexity, where its simplicity and lower resource demands may outweigh its performance drawbacks.
 
 \section{Application}
+\label{sec:application}
+The ability to detect deals from a wide range of supermarket leaflets provides the foundation for extracting structured information and building a centralized deal database.
+If all components, from deal detection to information extraction, function reliably, this enables the creation of a comprehensive repository containing deals from various supermarkets, based solely on the content of their weekly unstructured leaflets.
+Such a structured database allows for numerous applications, including price trend analysis, intelligent shopping list generation and deal comparison across stores.
+The immediate objective of this project was to develop a system that could automatically collect, process and present extracted deals in a structured manner.
+The resulting application is designed to scrape supermarket leaflets weekly, detect deals using the trained YOLO-based model and extract relevant metadata, including product names and prices.
+These extracted deals are then stored in a structured format within a database and made accessible through a web-based interface.
+
+\subsection{Database}
+\begin{figure*}[h!]
+    \centering
+    \includegraphics[width=0.8\linewidth]{figures/application/db_uml.png}
+    \caption{Database schema for storing metadata for supermarket leaflets and extracted deals.}
+    \label{fig:application_db_uml}
+\end{figure*}
+For storing the extracted deals, a lightweight and efficient solution was required.
+SQLite was chosen due to its simplicity and fast performance, making it well-suited for handling the structured but relatively small-scale dataset.
+After several weeks of scraping supermarket leaflets, the dataset grew to include 540 leaflets from 20 different supermarkets.
+The database is structured into three primary tables (cf.
+Figure \ref{fig:application_db_uml}): one for supermarket metadata, one for storing the leaflets and one containing the extracted deals.
+The total number of extracted deals in the database adds up to 47,829.
+Among these, the vast majority (46,869) are classified as standard deals, while 607 fall under product category deals, 144 correspond to coupons and 208 belong to miscellaneous categories.
+Since the structure and content of non-standard deals often differ significantly from regular deals featuring loyalty points, bulk discounts, or percentage-based reductions across entire product groups, the primary focus remains on standard deals.
+By structuring the data efficiently, the database serves as a robust backend for the subsequent web application, facilitating fast queries and scalable deal retrieval.
+
+\subsection{Web User Interface}
+\begin{figure*}[h!]
+    \centering
+    \includegraphics[width=0.8\linewidth]{figures/application/deals_overview.png}
+    \caption{Web-based application interface for browsing all extracted supermarket deals with search and filter functionality.}
+    \label{fig:application_web_overview}
+\end{figure*}
+
+Building on the database, a web-based application was developed to provide users with an interactive way to explore supermarket deals, which is shown in Figure \ref{fig:application_web_overview}.
+The core functionality centers around an intuitive search system that allows users to find deals based on specific product names.
+Additionally the interface supports filtering options, enabling users to refine searches by supermarket chain or deal validity period.
+Each deal is displayed with its corresponding image snippet, extracted metadata, and pricing information, making it easy to compare offers across different retailers.
+
+\begin{figure*}[h!]
+    \centering
+    \begin{tabular}{cc}
+    \includegraphics[width=0.45\linewidth]{figures/application/leaflet_segmentations.png} &   \includegraphics[width=0.45\linewidth]{figures/application/single_deal.png} \\
+    (a) Interactive leaflet segmentation & (b) Detailed view of a single deal \\[2pt]
+    \end{tabular}
+    \caption{Additional features of the web application, including interactive uploading of pdf leaflets and detailed deal views by clicking on individual deals.}
+    \label{fig:application_combined}
+\end{figure*}
+
+Beyond static deal browsing, the application also incorporates an upload feature that enables users to submit entire supermarket leaflets for processing.
+When a leaflet is uploaded, the system applies the full processing pipeline, from deal detection using YOLO to information extraction.
+The processed leaflet can then be browsed interactively, displaying detected deals with their segmentation masks overlaid on the original pages.
+This feature provides direct insights into the model’s performance, allowing users to verify the accuracy of detected promotions and extracted information.
+The efficiency of the application benefits from YOLO’s lightweight architecture, ensuring that leaflet processing remains fast and responsive.
+After a short processing time, users can navigate through detected deals and inspect the segmentation masks applied to the leaflet images.
+Clicking on an individual deal reveals extracted details such as the product name, price, and other metadata.
+The combination of automated deal extraction and interactive visualization makes the web application a practical tool for structured deal exploration and comparison.
 
 \section{Conclusion}
+\label{sec:conclusion}
     \subsection{Summary}
+    This work presents a comprehensive approach to the digitalization and structuring of supermarket leaflet information.
+The proposed modular pipeline encompasses deal detection and information extraction, transforming raw leaflet data into structured, actionable insights.
+The deal detection module leverages advanced YOLO-based models to accurately identify and segment deals within leaflets, while the information extraction module employs state-of-the-art OCR, LLM, and end-to-end models to extract and normalize deal attributes.
+The developed interactive application, backed by a robust database, allows users to browse, filter, and compare deals across multiple supermarket chains, providing a proof of concept for practical applications.
+Additionally, the research contributes two datasets: one for deal detection as instance segmentation and another for image-based information extraction, facilitating further research in this domain.
+
     \subsection{Future Work}
-    ww
+    This project opens up several avenues for future research and development to enhance the system's capabilities and usability.
 
-% Bibliography entries for the entire Anthology, followed by custom entries
-%\bibliography{anthology,custom}
-% Custom bibliography entries only
+    Firstly, enhancing the performance and runtime of the deal detection module is crucial.
+This involves optimizing the existing YOLO-based model and exploring alternative architectures that may offer better accuracy and efficiency.
+
+    Secondly, the information extraction (IE) component can be significantly improved by building a larger dataset specifically for training the Donut model.
+Given the promising results achieved with Donut, expanding the dataset and fine-tuning the model further could yield competitive results in extracting structured information from supermarket leaflets.
+
+    Additionally, several new branches of research and development can be pursued.
+These include the deal specification and product image extraction to build a comprehensive database, brand and product name normalization for database mapping, and time series analysis for price trend prediction.
+On the application side, scalability, frontend improvements, and additional features such as a recommendation engine and automatic weekly deal extraction can enhance user experience and system robustness.
+
 \bibliography{references}
+\newpage
+
+\appendix
+\section*{Appendices}
+\numberwithin{figure}{section}
+\numberwithin{table}{section}
+\addcontentsline{toc}{section}{Appendices}
+\renewcommand{\thesubsection}{\Alph{subsection}}
+
+\subsection{OCR Evaluation: Normalization Procedure}
+\label{app:ocr_normalization}
+The procedure is implemented as a multi-level function, where each level applies increasingly rigorous transformations.
+Below, we provide a detailed explanation of the normalization steps and present the procedure in pseudocode.
+
+\begin{algorithm}[H]
+\caption{Text Normalization Function}
+\label{alg:normalization}
+\begin{algorithmic}[1]
+\Require Input text $text$, normalization level $level$ (default: 6)
+\Ensure Normalized text
+\State \textbf{Initialize}: If $text$ is empty, null, or an empty string, return an empty string.
+\If{$level \geq 1$}
+    \State Strip leading and trailing whitespace from $text$.
+\EndIf
+\If{$level \geq 2$}
+    \State Convert $text$ to lowercase.
+    \State Replace newline, tab, and carriage return characters with spaces.
+    \State Normalize German characters: "ö" $\rightarrow$ "o", "ä" $\rightarrow$ "a", "ü" $\rightarrow$ "u", "ß" $\rightarrow$ "ss".
+\EndIf
+\If{$level \geq 3$}
+    \State Replace hyphens and dashes  with spaces.
+    \State Remove all non-alphanumeric characters except periods and spaces.
+    \State Collapse multiple spaces into a single space.
+\EndIf
+\If{$level \geq 4$}
+    \State Remove all spaces and periods from $text$.
+\EndIf
+\State \textbf{Return} normalized $text$.
+\end{algorithmic}
+\end{algorithm}
+
+The normalization function is applied to both OCR outputs and ground truth texts before evaluation.
+By standardizing the text at various levels, we ensure that the evaluation metrics are robust to minor formatting differences and focus on the semantic accuracy of the OCR system.
+
+\subsection{LLM Prompt for Structured Information Extraction}
+\label{app:llm_prompt}
+
+This appendix details the prompt template used to guide the Large Language Model (LLM) in extracting structured information from OCR text.
+The prompt is designed to ensure consistent and accurate extraction of supermarket deal information, including fields such as brand name, product name, original price, reduced price, and weight.
+Below, we provide the system template, instructions, and an example of the prompt in action.
+
+The system template defines the context, extraction requirements, and instructions for the LLM. It is structured as follows:
+
+\begin{verbatim}
+**Context:**  
+You are an advanced language model specializing in extracting 
+structured information from OCR text. 
+Your task is to extract one supermarket deal from the given OCR result.
+
+**Extraction Requirements:**  
+- **Fields:**  
+  - "Marke": Brand name (if explicitly mentioned)  
+  - "Produktname": Product name  
+  - "Original Preis": Original price  
+  - "Reduzierter Preis": Reduced price  
+  - "Gewicht": Weight (if available; otherwise, use null)
+
+- **Instructions:**  
+  - Return a single JSON object containing exactly one deal.
+  - Use JSON only—no additional text.
+  - If a field is missing, assign a null value.
+  - Correct OCR errors such as missing decimals (e.g., "229" → "2.29"), 
+    incorrect spellings, and OCR noise.
+  - Use contextual cues (e.g., euro symbols) to infer and correct pricing.
+
+**Example:**  
+OCR Input:                     
+Dallmayr Prodomo Kaffee gemahlen 500g 1kg=51.73 Dallmayr -24% prodomo 5 69 UVP7,49
+
+JSON OUTPUT:
+{
+    "Marke": "Dallmayr",
+    "Produktname": "Prodomo Kaffee gemahlen",
+    "Original Preis": "UVP7,49",
+    "Reduzierter Preis": "3,99 €",
+    "Gewicht": null
+}
+
+IMPORTANT: Return the JSON object in the above format only once.
+\end{verbatim}
+
+The prompt is constructed by combining the system template with the OCR input provided by the user. The structure of the prompt is as follows:
+
+\begin{verbatim}
+messages = [
+    SYSTEM_TEMPLATE,
+    {
+        "role": "user",
+        "content": f"OCR Input: {ocr_res}\nJSON OUTPUT:"
+    }
+]
+\end{verbatim}
+
+Here, \texttt{ocr\_res} represents the OCR output text, which is dynamically inserted into the prompt.
+
+\subsection{OCR + LLM Evaluation: Normalization Procedure}
+\label{app:ocr_llm_normalization}
+
+This appendix describes the normalization procedure applied to LLM-extracted data during evaluation.
+The normalization process ensures consistency by standardizing text formats, removing special characters, and correcting common OCR errors.
+Below, we provide a detailed explanation of the procedure and present the implementation in pseudocode.
+
+The normalization procedure is implemented as a Python function that performs the following steps:
+
+\begin{algorithm}[H]
+\caption{Text Normalization Procedure}
+\label{alg:final_normalization}
+\begin{algorithmic}[1]
+\Require Input text $text$
+\Ensure Normalized text
+\State \textbf{Initialize}: Define a dictionary $REPLACEMENTS$ for character replacements.
+\State $REPLACEMENTS \gets \{
+    \text{"ä"} \rightarrow \text{"a"}, \text{"ö"} \rightarrow \text{"o"}, \text{"ü"} \rightarrow \text{"u"}, 
+    \text{"ß"} \rightarrow \text{"ss"}, \text{","} \rightarrow \text{"."}, \text{"€"} \rightarrow \text{""}, 
+    \text{"ô"} \rightarrow \text{"o"}, \text{"é"} \rightarrow \text{"e"}, \text{"ç"} \rightarrow \text{"c"}, 
+    \text{"è"} \rightarrow \text{"e"}, \text{"à"} \rightarrow \text{"a"}, \text{"ê"} \rightarrow \text{"e"}, 
+    \text{"â"} \rightarrow \text{"a"}, \text{"û"} \rightarrow \text{"u"}, \text{"î"} \rightarrow \text{"i"}, 
+    \text{"ë"} \rightarrow \text{"e"}, \text{"ï"} \rightarrow \text{"i"}, \text{"œ"} \rightarrow \text{"oe"}, 
+    \text{"æ"} \rightarrow \text{"ae"}, \text{"ù"} \rightarrow \text{"u"}
+\}$
+\For{each $(key, value)$ in $REPLACEMENTS$}
+    \State Replace occurrences of $key$ with $value$ in $text$.
+\EndFor
+\State Filter $text$ to retain only alphanumeric characters, periods, and spaces.
+\State Remove all whitespace from $text$.
+\State Convert $text$ to lowercase.
+\State \textbf{Return} normalized $text$.
+\end{algorithmic}
+\end{algorithm}
+
+\subsection{OCR + LLM Evaluation: Entity-specific results per OCR model}
+\label{app:ocr_llm_results}
+
+This section collects further detailed results for the OCR + LLM evaluation for interested readers.
+The results are presented in the form of per-entity accuracies and Levenshtein distances for each OCR model used in the evaluation.
+The figures provide insights into the performance of each OCR model in extracting structured information from supermarket leaflets, highlighting the strengths and weaknesses of individual models across different entities.
+
+\begin{figure*}[h!]
+    \begin{tabular}{cc}
+      \includegraphics[width=0.5\linewidth]{figures/doctr_ocr_accuracies.png} &   \includegraphics[width=0.5\linewidth]{figures/tesseract_ocr_accuracies.png} \\
+    docTR & Tesseract \\[6pt]
+        \includegraphics[width=0.5\linewidth]{figures/easyocr_ocr_accuracies.png} &   \includegraphics[width=0.5\linewidth]{figures/ppocr_ocr_accuracies.png} \\
+    EasyOCR & PaddleOCR \\[6pt]
+    \end{tabular}
+    \caption{LLM accuracies per Entity for different OCR models. a: Llama 3.1 [8b, Q4], b: Qwen 2.5 [1.5b, Q8], c: Llama 3.2 [3b, Q8], d: Qwen 2.5 [7b, Q4].}
+    \label{fig:eval_ocr_llm_accuracies}
+\end{figure*}
+
+\begin{figure*}[h!]
+    \begin{tabular}{cc}
+        \includegraphics[width=0.5\linewidth]{figures/doctr_ocr_levdistances.png} &   \includegraphics[width=0.5\linewidth]{figures/tesseract_ocr_levdistances.png} \\
+    docTR & Tesseract \\[6pt]
+        \includegraphics[width=0.5\linewidth]{figures/easyocr_ocr_levdistances.png} &   \includegraphics[width=0.5\linewidth]{figures/ppocr_ocr_levdistances.png} \\
+    EasyOCR & PaddleOCR \\[6pt]
+    \end{tabular}
+    \caption{LLM Levenshtein Distances per Entity for different OCR models. a: Llama 3.1 [8b, Q4], b: Qwen 2.5 [1.5b, Q8], c: Llama 3.2 [3b, Q8], d: Qwen 2.5 [7b, Q4].}
+    \label{fig:eval_ocr_llm_levdistances}
+\end{figure*}
 

### 2025-02-25 paper/main.tex
Updates on paper

@@
 The modern shopper expects convenience, efficiency, and instant access to information, yet the digital transformation of supermarket leaflets in Germany lags significantly behind, even despite the existence of applications that centralize digital versions of these leaflets.
-The majority of these applications' digital leaflets are plain documents, failing to leverage the full potential of interactivity, searchability, and intelligent recommendation systems.
-
-Furthermore, while price comparison websites and applications have become commonplace for electronics, fashion, and travel, the grocery sector remains an overlooked frontier.
-Consumers are often left navigating multiple supermarket websites or manually cross-referencing prices to find the best deals—a tedious and inefficient process.
-A comprehensive digital ecosystem that integrates grocery price comparisons, personalized discounts, and AI-driven shopping assistants could bridge this gap and act as a workaround, offering an enhanced, data-driven shopping experience and a tool that allows consumers to create a dynamic shopping list, track price trends over time, and receive real-time updates on the best deals.
+The majority of these digital leaflets are plain documents, failing to leverage the full potential of interactivity, searchability and intelligent recommendation systems.
+
+Furthermore, while price comparison websites and applications have become commonplace for electronics, fashion and travel, the grocery sector remains an overlooked frontier.
+Consumers are often left navigating multiple supermarket websites or manually cross-referencing prices to find the best deals.
+This is often a tedious and inefficient process.
+A comprehensive digital ecosystem that integrates grocery price comparisons, personalized discounts and AI-driven shopping assistants could bridge this gap and act as a workaround, offering an enhanced, data-driven shopping experience and a tool that allows consumers to create a dynamic shopping list, track price trends over time, and receive real-time updates on the best deals.
 
@@
 \begin{enumerate}
+    \item Gathering a diverse set of supermarket leaflets from various retailers.
     \item Detecting and separating deals $p$ from the leaflet $L$.
@@
     \item Validating the extracted information to ensure accuracy.
+    \item Storing the extracted information in a structured format for efficient querying and comparison.
+    \item Developing an interactive application for browsing and comparing deals across multiple supermarket chains.
 \end{enumerate}
@@
 To enhance usability, an \emph{interactive application} is developed that allows consumers to browse, filter, and compare deals across multiple supermarket chains.
-It provides essential search, tracking, and comparison features for improved deal discovery.
+In addition, a feature allows an entire leaflet to be uploaded and the entire pipeline to be run in order to examine the deals in detail.
+This application serves as a proof of concept for the proposed system and demonstrates its practical utility.
 
@@
 These models are able to recognize objects in images and mark them with bounding boxes and further classify them.
-But because there is no direct research on the detection of deals in supermarket leaflets, the research has to be done in this area.
+% TODO: Add more advanced methods for object/instant segmentation
 
@@
 Additionally, typography challenges, such as superscripted decimals, struck-through original prices, and font inconsistencies between deals and regular text, further complicate the extraction process.
-Overlapping elements, where text is occluded by product images or graphical overlays, violate the assumptions of Optical Character Recognition (OCR) systems, which assume planar text.
+Overlapping elements, where text is occluded by product images or graphical overlays, violate the assumptions of OCR systems, which assume planar text.
 
@@
 These leaflets provide a more standardized input format and can be systematically downloaded using an automated script.
+% TODO: add url source
 
@@
 The primary focus remains on supermarkets that sell groceries and drugstore products, as these are the most relevant for the intended applications.
-Each leaflet page contains multiple distinct offers, which must be individually detected.
+Each leaflet page contains multiple distinct deals, which must be individually detected.
 This is achieved through object detection techniques, which can either utilize bounding boxes or instance segmentation.
-While bounding box detection provides a straightforward way to localize deals, it often struggles with overlapping offers, leading to incorrect classifications.
-Instance segmentation is therefore the preferred approach, as it allows for more precise extraction of deal regions without interference from neighboring offers.
-Deals in the dataset are categorized into four main classes:
+While bounding box detection provides a straightforward way to localize deals, it often struggles with overlapping deals, which can lead to inaccurate information extraction and misclassification of deals later on.
+Instance segmentation is therefore the preferred approach, as it allows for more precise extraction of deal regions without interference from neighboring deals.
+Deal Objects in the dataset are categorized into four main classes:
 
@@
 Depending on the training requirements, annotations can be converted between bounding boxes and segmentation masks, although segmentation masks provide a more granular representation.
+
+% TODO: Referenz auf untenstehende Figures.
 
@@
 
-To extract these entities, one aims to learn a function $f(\cdot)$ that maps an input image $I$ to the desired outputs:
+To extract these entities, the target is to learn a function $f(\cdot)$ that maps an input image $I$ to the desired outputs:
 \begin{equation}
@@
 Although effective in certain scenarios, these approaches suffer from inherent limitations, including computational overhead, error propagation, and suboptimal performance on edge cases.
-Recent advancements in large language models (LLMs) have led to the development of hybrid OCR-LLM architectures, which combine the precision of optical character recognition (OCR) with the contextual reasoning capabilities of LLMs.
+Recent advancements in LLMs have led to the development of hybrid OCR-LLM architectures, which combine the precision of OCR with the contextual reasoning capabilities of LLMs.
 Below, we formalize these approaches and discuss their strengths and limitations.
@@
 This is typically achieved through rule-based systems or sequence-to-sequence models that generate key-value pairs from the recognized text.
-The output is a set of structured entities $ \{y_i\}_{i=1}^{N} $, where each $ y_i $ represents a specific entity (e.g., product name, price, unit).
+The output is a set of structured entities $ \{y_i\}_{i=1}^{N} $, where each $ y_i $ represents one of the desired attributes.
 
@@
 \indent{\textbf{Large Vision-Language Models (LVLMs)}.} In the realm of upscaling language models into LLMs, computer vision utilizes this trend to process multimodal data.
-LVLMs like Llama 3.2 Vision \cite{touvron2023} scale this framework by integrating pretrained vision encoders with large language models (LLMs).
+LVLMs like Llama 3.2 Vision \cite{touvron2023} scale this framework by integrating pretrained vision encoders with LLMs.
 These architectures utilize \emph{cross-modal projection}, which aligns visual features with the LLM's embedding space, and \emph{multimodal decoding}, which attends to both visual tokens and textual prompts.
@@
     \centering
-    \caption{Leaflet-IE Dataset}
+    \caption{Leaflet-IE Dataset with a sum of 372 annotated deals.}
     \label{tab:ie_dataset}
@@
     \midrule
-    \code{image\_id}        & 372  \\
     \code{brand}            & 357  \\
@@
     \code{deal\_price}      & 372  \\
-    \code{weight}           & 369  \\
+    \code{unit}           & 369  \\
     \bottomrule
@@
 Each image is annotated with a corresponding label file that includes the desired entities as well as the image identificator.
-The dataset is split into a training (\~{} 80\%) and a validation set (\~{} 20\%) for each model to be trained and evaluated on.
+The dataset is split into a training (\~{} 80\%)
+and a validation set (\~{} 20\%) for each model to be trained and evaluated on.
 \tabref{tab:ie_dataset} provides an overview of the dataset with the sample size for each entity and \figref{fig:ie_dataset_samples} shows some sample images with their annotations.
@@
 However, as the reader may notice, the dataset is solely focused on single product deals at this point and explicitly does not include
+% TODO: Missing Text (ILYI)
 
@@
 
-The experiments aim to identify the most effective methodology for extracting structured information from supermarket leaflets by evaluating three candidate approaches: (1) Hybrid OCR + LLM pipelines, (2) end-to-end Vision-Encoder-Decoder models, and (3) Large Vision-Language Models (LVLMs).
+% TODO: Remove cause of ambiguity? (ILYI)
+% The experiments aim to identify the most effective methodology for extracting structured information from supermarket leaflets by evaluating three candidate approaches: (1) Hybrid OCR + LLM pipelines, (2) end-to-end Vision-Encoder-Decoder models, and (3) LVLMs.
 The evaluation is structured into four sequential phases to systematically assess performance and scalability.
@@
 for leveraging pre-trained models, ollama \footnote{\href{https://ollama.com/}{https://ollama.com/}}
-and lmstudio \footnote{\href{https://lmstudio.ai/}{https://lmstudio.ai/}} for large language models and large vision-language models, and OpenCV \footnote{\href{https://opencv.org/}{https://opencv.org/}} for image preprocessing and data augmentation, as well as various other libraries for data pre-and post-processing, visualization, data management and monitoring \footnote{The codebase is available at \href{https://github.com/ilyii/leaflets}{https://github.com/ilyii/leaflets}}.
+and lmstudio \footnote{\href{https://lmstudio.ai/}{https://lmstudio.ai/}} for LVLMs, and OpenCV \footnote{\href{https://opencv.org/}{https://opencv.org/}} for image preprocessing and data augmentation, as well as various other libraries for data pre-and post-processing, visualization, data management and monitoring \footnote{The codebase is available at \href{https://github.com/ilyii/leaflets}{https://github.com/ilyii/leaflets}}.
+% TODO: Remove this section or move it to the appendix or introduction because it is also relevant for deal detection chapter? (ILYI)
 
@@
 Therefore, the normalization procedure can be thought of as a gradual alignment of the OCR output to the ground truth to investigate the OCR model's robustness to different normalization levels.
-The reader is referred to \secref{app:ocr_normalization} for a detailed description of the normalization procedure.
+A detailed description of the normalization procedure can be found in \secref{app:ocr_normalization}.
 
@@
 
-In addition to evaluating the OCR capabilities, the performance of OCR models was assessed in conjunction with large language models (LLMs).
+In addition to evaluating the OCR capabilities, the performance of OCR models was assessed in conjunction with LLMs.
 The primary objectives were to determine the most effective OCR-LLM combination for information extraction and to evaluate the impact of different OCR models on the LLM's performance.
@@
 The LLMs are expected to handle such inconsistencies and errors in the input.
-Instead, here the entity values were evaluated in both raw form and with a normalization applied for the comparability between the LLM prediction and the ground truth value .
+Instead, here the entity values were evaluated in both raw form and with a normalization applied for the comparability between the LLM prediction and the ground truth value.
 The normalization procedure includes usual character replacements and filtering based on linguistic artifacts commonly encountered in OCR errors.
@@
 The training loss decreases rapidly, while the validation loss remains high, indicating overfitting.
-The overfitting is likely due to the limited number of leaflet layouts in the training data, which restricts the model's ability to generalize to unseen layouts.
-This issue is visually less pronounced, as the text is relatively consistent across leaflets, but textually, the model struggles to generalize due to the diverse language and layout variations.
+The overfitting is likely due to the limited number of deal layouts in the training data, which restricts the model's ability to generalize to unseen layouts.
+This issue is visually less pronounced, as the text is relatively consistent across deals, but textually, the model struggles to generalize due to the diverse language and layout variations.
+Another problem is that the model is not pretrained on the German language, which may further hinder its performance.
 
@@
 
-This section presents a comparative evaluation of a hybrid OCR+LLM pipeline against end-to-end models, specifically Donut and Large Vision-Language Models (LVLMs), for information extraction (IE) from supermarket leaflets.
+This section presents a comparative evaluation of a hybrid OCR+LLM pipeline against end-to-end models, specifically Donut and LVLMs, for IE from supermarket deals.
 The assessment focuses on model performance using the best OCR+LLM configuration and two end-to-end approaches.
@@
 \subsubsection{Experimental Setup}
-
-The evaluation framework was designed to compare the performance of three distinct model categories: OCR+LLM pipelines, end-to-end Vision Encoder-Decoder models, and large vision-language models (LVLMs).
+% TODO: Remove \subsection{Comparison of Hybrid OCR+LLM, Donut, and LVLM} because it is the same as the following? (ILYI)
+The evaluation framework was designed to compare the performance of three distinct model categories: OCR+LLM pipelines, end-to-end Vision Encoder-Decoder models, and LVLMs.
 For the OCR+LLM approach, DocTR served as the OCR engine, paired with Qwen 2.5-7B and LLaMA 3.1-8B as the large language models, selected for their comparable performance.
@@
 
-The evaluation was conducted on the Leaflet-IE validation subset, as Donut had already been trained on the training subset, ensuring a fair comparison across models.
-Performance was measured using two key metrics: (1) \textbf{Accuracy}, defined as the percentage of correctly extracted entity values, and (2) \textbf{Levenshtein Distance}, which quantifies the edit distance between predicted and ground truth values at the entity level.
-To maintain consistency, the same normalization approach employed in the OCR+LLM evaluation was applied uniformly to both model predictions and ground truth values.
+The evaluation was conducted on the Leaflet-IE validation subset, ensuring a fair comparison across the models.
+Donut had already been fine-tuned on the training subset.
+The same metrics, accuracy and Levenshtein distance, were employed to assess model performance.
+To maintain consistency, the same normalization approach used in the OCR+LLM evaluation was applied uniformly to both model predictions and ground truth values.
 This setup ensured a rigorous and standardized comparison of model performance across the selected metrics.
@@
 \indent{\textbf{Dicussion.}} The evaluation highlights distinct strengths and limitations across the tested models.
-LVLMs emerged as the most effective for information extraction (IE) tasks, particularly when spatial and visual context is critical.
+LVLMs emerged as the most effective for IE tasks, particularly when spatial and visual context is critical.
 However, their superior performance comes at the cost of significantly higher computational requirements, making them less practical for resource-constrained environments.
@@
 The processed leaflet can then be browsed interactively, displaying detected deals with their segmentation masks overlaid on the original pages.
-This feature provides direct insights into the model’s performance, allowing users to verify the accuracy of detected promotions and extracted information.
-The efficiency of the application benefits from YOLO’s lightweight architecture, ensuring that leaflet processing remains fast and responsive.
+This feature provides direct insights into the models performance, allowing users to verify the accuracy of detected promotions and extracted information.
+The efficiency of the application benefits from  lightweight architecture from YOLO, ensuring that leaflet processing remains fast and responsive.
 After a short processing time, users can navigate through detected deals and inspect the segmentation masks applied to the leaflet images.
@@
     \subsection{Summary}
-    This work presents a comprehensive approach to the digitalization and structuring of supermarket leaflet information.
-The proposed modular pipeline encompasses deal detection and information extraction, transforming raw leaflet data into structured, actionable insights.
-The deal detection module leverages advanced YOLO-based models to accurately identify and segment deals within leaflets, while the information extraction module employs state-of-the-art OCR, LLM, and end-to-end models to extract and normalize deal attributes.
+    This work presents a comprehensive approach to the digitalization and structuring of supermarket leaflet deals.
+The proposed modular pipeline encompasses deal detection and information extraction, transforming raw leaflet data into structured data.
+The deal detection module leverages lightweight and efficient YOLO-based models to accurately identify and segment deals within leaflets, while the information extraction module employs state-of-the-art OCR, LLM, and end-to-end models to extract and normalize deal attributes.
 The developed interactive application, backed by a robust database, allows users to browse, filter, and compare deals across multiple supermarket chains, providing a proof of concept for practical applications.
@@
 This involves optimizing the existing YOLO-based model and exploring alternative architectures that may offer better accuracy and efficiency.
-
-    Secondly, the information extraction (IE) component can be significantly improved by building a larger dataset specifically for training the Donut model.
+Also, the size of the dataset can be increased by including more leaflets from different supermarkets, which would improve the model's generalization capabilities.
+
+    Secondly, the IE component can be significantly improved by building a larger dataset specifically for training the Donut model.
 Given the promising results achieved with Donut, expanding the dataset and fine-tuning the model further could yield competitive results in extracting structured information from supermarket leaflets.
@@
 On the application side, scalability, frontend improvements, and additional features such as a recommendation engine and automatic weekly deal extraction can enhance user experience and system robustness.
+There are numerous possibilities for future work and the project serves as a foundation for further exploration in the field of supermarket deal extraction based on leaflets.
 

### 2025-02-26 paper/main.tex
Add final changes.

@@
-% !TEX root = main_ilyi.tex
+% !TEX root = main.tex
 
@@
 \end{abstract}
+
+% Table of contents
+% \tableofcontents
 
@@
 This approach penalizes models that fail to produce accurate segmentations and is particularly useful for assessing how well the model distinguishes closely packed or irregularly shaped deals.
+The implemention details can be found in \secref{app:implementation_details}.
 
@@
 Each model was trained for 20 epochs without additional data augmentation.
-The results, shown in Figure \ref{fig:all_yolo_results} (a), present the mAP50 (mask) scores for YOLOv8 and YOLOv11 in their small, medium, and large configurations.
+The results, shown in \figref{fig:all_yolo_results} (a), present the mAP50 (mask) scores for YOLOv8 and YOLOv11 in their small, medium, and large configurations.
 The findings indicate that the smallest version of YOLOv8 achieved the highest validation mAP50, outperforming larger models in this setting.
-A second analysis, visualized in Figure \ref{fig:all_yolo_results} (b), examines mAP50-95 scores for the same models, reinforcing the observation that a lightweight YOLO model is sufficient for this particular task.
+A second analysis, visualized in \figref{fig:all_yolo_results} (b), examines mAP50-95 scores for the same models, reinforcing the observation that a lightweight YOLO model is sufficient for this particular task.
 The lower performance of larger models suggests that the dataset’s structure, with relatively uniform layouts, does not require highly complex architectures to achieve strong results.
@@
 The goal was to determine whether these transformations improved the model’s ability to generalize across different leaflet layouts.
-Each augmented model was trained for ten additional epochs, and the results are displayed in Figure \ref{fig:yolo8_results}.
+Each augmented model was trained for ten additional epochs, and the results are displayed in \figref{fig:yolo8_results}.
 While certain augmentation techniques led to slight improvements in segmentation accuracy, particularly for models trained with random translations, the overall best-performing model remained the one trained without any augmentation.
@@
 
-\subsubsection{Traditional and Hybrid Approaches for Supermarket Leaflet Information Extraction}  
+\subsubsection{Traditional and Hybrid Approaches}  
 Information extraction from supermarket leaflets has traditionally been approached through a pipeline of sequential sub-tasks, each addressed by specialized systems.
@@
 
-\subsection{Dataset Creation}
+\subsection{Dataset: Leaflet-IE}
 
@@
 Even though the Leaflet-IE dataset is relatively small, the reader will be able to see that the dataset is sufficient to evaluate the performance of different IE appraoches as well as to train an competitive end-to-end model.
-However, as the reader may notice, the dataset is solely focused on single product deals at this point and explicitly does not include
-% TODO: Missing Text (ILYI)
-
+However, as the reader may notice, the dataset is solely focused on single product deals at this point and explicitly does not include more complex deals like "buy-one-get-one-free" or "buy-two-for-the-price-of-one" deals.
+In this stage, the dataset is designed to be a starting point for further research and development, and the inclusion of more complex deals is planned for future work.
 \begin{figure*}[h!]
@@
 \subsection{Experiments}
-
-% TODO: Remove cause of ambiguity? (ILYI)
-% The experiments aim to identify the most effective methodology for extracting structured information from supermarket leaflets by evaluating three candidate approaches: (1) Hybrid OCR + LLM pipelines, (2) end-to-end Vision-Encoder-Decoder models, and (3) LVLMs.
-The evaluation is structured into four sequential phases to systematically assess performance and scalability.
 
@@
 Finally, the MAIN experiment conducts a comprehensive comparison of Hybrid OCR+LLM, Donut, and LVLM approaches, analyzing their accuracy, robustness, and computational efficiency in real-world leaflet data scenarios.
-
-\subsubsection{Implementation Details}
-The experiments were conducted on two distinct computational workstations - station 1 equipped with an NVIDIA RTX 4080 GPU and station 2 with an NVIDIA GTX 1080 GPU.
-Therefore, the experiments could be conducted in parallel, ensuring efficient model training and evaluation.
-
-The software stack includegraphics Python with PyTorch\footnote{\href{https://pytorch.org/}{https://pytorch.org/}} as the primary deep learning framework, HuggingFace Transformers \footnote{\href{https://huggingface.co/transformers/}{https://huggingface.co/transformers/}}
-for leveraging pre-trained models, ollama \footnote{\href{https://ollama.com/}{https://ollama.com/}}
-and lmstudio \footnote{\href{https://lmstudio.ai/}{https://lmstudio.ai/}} for LVLMs, and OpenCV \footnote{\href{https://opencv.org/}{https://opencv.org/}} for image preprocessing and data augmentation, as well as various other libraries for data pre-and post-processing, visualization, data management and monitoring \footnote{The codebase is available at \href{https://github.com/ilyii/leaflets}{https://github.com/ilyii/leaflets}}.
-% TODO: Remove this section or move it to the appendix or introduction because it is also relevant for deal detection chapter? (ILYI)
+The hardware and software related implementation details can be found in \secref{app:implementation_details}.
 
@@
 
-\indent{\textbf{Results}.} Figure \ref{fig:eval_ocr_accuracies} presents a comparative analysis of various OCR models and normalization levels based on per-entity accuracy.
+\indent{\textbf{Results}.} \figref{fig:eval_ocr_accuracies} presents a comparative analysis of various OCR models and normalization levels based on per-entity accuracy.
 The results highlight several key trends regarding the recognition performance of different entities.
@@
 \paragraph{Results:}
-The entity-averaged accuracies and Levenshtein distances for the raw OCR output are depicted in Figures \ref{fig:eval_ocr_llm_accuracies_avg} and \ref{fig:eval_ocr_llm_levdist_avg}, respectively.
+The entity-averaged accuracies and Levenshtein distances for the raw OCR output are depicted in  \figref{fig:eval_ocr_llm_accuracies_avg} and \figref{fig:eval_ocr_llm_levdist_avg}, respectively.
 
@@
 
-\subsection{Donut Fine-Tuning Performance}
+\subsubsection{Donut Fine-Tuning Performance}
 The experiment aims to evaluate the fine-tuning performance of the Vision Encoder-Decoder model, Donut, pretrained on the CORD dataset, to determine its capability in extracting end-to-end information from supermarket leaflet deal images.
@@
 
-\subsection{Comparison of Hybrid OCR+LLM, Donut, and LVLM}
-
-This section presents a comparative evaluation of a hybrid OCR+LLM pipeline against end-to-end models, specifically Donut and LVLMs, for IE from supermarket deals.
+\subsubsection{Comparison of Hybrid OCR+LLM, Donut, and LVLM}
+
+This section presents the central comparative evaluation of a hybrid OCR+LLM pipeline against end-to-end models, specifically Donut and LVLMs, for IE from supermarket deals.
 The assessment focuses on model performance using the best OCR+LLM configuration and two end-to-end approaches.
 
-\subsubsection{Experimental Setup}
-% TODO: Remove \subsection{Comparison of Hybrid OCR+LLM, Donut, and LVLM} because it is the same as the following? (ILYI)
 The evaluation framework was designed to compare the performance of three distinct model categories: OCR+LLM pipelines, end-to-end Vision Encoder-Decoder models, and LVLMs.
@@
 The database is structured into three primary tables (cf.
-Figure \ref{fig:application_db_uml}): one for supermarket metadata, one for storing the leaflets and one containing the extracted deals.
+\figref{fig:application_db_uml}): one for supermarket metadata, one for storing the leaflets and one containing the extracted deals.
 The total number of extracted deals in the database adds up to 47,829.
@@
 
-Building on the database, a web-based application was developed to provide users with an interactive way to explore supermarket deals, which is shown in Figure \ref{fig:application_web_overview}.
+Building on the database, a web-based application was developed to provide users with an interactive way to explore supermarket deals, which is shown in \figref{fig:application_web_overview}.
 The core functionality centers around an intuitive search system that allows users to find deals based on specific product names.
@@
 \renewcommand{\thesubsection}{\Alph{subsection}}
+
+\subsection{Implementation Details}
+\label{app:implementation_details}
+
+The experiments were conducted on two distinct computational workstations - station 1 equipped with an NVIDIA RTX 4080 GPU and station 2 with an NVIDIA GTX 1080 GPU.
+Therefore, the experiments could be conducted in parallel, ensuring efficient model training and evaluation.
+
+The software stack includegraphics Python with PyTorch\footnote{\href{https://pytorch.org/}{https://pytorch.org/}} as the primary deep learning framework, HuggingFace Transformers \footnote{\href{https://huggingface.co/transformers/}{https://huggingface.co/transformers/}}
+for leveraging pre-trained models, ollama \footnote{\href{https://ollama.com/}{https://ollama.com/}}
+and lmstudio \footnote{\href{https://lmstudio.ai/}{https://lmstudio.ai/}} for LVLMs, and OpenCV \footnote{\href{https://opencv.org/}{https://opencv.org/}} for image preprocessing and data augmentation, as well as various other libraries for data pre-and post-processing, visualization, data management and monitoring \footnote{The codebase is available at \href{https://github.com/ilyii/leaflets}{https://github.com/ilyii/leaflets}}.
 

### 2025-03-15 report/main.tex
Cleaned up codebase.

--- 2025-02-26 paper/main.tex
@@
 However, the detection of specific elements in documents, or more generally, the detection of objects in images, is a widely researched area.
-When it comes to just the actual detection of these elements without understanding the semantic meaning, models such as YOLO or Faster R-CNN prove to be effective.
+When it comes to just the actual detection of these elements without understanding the semantic meaning, models such as YOLO (You Only Look Once) \cite{redmonYouOnlyLook2016} or Faster R-CNN \cite{renFasterRCNNRealTime2016} prove to be effective.
 These models are able to recognize objects in images and mark them with bounding boxes and further classify them.
-% TODO: Add more advanced methods for object/instant segmentation
+More advanced methods, such as Mask R-CNN \cite{heMaskRCNN2018} or additional segmentation heads for YOLO like proposed in \cite{mohamedINSTAYOLORealTimeInstance2024}, can even segment the objects in the image.
+Furthermore, more recent models, such as DETR \cite{zhuDeformableDETRDeformable2021} or RT-DETR \cite{zhaoDETRsBeatYOLOs2024a}, have shown promising results in object detection tasks using transformer-based architectures.
+So there is a wide range of models available for the task of object detection and segmentation in general, which can be investigated for the task of deal detection in supermarket leaflets.
 
@@
 These leaflets provide a more standardized input format and can be systematically downloaded using an automated script.
-% TODO: add url source
+For this purpose, a web scraper was developed to download the leaflets from the website \url{https://www.prospektangebote.de/}.
 
@@
 Object detection models can be broadly categorized into multi-stage (multi-shot) detectors and single-stage (single-shot) detectors.
-Multi-stage detectors, such as the R-CNN family (R-CNN, Fast R-CNN, Faster R-CNN, Mask R-CNN), follow a sequential process.
+Multi-stage detectors, such as the R-CNN family (R-CNN \cite{girshickRichFeatureHierarchies2014a}, Fast R-CNN \cite{girshickFastRCNN2015}, Faster R-CNN, Mask R-CNN), follow a sequential process.
 First, they generate a set of region proposals, indicating potential object locations.
@@
 While this method achieves high accuracy, it introduces significant computational overhead.
-Earlier versions, such as R-CNN, even relied on separate, non-learnable algorithms for proposal generation.
+Earlier versions, such as R-CNN, even relied on separate, non-learnable algorithms for proposal generation \cite{uijlingsSelectiveSearchObject2013}.
 Faster R-CNN improved efficiency by integrating the Region Proposal Network (RPN) directly into the model, eliminating the need for external proposal algorithms.
 However, even this approach remains computationally demanding.
-In contrast, single-stage detectors, such as YOLO (You Only Look Once), perform detection in a single forward pass, predicting object locations and classifications simultaneously.
+In contrast, single-stage detectors, such as YOLO, perform detection in a single forward pass, predicting object locations and classifications simultaneously.
 This significantly reduces inference time, making these models well-suited for real-time applications.
@@
 
-The YOLO model follows a grid-based detection approach, where the input image is divided into an SxS grid.
+The YOLO model follows a grid-based detection approach, where the input image is divided into an $S \times S$ grid.
 Each grid cell is processed for predicting objects whose centers fall within it.
 Instead of relying on separate region proposal mechanisms, YOLO processes the image in a single forward pass, directly predicting bounding box coordinates, confidence scores, and class probabilities per grid cell.
-The bounding boxes are parameterized by their center coordinates, width, and height, while the confidence scores indicate the model’s certainty that a given bounding box contains an object.
+The bounding boxes are parameterized by their center coordinates, width, and height, while the confidence scores indicate the model's certainty that a given bounding box contains an object.
 The class probabilities further specify which category the detected object belongs to.
@@
 The segmentation head shares feature representations with the object detection components, ensuring efficient training and inference.
-This method enhances the model’s ability to isolate individual deals even in cluttered layouts, making it particularly suited for supermarket leaflets where offers frequently overlap or appear with complex backgrounds.
+This method enhances the model's ability to isolate individual deals even in cluttered layouts, making it particularly suited for supermarket leaflets where offers frequently overlap or appear with complex backgrounds.
 
@@
 This approach penalizes models that fail to produce accurate segmentations and is particularly useful for assessing how well the model distinguishes closely packed or irregularly shaped deals.
+
+For the experiments, the \emph{YOLOv8} and \emph{YOLOv11} models were selected, as they are the most recent and widely used architectures in the YOLO family which support instance segmentation with available pretrained weights.
 The implemention details can be found in \secref{app:implementation_details}.
@@
 A second analysis, visualized in \figref{fig:all_yolo_results} (b), examines mAP50-95 scores for the same models, reinforcing the observation that a lightweight YOLO model is sufficient for this particular task.
-The lower performance of larger models suggests that the dataset’s structure, with relatively uniform layouts, does not require highly complex architectures to achieve strong results.
+The lower performance of larger models suggests that the dataset's structure, with relatively uniform layouts, does not require highly complex architectures to achieve strong results.
 
@@
 Various augmentation strategies were applied, including translation, scaling, horizontal flipping, and color transformations.
-The goal was to determine whether these transformations improved the model’s ability to generalize across different leaflet layouts.
+The goal was to determine whether these transformations improved the model's ability to generalize across different leaflet layouts.
 Each augmented model was trained for ten additional epochs, and the results are displayed in \figref{fig:yolo8_results}.
@@
 The final model selection was based on the combination of high segmentation accuracy and computational efficiency.
-Given the results, \emph{YOLOv8s} was chosen as the preferred model, as it consistently outperformed more complex variants while maintaining a lower computational cost.
-The model’s ability to detect deals with high precision makes it a strong candidate for further applications.
+Given the results, YOLOv8s was chosen as the preferred model, as it consistently outperformed more complex variants while maintaining a lower computational cost.
+The model's ability to detect deals with high precision makes it a strong candidate for further applications.
 And this is particularly important because everything else builds on it.
@@
 The immediate objective of this project was to develop a system that could automatically collect, process and present extracted deals in a structured manner.
-The resulting application is designed to scrape supermarket leaflets weekly, detect deals using the trained YOLO-based model and extract relevant metadata, including product names and prices.
+The resulting application is designed to scrape supermarket leaflets weekly, detect deals using the trained YOLO model and extract relevant metadata, including product names and prices.
 These extracted deals are then stored in a structured format within a database and made accessible through a web-based interface.
@@
     Firstly, enhancing the performance and runtime of the deal detection module is crucial.
-This involves optimizing the existing YOLO-based model and exploring alternative architectures that may offer better accuracy and efficiency.
+This involves optimizing the existing YOLO-based model and exploring alternative architectures that may offer better accuracy and efficiency like transformer based architectures like DETR.
 Also, the size of the dataset can be increased by including more leaflets from different supermarkets, which would improve the model's generalization capabilities.
@@
 
+\newpage
 \bibliography{references}

### 2025-03-15 label_ml_backend/_wsgi.py

@@ -1,125 +1,0 @@
-import os
-import argparse
-import json
-import logging
-import logging.config
-
-# Set a default log level if LOG_LEVEL is not defined
-log_level = os.getenv("LOG_LEVEL", "INFO")
-
-logging.config.dictConfig({
-  "version": 1,
-  "disable_existing_loggers": False,  # Prevent overriding existing loggers
-  "formatters": {
-    "standard": {
-      "format": "[%(asctime)s] [%(levelname)s] [%(name)s::%(funcName)s::%(lineno)d] %(message)s"
-    }
-  },
-  "handlers": {
-    "console": {
-      "class": "logging.StreamHandler",
-      "level": log_level,
-      "stream": "ext://sys.stdout",
-      "formatter": "standard"
-    }
-  },
-  "root": {
-    "level": log_level,
-    "handlers": [
-      "console"
-    ],
-    "propagate": True
-  }
-})
-
-from label_studio_ml.api import init_app
-from model import NewModel
-
-
-_DEFAULT_CONFIG_PATH = os.path.join(os.path.dirname(__file__), 'config.json')
-
-
-def get_kwargs_from_config(config_path=_DEFAULT_CONFIG_PATH):
-    if not os.path.exists(config_path):
-        return dict()
-    with open(config_path) as f:
-        config = json.load(f)
-    assert isinstance(config, dict)
-    return config
-
-
-if __name__ == "__main__":
-    parser = argparse.ArgumentParser(description='Label studio')
-    parser.add_argument(
-        '-p', '--port', dest='port', type=int, default=9090,
-        help='Server port')
-    parser.add_argument(
-        '--host', dest='host', type=str, default='0.0.0.0',
-        help='Server host')
-    parser.add_argument(
-        '--kwargs', '--with', dest='kwargs', metavar='KEY=VAL', nargs='+', type=lambda kv: kv.split('='),
-        help='Additional LabelStudioMLBase model initialization kwargs')
-    parser.add_argument(
-        '-d', '--debug', dest='debug', action='store_true',
-        help='Switch debug mode')
-    parser.add_argument(
-        '--log-level', dest='log_level', choices=['DEBUG', 'INFO', 'WARNING', 'ERROR'], default=log_level,
-        help='Logging level')
-    parser.add_argument(
-        '--model-dir', dest='model_dir', default=os.path.dirname(__file__),
-        help='Directory where models are stored (relative to the project directory)')
-    parser.add_argument(
-        '--check', dest='check', action='store_true',
[…]

### 2025-03-15 label_ml_backend/model.py

@@ -1,87 +1,0 @@
-from typing import List, Dict, Optional
-from label_studio_ml.model import LabelStudioMLBase
-from label_studio_ml.response import ModelResponse
-from PIL import Image
-from ultralytics import YOLO
-import os
-
-
-
-class NewModel(LabelStudioMLBase):
-    """Custom ML Backend model
-    """
-
-    def setup(self):
-        """Configure any parameters of your model here
-        """
-        self.set("model_version", "0.0.1")
-        self.model = YOLO("models/best.pt")
-        self.cur_dir = os.path.dirname(os.path.realpath(__file__))
-
-    def predict(self, tasks: List[Dict], context: Optional[Dict] = None, **kwargs) -> ModelResponse:
-        """ Write your inference logic here
-            :param tasks: [Label Studio tasks in JSON format](https://labelstud.io/guide/task_format.html)
-            :param context: [Label Studio context in JSON format](https://labelstud.io/guide/ml_create#Implement-prediction-logic)
-            :return model_response
-                ModelResponse(predictions=predictions) with
-                predictions: [Predictions array in JSON format](https://labelstud.io/guide/export.html#Label-Studio-JSON-format-of-annotated-tasks)
-        """
-        # print(f'''\
-        # Run prediction on {tasks}
-        # Received context: {context}
-        # Project ID: {self.project_id}
-        # Label config: {self.label_config}
-        # Parsed JSON Label config: {self.parsed_label_config}
-        # Extra params: {self.extra_params}''')
-        print("HHEELLLOOOOO")
-        # example for resource downloading from Label Studio instance,
-        # you need to set env vars LABEL_STUDIO_URL and LABEL_STUDIO_API_KEY
-        # path = self.get_local_path(tasks[0]['data']['image_url'], task_id=tasks[0]['id'])
-        path = f"http://labelstudio:8080{tasks[0]['data']['image']}"
-        os.system(f'{path} -O /app/image.jpg')
-        results = self.model("/app/image.jpg")
-        os.system("rm /app/image.jpg")
-        print(results)
-
-
-        # example for simple classification
-        # return [{
-        #     "model_version": self.get("model_version"),
-        #     "score": 0.12,
-        #     "result": [{
-        #         "id": "vgzE336-a8",
-        #         "from_name": "sentiment",
-        #         "to_name": "text",
-        #         "type": "choices",
-        #         "value": {
-        #             "choices": [ "Negative" ]
-        #         }
-        #     }]
-        # }]
-
-        return ModelResponse(predictions=[])
-
[…]

### 2025-03-15 src/application/main.py

@@ -1,0 +1,342 @@
+from fastapi import FastAPI, Request, File, UploadFile, Form
+from fastapi.responses import HTMLResponse, JSONResponse
+from fastapi.staticfiles import StaticFiles
+from fastapi.templating import Jinja2Templates
+
+import sqlite3
+import os
+from dotenv import load_dotenv
+from typing import Optional
+from datetime import datetime
+import uuid
+from tqdm import tqdm
+
+from ultralytics import YOLO
+# from pdf2image import convert_from_path
+import fitz
+
+from PIL import Image, ImageDraw  # Ensure ImageDraw is imported
+from deal_processing import process_image  # import process_image from deal_processing.py
+
+SEGMENTATION_CACHE = {}
+
+load_dotenv(override=True)
+
+PROJECT_DIR = os.getenv("PROJECT_DIR", ".")
+DB_PATH = os.path.join(PROJECT_DIR, "crawled_leaflets", "supermarket_leaflets.db")
+MODELS_DIR = os.path.join(PROJECT_DIR, "models")
+DEALS_DIR = os.path.join(PROJECT_DIR, "deals")
+
+app = FastAPI()
+
+app.mount("/static", StaticFiles(directory="static"), name="static")
+app.mount(
+    "/onedrive-images",
+    StaticFiles(directory=DEALS_DIR),
+    name="onedrive-images"
+)
+YOLOV11_PATH = os.path.join(MODELS_DIR, "model.pt")
+model = YOLO(YOLOV11_PATH, verbose=False)
+
+all_images = {}
+
+for root, dirs, files in tqdm(os.walk(DEALS_DIR), desc="Loading image paths"):
+    for file in files:
+        if file.endswith(".png") and "annotated" not in file:
+            all_images[file] = f"/onedrive-images{root.replace(DEALS_DIR, '')}/{file}"
+
+templates = Jinja2Templates(directory="templates")
+
+def get_db_connection():
+    conn = sqlite3.connect(DB_PATH)
+    conn.row_factory = sqlite3.Row
+    return conn
+
+@app.get("/", response_class=HTMLResponse)
+async def read_root(request: Request):
+    # return a list of all supermarket names to filter by
+    conn = get_db_connection()
+    cursor = conn.cursor()
+    cursor.execute("SELECT name FROM supermarket")
+    supermarkets = cursor.fetchall()
+    conn.close()
+    return templates.TemplateResponse("index.html", {
+        "request": request,
[…]

### 2025-03-15 src/application/static/js/app.js

@@ -1,0 +1,154 @@
+let currentPage = 1;
+
+async function fetchDeals(page = 1) {
+    currentPage = page;
+
+    const search = document.getElementById("searchInput").value.trim();
+    const metadataOnly = document.getElementById("metadataOnly").checked;
+    const supermarket = document.getElementById("supermarketSelect").value;
+    const validOnly = document.getElementById("validOnly").checked;
+    const sortByDate = document.getElementById("sortByDate").checked;
+
+    const params = new URLSearchParams();
+    params.append("page", page);
+    if (search) params.append("search", search);
+    if (supermarket) params.append("supermarket", supermarket);
+    if (validOnly) params.append("valid_only", "true");
+    if (metadataOnly) params.append("metadata_only", "true");
+    if (sortByDate) params.append("sort_by_date", "true");
+
+    const url = "/api/deals?" + params.toString();
+
+    try {
+        const res = await fetch(url);
+        const data = await res.json();
+        renderDeals(data.deals);
+    } catch (error) {
+        console.error("Error fetching deals:", error);
+    }
+}
+
+function capitalizeFirstLetter(val) {
+    return String(val).charAt(0).toUpperCase() + String(val).slice(1);
+}
+
+function renderDeals(deals) {
+    const container = document.getElementById("dealsContainer");
+    container.innerHTML = "";
+
+    deals.forEach((deal) => {
+        const card = document.createElement("div");
+        card.classList.add("deal-card");
+
+        const header = document.createElement("div");
+        header.classList.add("deal-header");
+        header.innerText = capitalizeFirstLetter(deal.supermarket_name) || "Unbekannt";
+        card.appendChild(header);
+
+        const imgContainer = document.createElement("div");
+        imgContainer.classList.add("deal-image-container");
+        const img = document.createElement("img");
+        img.src = deal.img_name || "/static/img/placeholder.png";
+        imgContainer.appendChild(img);
+        card.appendChild(imgContainer);
+
+        const content = document.createElement("div");
+        content.classList.add("deal-content");
+
+        const titleEl = document.createElement("div");
+        titleEl.classList.add("deal-title");
+        titleEl.innerText = deal.clean_title || "Ohne Titel";
+        content.appendChild(titleEl);
+
+        const priceWrapper = document.createElement("div");
+        if (deal.price_old && deal.price_old > 0) {
[…]

### 2025-03-15 src/application/static/js/preview.js

@@ -1,0 +1,217 @@
+let pagesData = [];
+let currentPageIndex = 0;
+
+let pageImageEl;
+let canvasEl;
+let ctx;
+let highlightedPolygonIndex = -1;
+
+let modal;
+let modalTitle;
+let modalText;
+let closeModalBtn;
+
+document.addEventListener("DOMContentLoaded", async () => {
+    pageImageEl = document.getElementById("pageImage");
+    canvasEl = document.getElementById("overlayCanvas");
+    ctx = canvasEl.getContext("2d");
+
+    modal = document.getElementById("modal");
+    modalTitle = document.getElementById("modalTitle");
+    modalText = document.getElementById("modalText");
+    closeModalBtn = document.getElementById("closeModal");
+
+    document.getElementById("prevBtn").addEventListener("click", prevPage);
+    document.getElementById("nextBtn").addEventListener("click", nextPage);
+
+    closeModalBtn.onclick = () => { modal.style.display = "none"; };
+    window.onclick = (evt) => {
+        if (evt.target === modal) {
+            modal.style.display = "none";
+        }
+    };
+
+    await loadPreviewData();
+    renderPage();
+});
+
+async function loadPreviewData() {
+    const url = `/api/preview_data?session_id=${sessionId}`;
+    const res = await fetch(url);
+    if (!res.ok) {
+        alert("Fehler beim Laden der Preview-Daten.");
+        return;
+    }
+    const data = await res.json();
+    pagesData = data.pages || [];
+    if (pagesData.length === 0) {
+        alert("Keine Seiten enthalten.");
+    }
+    currentPageIndex = 0;
+}
+
+function renderPage() {
+    const pageData = pagesData[currentPageIndex];
+    const imgSrc = `/tmp/${pageData.page_image}`;
+    pageImageEl.src = imgSrc;
+
+    pageImageEl.onload = () => {
+        canvasEl.width = pageImageEl.width;
+        canvasEl.height = pageImageEl.height;
+
+        const origWidth = pageData.original_size[0];
+        const origHeight = pageData.original_size[1];
+
+        const dispWidth = pageImageEl.width;
+        const dispHeight = pageImageEl.height;
+
+        const ratioX = dispWidth / origWidth;
+        const ratioY = dispHeight / origHeight;
+
+        const scaledPolygons = pageData.polygons.map(det => {
+            const scaledPoly = det.polygon.map(([x, y]) => {
+                return [x * ratioX, y * ratioY];
[…]

### 2025-03-15 src/deal_detection/predict.py

@@ -1,0 +1,53 @@
+from ultralytics import YOLO
+import argparse
+import os
+
+cur_dir = os.path.dirname(os.path.realpath(__file__))
+
+
+def predict(model_path, input_path, output_path, imgsz, conf, iou):
+    """Run predictions on the input data."""
+    model = YOLO(model_path)
+
+    results = model.predict(
+        source=input_path,  # Path to input image or directory
+        imgsz=imgsz,  # Image size
+        conf=conf,  # Confidence threshold
+        iou=iou,  # IOU threshold
+        device="0",  # GPU device
+        save=True,  # Save output images
+        save_txt=True,  # Save predictions in text files
+        save_conf=True,  # Save confidences in text files
+        project=output_path,  # Directory to save results
+        name="predictions"  # Subdirectory name
+    )
+    return results
+
+
+def main():
+    """Main function to execute prediction pipeline."""
+    parser = argparse.ArgumentParser(description="YOLO Prediction Script")
+    parser.add_argument("--weights", "-w", type=str, required=True, help="Path to the trained YOLO model")
+    parser.add_argument("--input-path", "-i", type=str, required=True, help="Path to input images or directory")
+    parser.add_argument("--output-path", "-o", type=str, required=True, help="Directory to save prediction results")
+    parser.add_argument("--imgsz", type=int, default=640, help="Image size (default: 640)")
+    parser.add_argument("--conf", type=float, default=0.95, help="Confidence threshold (default: 0.25)")
+    parser.add_argument("--iou", type=float, default=0.6, help="IOU threshold (default: 0.45)")
+
+    args = parser.parse_args()
+
+    results = predict(
+        model_path=args.weights,
+        input_path=args.input_path,
+        output_path=args.output_path,
+        imgsz=args.imgsz,
+        conf=args.conf,
+        iou=args.iou
+    )
+
+    print("Prediction complete.")
+    print(f"Results saved to: {os.path.join(args.output_path, 'predictions')}")
+
+
+if __name__ == "__main__":
+    main()

### 2025-03-15 src/deal_detection/split_data.py

@@ -1,0 +1,63 @@
+import os
+import shutil
+import random
+from utils import get_labels_path
+
+def split_data():
+    src_dir = os.path.join(get_labels_path(), 'merged_data')
+    dest_train_dir = os.path.join(get_labels_path(), 'yolo_train_data')
+    dest_val_dir = os.path.join(get_labels_path(), 'yolo_val_data')
+
+    # Ensure destination directories exist
+    if not os.path.exists(dest_train_dir):
+        os.makedirs(dest_train_dir)
+    if not os.path.exists(dest_val_dir):
+        os.makedirs(dest_val_dir)
+
+    # List all subdirectories in src_dir
+    all_dirs = [d for d in os.listdir(src_dir)
+                if os.path.isdir(os.path.join(src_dir, d))]
+    # Create matching subdirectories in both train and val folders
+    for d in all_dirs:
+        os.makedirs(os.path.join(dest_train_dir, d), exist_ok=True)
+        os.makedirs(os.path.join(dest_val_dir, d), exist_ok=True)
+
+    # collect all names from for example image dir
+    all_files = []
+    for img in os.listdir(os.path.join(src_dir, 'images')):
+        if img.endswith('.jpg') or img.endswith('.jpeg') or img.endswith('.png'):
+            all_files.append(os.path.splitext(img)[0])
+
+    # Shuffle the list of all files
+    random.shuffle(all_files)
+
+    # Split the list of all files into train and val lists
+    split_ratio = 0.9
+    split_idx = int(len(all_files) * split_ratio)
+    train_files = all_files[:split_idx]
+    val_files = all_files[split_idx:]
+
+    # Copy files to train and val directories
+    for f in train_files:
+        for d in all_dirs:
+            if "label" in d:
+                shutil.copy(os.path.join(src_dir, d, f + '.txt'),
+                            os.path.join(dest_train_dir, d, f + '.txt'))
+            else:
+                shutil.copy(os.path.join(src_dir, d, f + '.jpg'),
+                            os.path.join(dest_train_dir, d, f + '.jpg'))
+    for f in val_files:
+        for d in all_dirs:
+            if "label" in d:
+                shutil.copy(os.path.join(src_dir, d, f + '.txt'),
+                            os.path.join(dest_val_dir, d, f + '.txt'))
+            else:
+                shutil.copy(os.path.join(src_dir, d, f + '.jpg'),
+                            os.path.join(dest_val_dir, d, f + '.jpg'))
+
[…]

### 2025-03-15 src/deal_detection/train.py

@@ -1,0 +1,60 @@
+from ultralytics import YOLO
+import yaml
+import os
+import argparse
+
+cur_dir = os.path.dirname(os.path.realpath(__file__))
+
+
+def load_config(config_path):
+    with open(config_path, "r") as f:
+        config = yaml.safe_load(f)
+    return config
+
+def parse_args():
+    parser = argparse.ArgumentParser(description="Train YOLO model")
+    parser.add_argument(
+        "--config", default=os.path.join(cur_dir, "train_configs.yaml"), type=str
+    )
+    args = parser.parse_args()
+    return args
+
+def train(cfg):
+    model = YOLO(cfg["model_path"], verbose=False)
+    results = model.train(
+        data=cfg["data_path"],
+        imgsz=cfg["imgsz"],
+        epochs=cfg["epochs"],
+        device="0",
+        cache=cfg["cache"],
+        batch=cfg["batch"],
+        hsv_h=cfg["hsv_h"],
+        hsv_s=cfg["hsv_s"],
+        hsv_v=cfg["hsv_v"],
+        degrees=cfg["degrees"],
+        translate=cfg["translate"],
+        scale=cfg["scale"],
+        shear=cfg["shear"],
+        fliplr=cfg["fliplr"],
+    )
+    return results
+
+
+def validate(cfg, best_model_path):
+    model = YOLO(best_model_path)
+    results = model.val(data=cfg["data_path"], imgsz=cfg["imgsz"], device="0")
+    return results
+
+
+def main(cfg):
+    results = train(cfg)
+    run_path = results.save_dir
+    print(f"Results saved to {run_path}")
+    # best_model_path = os.path.join(run_path, "weights", "best.pt")
+    # val_results = validate(cfg, best_model_path)
+
+
+if __name__ == "__main__":
+    args = parse_args()
+    cfg = load_config(args.config)
+    main(cfg)

### 2025-03-15 src/extraction/evaluation/evaluate_ocr-llm_donut_lvlm.py

@@ -1,580 +1,0 @@
-# General imports
-from collections import defaultdict
-import datetime
-import json
-import os
-import pickle
-import re
-import traceback
-import cv2
-import matplotlib.pyplot as plt
-import pandas as pd
-import numpy as np
-from pathlib import Path
-import seaborn as sns
-import pickle
-import jellyfish
-from dotenv import load_dotenv
-
-# --- OCR
-from paddleocr import PaddleOCR
-import pytesseract
-import easyocr
-from doctr.models import ocr_predictor
-
-
-# --- LLM
-from openai import OpenAI
-from ollama import chat
-
-# Torch / Huggingface
-import torch
-from transformers import DonutProcessor, VisionEncoderDecoderModel
-
-
-SYSTEM_TEMPLATE ="""
-                    **Context:**  
-                    You are an advanced language model specializing in structured data extraction from OCR text. Your task is to extract structured information from a supermarket deal OCR result.  
-                    **Important: Extract exactly one deal. Output a single JSON object with the required four fields.**  
-
-                    **Extraction Fields:**  
-                    - **Marke**: The brand name, if explicitly mentioned.  
-                    - **Produktname**: The product name.
-                    - **Original Preis**: The original price of the product.
-                    - **Reduzierter Preis**: The reduced price of the product.
-                    - **Gewicht**: The weight of the product, if available.
-
-                    **Guidelines:**  
-                    - **Return data strictly in JSON format as a single object.**  
-                    - **Ensure accuracy** by considering spatial context if available.  
-                    - **Use null values** for missing fields.  
-                    - **Filter out irrelevant numbers** (e.g., product weight should not be confused with price).  
-                    - **Fix OCR errors**:  
-                    1. **Price correction**: Identify and fix missing decimals (e.g., `"229"` → `"2.29"`).  
-                    2. **Contextual reasoning**: Infer correct prices using the euro symbol and typical pricing patterns.  
-                    3. **Ignore OCR noise**: Disregard unrelated text like `"Faarconn Galh"` or `"4B6e3Alus"`.  
-                    4. **Correct spelling mistakes**: Use the correct spelling for brands and products.
-
-                    **Output:**  
[…]

### 2025-03-15 src/extraction/evaluation/evaluate_ocr.py

@@ -1,394 +1,0 @@
-# General imports
-from collections import defaultdict
-import datetime
-import json
-import os
-import pickle
-import re
-import traceback
-import cv2
-import matplotlib.pyplot as plt
-import pandas as pd
-import numpy as np
-from pathlib import Path
-import seaborn as sns
-import pickle
-import jellyfish
-from dotenv import load_dotenv
-
-# --- OCR
-from paddleocr import PaddleOCR
-import pytesseract
-import easyocr
-from doctr.models import ocr_predictor
-
-
-
-
-
-
-DTYPES = {
-    "img_name": str,
-    "Marke": str,
-    "Produktname": str,
-    "Original Preis": str,
-    "Reduzierter Preis": str,
-    "Gewicht": str,
-    }
-
-ALIGNMENT_LABELS = {
-    "brand": ["marke", "brand", "hersteller", "manufacturer"],
-    "product_name": ["produktname", "productname", "name", "produkt", "product"],
-    "original_price": ["originalpreis", "preis", "original_price", "original preis", "original_preis"],
-    "deal_price": ["deal_price", "reduced_price", "reduzierter preis", "reduzierter_preis"],
-    "weight": ["gewicht", "weight"]
-}
-
-
-# Conduct OCR of different models
-MODELS = {
-    "ppocr_ocr": "PaddleOCR",
-    "easyocr_ocr": "EasyOCR",
-    "tesseract_ocr": "Tesseract",
-    "doctr_ocr": "DocTR",
-}
-
-LABELS = {
-    "brand": "Brand",
-    "product_name": "Product Name",
-    "original_price": "Original Price",
-    "deal_price": "Deal Price",
-    "weight": "Unit"
-
-
-}
-
-
-
-def df_label_alignment(df, alignment_labels=ALIGNMENT_LABELS):
-    """
-    Align the column names to match.
-    - The ALIGNMENT_LABELS dictionary contains the desired values as keys.
-    """
-    new_colnames = []
-    for col in df.columns:
-        for key, values in alignment_labels.items():
-            if col.lower() in values:
-                new_colnames.append(key)
-                break
-        else:
-            new_colnames.append(col)
-    df.columns = new_colnames
-    print(f"Datframe columns aligned to: {new_colnames}")
-    return df
-    
-
-
-# Preprocessing function
-def normalize_text(text, level=6):
-    if not text or pd.isnull(text) or text == "":
-        return ""
-    
-    # Level 1: Basic cleaning (handles empty values)
-    if level >= 1:
[…]

### 2025-03-15 src/extraction/evaluation/evaluate_ocr_llm.py

@@ -1,742 +1,0 @@
-# General imports
-from collections import defaultdict
-import datetime
-import json
-import os
-import pickle
-import re
-import traceback
-import cv2
-import matplotlib.pyplot as plt
-import pandas as pd
-import numpy as np
-from pathlib import Path
-import seaborn as sns
-import pickle
-import jellyfish
-from dotenv import load_dotenv
-
-# --- OCR
-from paddleocr import PaddleOCR
-import pytesseract
-import easyocr
-from doctr.models import ocr_predictor
-
-
-# --- LLM
-from openai import OpenAI
-from ollama import chat
-
-
-SYSTEM_TEMPLATE = """
-**Context:**  
-You are an advanced language model specializing in extracting structured information from OCR text. Your task is to extract one supermarket deal from the given OCR result.
-
-**Extraction Requirements:**  
-- **Fields:**  
-  - "Marke": Brand name (if explicitly mentioned)  
-  - "Produktname": Product name  
-  - "Original Preis": Original price  
-  - "Reduzierter Preis": Reduced price  
-  - "Gewicht": Weight (if available; otherwise, use null)
-
-- **Instructions:**  
-  - Return a single JSON object containing exactly one deal.
-  - Use JSON only—no additional text.
-  - If a field is missing, assign a null value.
-  - Correct OCR errors such as missing decimals (e.g., "229" → "2.29"), incorrect spellings, and OCR noise.
-  - Use contextual cues (e.g. euro symbols) to infer and correct pricing.
-
-**Example:**  
-OCR Input:                     
-Dallmayr Prodomo Kaffee gemahlen 500g 1kg=51.73 Dallmayr -24% prodomo 5 69 UVP7,49  
-
-JSON OUTPUT:
-{
-    "Marke": "Dallmayr",
-    "Produktname": "Prodomo Kaffee gemahlen",
-    "Original Preis": "UVP7,49",
-    "Reduzierter Preis": "3,99 €",
-    "Gewicht": null
-}
-
-IMPORTANT: Return the JSON object in the above format only once.
-"""
-
-
-DTYPES = {
-    "img_name": str,
-    "Marke": str,
-    "Produktname": str,
-    "Original Preis": str,
-    "Reduzierter Preis": str,
-    "Gewicht": str,
-    }
-
-ALIGNMENT_LABELS = {
-    "brand": ["marke", "brand", "hersteller", "manufacturer"],
-    "product_name": ["produktname", "productname", "name", "produkt", "product"],
[…]

### 2025-03-15 src/extraction/extract.py

@@ -1,175 +1,0 @@
-from collections import defaultdict
-import json
-import re
-import time
-import os
-import argparse
-import pickle
-
-import cv2
-from matplotlib import pyplot as plt
-import numpy as np
-from doctr.io import DocumentFile
-from doctr.models import ocr_predictor
-from openai import OpenAI
-
-import utils
-
-llm = OpenAI(base_url="http://127.0.0.1:1234/v1", api_key="lm-studio")
-LLM_MODEL = "qwen2.5-7b-instruct-1m@q8_0"
-
-SYSTEM_TEMPLATE = {
-            "role": "system",
-            "content": (
-                """
-                    **Context:**  
-                    You are an advanced language model specializing in structured data extraction from OCR text. Your task is to extract structured information from a supermarket deal OCR result.  
-                    **Important: Extract exactly one deal. Output a single JSON object with the required four fields.**  
-
-                    **Extraction Fields:**  
-                    - **Price**: The product price in euros (€), ensuring proper decimal placement.  
-                    - **Brand**: The brand name, if explicitly mentioned.  
-                    - **Product Description**: The product name, key details, packaging, size, or specifications.  
-                    - **Discount**: A number representing the percentage or absolute discount, if applicable.  
-
-                    **Guidelines:**  
-                    - **Return data strictly in JSON format as a single object.**  
-                    - **Ensure accuracy** by considering spatial context if available.  
-                    - **Use null values** for missing fields.  
-                    - **Filter out irrelevant numbers** (e.g., product weight should not be confused with price).  
-                    - **Fix OCR errors**:  
-                    1. **Price correction**: Identify and fix missing decimals (e.g., `"229"` → `"2.29"`).  
-                    2. **Contextual reasoning**: Infer correct prices using the euro symbol and typical pricing patterns.  
-                    3. **Ignore OCR noise**: Disregard unrelated text like `"Faarconn Galh"` or `"4B6e3Alus"`.  
-
-                    **Output:**  
-                    - **Return JSON only, containing exactly one deal.**  
-                    - **Ensure all prices are in euros (€) only.**  
[…]

### 2025-03-15 src/extraction/utils/data.py

@@ -1,66 +1,0 @@
-import os
-import cv2
-import matplotlib.pyplot as plt
-import numpy as np
-
-def read_polygons(p):
-    """
-    Reads polygons in YOLO format and displays the annotated image.
-
-    Args:
-        lbl (str): PATH to the label file.
-        
-    """
-
-    polygons = []
-    with open(p, 'r', encoding='utf-8') as file:
-        for line in file:
-            parts = line.strip().split()
-            class_id = int(parts[0]) 
-            coords = list(map(float, parts[1:]))
-            
-            # Try to unnormalize the coordinates
-            image = None
-            for ext in [".jpg", ".jpeg", ".png"]:
-                imgp = p.replace('labels', 'images').replace('.txt', ext)
-                if os.path.exists(imgp):
-                    image = cv2.cvtColor(cv2.imread(imgp), cv2.COLOR_BGR2RGB)
-                    break
-            
-            if image is not None:
-                polygon = np.array(coords).reshape(-1, 2) * [image.shape[1], image.shape[0]]
-            else:
-                polygon = np.array(coords).reshape(-1, 2)
-                print(f"WARNING: Image not found for label \n{p}\n Using normalized coordinates.")
-
-            polygons.append((class_id, polygon))
-
-    return polygons
-
-
-def extract_polygons(image, polygons):
-    """
-    Extracts and crops regions defined by polygons from an image.
-
-    Args:
-        image (numpy.ndarray): The source image.
-        polygons (list): A list of tuples, where each tuple contains a class ID and a polygon 
-                         (as a numpy array of normalized coordinates).
-
-    Returns:
-        list: A list of cropped images containing the extracted polygons.
-    """
-    results = []
-    for class_id, polygon in polygons:
-        points = polygon.astype(int)
-
-        mask = np.zeros(image.shape[:2], dtype=np.uint8)
-        cv2.fillPoly(mask, [points], color=255)
-        extracted = cv2.bitwise_and(image, image, mask=mask)
-
-        x, y, w, h = cv2.boundingRect(points)
-
-        cropped = extracted[y:y+h, x:x+w]
-        results.append(cropped)
-
-    return results

### 2025-03-15 src/information_extraction/evaluation/evaluate_ocr-llm_donut_lvlm.py

@@ -1,0 +1,580 @@
+# General imports
+from collections import defaultdict
+import datetime
+import json
+import os
+import pickle
+import re
+import traceback
+import cv2
+import matplotlib.pyplot as plt
+import pandas as pd
+import numpy as np
+from pathlib import Path
+import seaborn as sns
+import pickle
+import jellyfish
+from dotenv import load_dotenv
+
+# --- OCR
+from paddleocr import PaddleOCR
+import pytesseract
+import easyocr
+from doctr.models import ocr_predictor
+
+
+# --- LLM
+from openai import OpenAI
+from ollama import chat
+
+# Torch / Huggingface
+import torch
+from transformers import DonutProcessor, VisionEncoderDecoderModel
+
+
+SYSTEM_TEMPLATE ="""
+                    **Context:**  
+                    You are an advanced language model specializing in structured data extraction from OCR text. Your task is to extract structured information from a supermarket deal OCR result.  
+                    **Important: Extract exactly one deal. Output a single JSON object with the required four fields.**  
+
+                    **Extraction Fields:**  
+                    - **Marke**: The brand name, if explicitly mentioned.  
+                    - **Produktname**: The product name.
+                    - **Original Preis**: The original price of the product.
+                    - **Reduzierter Preis**: The reduced price of the product.
+                    - **Gewicht**: The weight of the product, if available.
+
+                    **Guidelines:**  
+                    - **Return data strictly in JSON format as a single object.**  
+                    - **Ensure accuracy** by considering spatial context if available.  
+                    - **Use null values** for missing fields.  
+                    - **Filter out irrelevant numbers** (e.g., product weight should not be confused with price).  
+                    - **Fix OCR errors**:  
+                    1. **Price correction**: Identify and fix missing decimals (e.g., `"229"` → `"2.29"`).  
+                    2. **Contextual reasoning**: Infer correct prices using the euro symbol and typical pricing patterns.  
+                    3. **Ignore OCR noise**: Disregard unrelated text like `"Faarconn Galh"` or `"4B6e3Alus"`.  
+                    4. **Correct spelling mistakes**: Use the correct spelling for brands and products.
+
+                    **Output:**  
[…]

### 2025-03-15 src/information_extraction/evaluation/evaluate_ocr.py

@@ -1,0 +1,394 @@
+# General imports
+from collections import defaultdict
+import datetime
+import json
+import os
+import pickle
+import re
+import traceback
+import cv2
+import matplotlib.pyplot as plt
+import pandas as pd
+import numpy as np
+from pathlib import Path
+import seaborn as sns
+import pickle
+import jellyfish
+from dotenv import load_dotenv
+
+# --- OCR
+from paddleocr import PaddleOCR
+import pytesseract
+import easyocr
+from doctr.models import ocr_predictor
+
+
+
+
+
+
+DTYPES = {
+    "img_name": str,
+    "Marke": str,
+    "Produktname": str,
+    "Original Preis": str,
+    "Reduzierter Preis": str,
+    "Gewicht": str,
+    }
+
+ALIGNMENT_LABELS = {
+    "brand": ["marke", "brand", "hersteller", "manufacturer"],
+    "product_name": ["produktname", "productname", "name", "produkt", "product"],
+    "original_price": ["originalpreis", "preis", "original_price", "original preis", "original_preis"],
+    "deal_price": ["deal_price", "reduced_price", "reduzierter preis", "reduzierter_preis"],
+    "weight": ["gewicht", "weight"]
+}
+
+
+# Conduct OCR of different models
+MODELS = {
+    "ppocr_ocr": "PaddleOCR",
+    "easyocr_ocr": "EasyOCR",
+    "tesseract_ocr": "Tesseract",
+    "doctr_ocr": "DocTR",
+}
+
+LABELS = {
+    "brand": "Brand",
+    "product_name": "Product Name",
+    "original_price": "Original Price",
+    "deal_price": "Deal Price",
+    "weight": "Unit"
+
+
+}
+
+
+
+def df_label_alignment(df, alignment_labels=ALIGNMENT_LABELS):
+    """
+    Align the column names to match.
+    - The ALIGNMENT_LABELS dictionary contains the desired values as keys.
+    """
+    new_colnames = []
+    for col in df.columns:
+        for key, values in alignment_labels.items():
+            if col.lower() in values:
+                new_colnames.append(key)
+                break
+        else:
+            new_colnames.append(col)
+    df.columns = new_colnames
+    print(f"Datframe columns aligned to: {new_colnames}")
+    return df
+    
+
+
+# Preprocessing function
+def normalize_text(text, level=6):
+    if not text or pd.isnull(text) or text == "":
+        return ""
+    
+    # Level 1: Basic cleaning (handles empty values)
+    if level >= 1:
[…]

### 2025-03-15 src/information_extraction/evaluation/evaluate_ocr_llm.py

@@ -1,0 +1,742 @@
+# General imports
+from collections import defaultdict
+import datetime
+import json
+import os
+import pickle
+import re
+import traceback
+import cv2
+import matplotlib.pyplot as plt
+import pandas as pd
+import numpy as np
+from pathlib import Path
+import seaborn as sns
+import pickle
+import jellyfish
+from dotenv import load_dotenv
+
+# --- OCR
+from paddleocr import PaddleOCR
+import pytesseract
+import easyocr
+from doctr.models import ocr_predictor
+
+
+# --- LLM
+from openai import OpenAI
+from ollama import chat
+
+
+SYSTEM_TEMPLATE = """
+**Context:**  
+You are an advanced language model specializing in extracting structured information from OCR text. Your task is to extract one supermarket deal from the given OCR result.
+
+**Extraction Requirements:**  
+- **Fields:**  
+  - "Marke": Brand name (if explicitly mentioned)  
+  - "Produktname": Product name  
+  - "Original Preis": Original price  
+  - "Reduzierter Preis": Reduced price  
+  - "Gewicht": Weight (if available; otherwise, use null)
+
+- **Instructions:**  
+  - Return a single JSON object containing exactly one deal.
+  - Use JSON only—no additional text.
+  - If a field is missing, assign a null value.
+  - Correct OCR errors such as missing decimals (e.g., "229" → "2.29"), incorrect spellings, and OCR noise.
+  - Use contextual cues (e.g. euro symbols) to infer and correct pricing.
+
+**Example:**  
+OCR Input:                     
+Dallmayr Prodomo Kaffee gemahlen 500g 1kg=51.73 Dallmayr -24% prodomo 5 69 UVP7,49  
+
+JSON OUTPUT:
+{
+    "Marke": "Dallmayr",
+    "Produktname": "Prodomo Kaffee gemahlen",
+    "Original Preis": "UVP7,49",
+    "Reduzierter Preis": "3,99 €",
+    "Gewicht": null
+}
+
+IMPORTANT: Return the JSON object in the above format only once.
+"""
+
+
+DTYPES = {
+    "img_name": str,
+    "Marke": str,
+    "Produktname": str,
+    "Original Preis": str,
+    "Reduzierter Preis": str,
+    "Gewicht": str,
+    }
+
+ALIGNMENT_LABELS = {
+    "brand": ["marke", "brand", "hersteller", "manufacturer"],
+    "product_name": ["produktname", "productname", "name", "produkt", "product"],
[…]

### 2025-03-15 src/information_extraction/extract.py

@@ -1,0 +1,175 @@
+from collections import defaultdict
+import json
+import re
+import time
+import os
+import argparse
+import pickle
+
+import cv2
+from matplotlib import pyplot as plt
+import numpy as np
+from doctr.io import DocumentFile
+from doctr.models import ocr_predictor
+from openai import OpenAI
+
+import utils
+
+llm = OpenAI(base_url="http://127.0.0.1:1234/v1", api_key="lm-studio")
+LLM_MODEL = "qwen2.5-7b-instruct-1m@q8_0"
+
+SYSTEM_TEMPLATE = {
+            "role": "system",
+            "content": (
+                """
+                    **Context:**  
+                    You are an advanced language model specializing in structured data extraction from OCR text. Your task is to extract structured information from a supermarket deal OCR result.  
+                    **Important: Extract exactly one deal. Output a single JSON object with the required four fields.**  
+
+                    **Extraction Fields:**  
+                    - **Price**: The product price in euros (€), ensuring proper decimal placement.  
+                    - **Brand**: The brand name, if explicitly mentioned.  
+                    - **Product Description**: The product name, key details, packaging, size, or specifications.  
+                    - **Discount**: A number representing the percentage or absolute discount, if applicable.  
+
+                    **Guidelines:**  
+                    - **Return data strictly in JSON format as a single object.**  
+                    - **Ensure accuracy** by considering spatial context if available.  
+                    - **Use null values** for missing fields.  
+                    - **Filter out irrelevant numbers** (e.g., product weight should not be confused with price).  
+                    - **Fix OCR errors**:  
+                    1. **Price correction**: Identify and fix missing decimals (e.g., `"229"` → `"2.29"`).  
+                    2. **Contextual reasoning**: Infer correct prices using the euro symbol and typical pricing patterns.  
+                    3. **Ignore OCR noise**: Disregard unrelated text like `"Faarconn Galh"` or `"4B6e3Alus"`.  
+
+                    **Output:**  
+                    - **Return JSON only, containing exactly one deal.**  
+                    - **Ensure all prices are in euros (€) only.**  
[…]

### 2025-03-15 src/information_extraction/utils/data.py

@@ -1,0 +1,66 @@
+import os
+import cv2
+import matplotlib.pyplot as plt
+import numpy as np
+
+def read_polygons(p):
+    """
+    Reads polygons in YOLO format and displays the annotated image.
+
+    Args:
+        lbl (str): PATH to the label file.
+        
+    """
+
+    polygons = []
+    with open(p, 'r', encoding='utf-8') as file:
+        for line in file:
+            parts = line.strip().split()
+            class_id = int(parts[0]) 
+            coords = list(map(float, parts[1:]))
+            
+            # Try to unnormalize the coordinates
+            image = None
+            for ext in [".jpg", ".jpeg", ".png"]:
+                imgp = p.replace('labels', 'images').replace('.txt', ext)
+                if os.path.exists(imgp):
+                    image = cv2.cvtColor(cv2.imread(imgp), cv2.COLOR_BGR2RGB)
+                    break
+            
+            if image is not None:
+                polygon = np.array(coords).reshape(-1, 2) * [image.shape[1], image.shape[0]]
+            else:
+                polygon = np.array(coords).reshape(-1, 2)
+                print(f"WARNING: Image not found for label \n{p}\n Using normalized coordinates.")
+
+            polygons.append((class_id, polygon))
+
+    return polygons
+
+
+def extract_polygons(image, polygons):
+    """
+    Extracts and crops regions defined by polygons from an image.
+
+    Args:
+        image (numpy.ndarray): The source image.
+        polygons (list): A list of tuples, where each tuple contains a class ID and a polygon 
+                         (as a numpy array of normalized coordinates).
+
+    Returns:
+        list: A list of cropped images containing the extracted polygons.
+    """
+    results = []
+    for class_id, polygon in polygons:
+        points = polygon.astype(int)
+
+        mask = np.zeros(image.shape[:2], dtype=np.uint8)
+        cv2.fillPoly(mask, [points], color=255)
+        extracted = cv2.bitwise_and(image, image, mask=mask)
+
+        x, y, w, h = cv2.boundingRect(points)
+
+        cropped = extracted[y:y+h, x:x+w]
+        results.append(cropped)
+
+    return results

### 2025-03-15 src/information_extraction/utils/find_dates.py

@@ -1,0 +1,65 @@
+
+from collections import defaultdict
+import copy
+import os
+import re
+from PIL import Image
+from paddleocr import PaddleOCR, draw_ocr
+from tqdm import tqdm
+
+# ------------- VARIABLES ------------- #
+ROOT_DIR = r"C:\Users\ihett\OneDrive\Gabrilyi\leaflet_project\crawled_leaflets" # It will recursively search for all images.
+PATTERN = r'\b(0[1-9]|[12][0-9]|3[01])\.(0[1-9]|1[0-2])\b'
+EXTENDED_PATTERN = r'\b(?:gültig\s+ab|ab|gültig\s+von|von)\s+(?:Mo|Di|Mi|Do|Fr|Sa|So|Montag|Dienstag|Mittwoch|Donnerstag|Freitag|Samstag|Sonntag)?\.?\s*\d{1,2}\.\d{2}(?:\s*(?:-|bis)\s*\d{1,2}\.\d{2})?\b'
+OUTPUT_DIR = "."
+
+
+def get_image_folders_list():
+    r = []
+    for root, dirs, files in os.walk(ROOT_DIR):
+        for dir in dirs:            
+            if all([file.endswith(('.jpg', '.jpeg', '.png')) for file in os.listdir(os.path.join(root, dir))]):
+                r.append(os.path.join(root, dir))
+    return r
+
+
+def write_dict(d):
+    with open(os.path.join(OUTPUT_DIR, "dates.txt"), "w+") as f:
+        for key, val in d.items():
+            f.write(f"{key}: {val}\n")
+
+
+if __name__ == "__main__":
+    res_dict = defaultdict(str)
+    ocr = PaddleOCR(use_angle_cls=True, lang='german') 
+    folders = get_image_folders_list()
+    pbar = tqdm(folders, total=len(folders), unit="folder")
+    try:
+        for folder in pbar:
+            pbar.set_description(f"Processing {folder}")
+
+            scheme = "_".join(folder.lower().split(os.sep)[-2:])  
+            images = [os.path.join(folder, file) for file in os.listdir(folder)]
+            dates = []
+            for img in images:
+                result = ocr.ocr(img, cls=True)
+                for idx, res in enumerate(result):
+                    boxes = [line[0] for line in res]
+                    txts = [line[1][0] for line in res]
+                    scores = [line[1][1] for line in res]
+                    for txt in txts:
+                        if re.search(EXTENDED_PATTERN, txt):
[…]

### 2025-03-15 src/webapp/deal_processing.py

@@ -1,62 +1,0 @@
-from pydantic import BaseModel
-from typing import Optional, List
-from collections import defaultdict
-import os
-import pandas as pd
-from tqdm import tqdm
-import json
-from ollama import chat
-
-class DealDescription(BaseModel):
-    brand: Optional[str] = None
-    productname: Optional[str] = None
-    unbinding_price_recommendation: Optional[float] = None
-    deal_price: float = None
-    weight: Optional[str] = None
-
-def process_image(img_path: str, model: str) -> dict:
-    """
-    Processes a single deal image given by its file path using the vision-language model.
-    Returns a dictionary with the extracted structured information.
-    """
-    response = chat(
-        model=model,
-        format=DealDescription.model_json_schema(),
-        messages=[{
-            "role": "user",
-            "content": (
-                """
-                You are an advanced vision language model specializing in structured data extraction from an image of a deal. Your task is to extract structured information from a supermarket deal.
-
-                Extraction Fields:
-                    - brand: The brand name, if available (e.g. "Coca Cola", "Milka", "Nestle", "Müller", "Iglo").
-                    - productname: The name of the product without mentioning the brand and description.
-                    - unbinding_price_recommendation: The price of the product without discount, if given (e.g. 2.99, 3.50, 1.99).
-                    - deal_price: The price of the product on sale (e.g. 1.99, 2.50, 0.99). Never negative.
-                    - weight: The amount of the product, if given (e.g. 500g, 1kg, 1 piece).
-                """
-            ),
-            "images": [img_path],
-        }],
-        options={"temperature": 0}
-    )
-
-    try:
-        image_description = DealDescription.model_validate_json(response.message.content)
-    except Exception as e:
-        image_description = DealDescription(
-            brand="unknown",
-            productname="unknown",
-            unbinding_price_recommendation=None,
-            deal_price=0.0,
-            weight="unknown"
-        )
-
-    return {
-        "img_name": os.path.basename(img_path),
-        "brand": image_description.brand,
-        "productname": image_description.productname,
-        "original_price": image_description.unbinding_price_recommendation,
-        "deal_price": image_description.deal_price,
-        "weight": image_description.weight
-    }

### 2025-03-15 src/webapp/main.py

@@ -1,342 +1,0 @@
-from fastapi import FastAPI, Request, File, UploadFile, Form
-from fastapi.responses import HTMLResponse, JSONResponse
-from fastapi.staticfiles import StaticFiles
-from fastapi.templating import Jinja2Templates
-
-import sqlite3
-import os
-from dotenv import load_dotenv
-from typing import Optional
-from datetime import datetime
-import uuid
-from tqdm import tqdm
-
-from ultralytics import YOLO
-# from pdf2image import convert_from_path
-import fitz
-
-from PIL import Image, ImageDraw  # Ensure ImageDraw is imported
-from deal_processing import process_image  # import process_image from deal_processing.py
-
-SEGMENTATION_CACHE = {}
-
-load_dotenv(override=True)
-
-PROJECT_DIR = os.getenv("PROJECT_DIR", ".")
-DB_PATH = os.path.join(PROJECT_DIR, "crawled_leaflets", "supermarket_leaflets.db")
-MODELS_DIR = os.path.join(PROJECT_DIR, "models")
-DEALS_DIR = os.path.join(PROJECT_DIR, "deals")
-
-app = FastAPI()
-
-app.mount("/static", StaticFiles(directory="static"), name="static")
-app.mount(
-    "/onedrive-images",
-    StaticFiles(directory=DEALS_DIR),
-    name="onedrive-images"
-)
-YOLOV11_PATH = os.path.join(MODELS_DIR, "model.pt")
-model = YOLO(YOLOV11_PATH, verbose=False)
-
-all_images = {}
-
-for root, dirs, files in tqdm(os.walk(DEALS_DIR), desc="Loading image paths"):
-    for file in files:
-        if file.endswith(".png") and "annotated" not in file:
-            all_images[file] = f"/onedrive-images{root.replace(DEALS_DIR, '')}/{file}"
-
-templates = Jinja2Templates(directory="templates")
-
-def get_db_connection():
-    conn = sqlite3.connect(DB_PATH)
-    conn.row_factory = sqlite3.Row
-    return conn
-
-@app.get("/", response_class=HTMLResponse)
-async def read_root(request: Request):
-    # return a list of all supermarket names to filter by
-    conn = get_db_connection()
-    cursor = conn.cursor()
-    cursor.execute("SELECT name FROM supermarket")
-    supermarkets = cursor.fetchall()
-    conn.close()
-    return templates.TemplateResponse("index.html", {
-        "request": request,
[…]

### 2025-03-15 src/webapp/static/js/app.js

@@ -1,154 +1,0 @@
-let currentPage = 1;
-
-async function fetchDeals(page = 1) {
-    currentPage = page;
-
-    const search = document.getElementById("searchInput").value.trim();
-    const metadataOnly = document.getElementById("metadataOnly").checked;
-    const supermarket = document.getElementById("supermarketSelect").value;
-    const validOnly = document.getElementById("validOnly").checked;
-    const sortByDate = document.getElementById("sortByDate").checked;
-
-    const params = new URLSearchParams();
-    params.append("page", page);
-    if (search) params.append("search", search);
-    if (supermarket) params.append("supermarket", supermarket);
-    if (validOnly) params.append("valid_only", "true");
-    if (metadataOnly) params.append("metadata_only", "true");
-    if (sortByDate) params.append("sort_by_date", "true");
-
-    const url = "/api/deals?" + params.toString();
-
-    try {
-        const res = await fetch(url);
-        const data = await res.json();
-        renderDeals(data.deals);
-    } catch (error) {
-        console.error("Error fetching deals:", error);
-    }
-}
-
-function capitalizeFirstLetter(val) {
-    return String(val).charAt(0).toUpperCase() + String(val).slice(1);
-}
-
-function renderDeals(deals) {
-    const container = document.getElementById("dealsContainer");
-    container.innerHTML = "";
-
-    deals.forEach((deal) => {
-        const card = document.createElement("div");
-        card.classList.add("deal-card");
-
-        const header = document.createElement("div");
-        header.classList.add("deal-header");
-        header.innerText = capitalizeFirstLetter(deal.supermarket_name) || "Unbekannt";
-        card.appendChild(header);
-
-        const imgContainer = document.createElement("div");
-        imgContainer.classList.add("deal-image-container");
-        const img = document.createElement("img");
-        img.src = deal.img_name || "/static/img/placeholder.png";
-        imgContainer.appendChild(img);
-        card.appendChild(imgContainer);
-
-        const content = document.createElement("div");
-        content.classList.add("deal-content");
-
-        const titleEl = document.createElement("div");
-        titleEl.classList.add("deal-title");
-        titleEl.innerText = deal.clean_title || "Ohne Titel";
-        content.appendChild(titleEl);
-
-        const priceWrapper = document.createElement("div");
-        if (deal.price_old && deal.price_old > 0) {
[…]

### 2025-03-15 src/webapp/static/js/preview.js

@@ -1,217 +1,0 @@
-let pagesData = [];
-let currentPageIndex = 0;
-
-let pageImageEl;
-let canvasEl;
-let ctx;
-let highlightedPolygonIndex = -1;
-
-let modal;
-let modalTitle;
-let modalText;
-let closeModalBtn;
-
-document.addEventListener("DOMContentLoaded", async () => {
-    pageImageEl = document.getElementById("pageImage");
-    canvasEl = document.getElementById("overlayCanvas");
-    ctx = canvasEl.getContext("2d");
-
-    modal = document.getElementById("modal");
-    modalTitle = document.getElementById("modalTitle");
-    modalText = document.getElementById("modalText");
-    closeModalBtn = document.getElementById("closeModal");
-
-    document.getElementById("prevBtn").addEventListener("click", prevPage);
-    document.getElementById("nextBtn").addEventListener("click", nextPage);
-
-    closeModalBtn.onclick = () => { modal.style.display = "none"; };
-    window.onclick = (evt) => {
-        if (evt.target === modal) {
-            modal.style.display = "none";
-        }
-    };
-
-    await loadPreviewData();
-    renderPage();
-});
-
-async function loadPreviewData() {
-    const url = `/api/preview_data?session_id=${sessionId}`;
-    const res = await fetch(url);
-    if (!res.ok) {
-        alert("Fehler beim Laden der Preview-Daten.");
-        return;
-    }
-    const data = await res.json();
-    pagesData = data.pages || [];
-    if (pagesData.length === 0) {
-        alert("Keine Seiten enthalten.");
-    }
-    currentPageIndex = 0;
-}
-
-function renderPage() {
-    const pageData = pagesData[currentPageIndex];
-    const imgSrc = `/tmp/${pageData.page_image}`;
-    pageImageEl.src = imgSrc;
-
-    pageImageEl.onload = () => {
-        canvasEl.width = pageImageEl.width;
-        canvasEl.height = pageImageEl.height;
-
-        const origWidth = pageData.original_size[0];
-        const origHeight = pageData.original_size[1];
-
-        const dispWidth = pageImageEl.width;
-        const dispHeight = pageImageEl.height;
-
-        const ratioX = dispWidth / origWidth;
-        const ratioY = dispHeight / origHeight;
-
-        const scaledPolygons = pageData.polygons.map(det => {
-            const scaledPoly = det.polygon.map(([x, y]) => {
-                return [x * ratioX, y * ratioY];
[…]

### 2025-03-15 src/yolo/create_bbox_labels.py

@@ -1,190 +1,0 @@
-import os
-import shutil
-from utils import get_labels_path
-import cv2
-import numpy as np
-from PIL import Image
-from PIL import ImageDraw
-from PIL import ImageFont
-from tqdm import tqdm
-
-def create_bbox_labels():
-    src_dir = os.path.join(get_labels_path(), 'merged_data', 'old_labels')
-    target_dir = os.path.join(get_labels_path(), 'merged_data', 'bbox_labels')
-    bbox_imgs = os.path.join(get_labels_path(), 'merged_data', 'bbox_drawn_images')
-
-    if not os.path.exists(target_dir):
-        os.makedirs(target_dir)
-
-    if not os.path.exists(bbox_imgs):
-        os.makedirs(bbox_imgs)
-
-    for old_label in tqdm(os.listdir(src_dir)):
-        label_filepath = os.path.join(src_dir, old_label)
-        with open(label_filepath, 'r') as f:
-            lines = f.readlines()
-
-        new_lines = []
-        for line in lines:
-            parts = line.strip().split()
-            # If already a bbox label (class + 4 numbers), keep it as-is.
-            if len(parts) == 5:
-                new_lines.append(line.strip())
-            else:
-                # Assume polygon label: class followed by an even number of coordinates.
-                class_id = parts[0]
-                try:
-                    coords = [float(x) for x in parts[1:]]
-                except ValueError:
-                    # Skip this line if conversion fails
-                    continue
-                if len(coords) % 2 != 0 or len(coords) < 4:
-                    # Invalid polygon data
-                    continue
-
-                xs = coords[0::2]
-                ys = coords[1::2]
-                min_x = min(xs)
-                max_x = max(xs)
-                min_y = min(ys)
-                max_y = max(ys)
-                center_x = (min_x + max_x) / 2
-                center_y = (min_y + max_y) / 2
-                box_width = max_x - min_x
-                box_height = max_y - min_y
-                new_line = f"{class_id} {center_x:.6f} {center_y:.6f} {box_width:.6f} {box_height:.6f}"
-                new_lines.append(new_line)
-
-        # Write the new bbox labels to the target directory (preserving the filename)
-        target_filepath = os.path.join(target_dir, old_label)
-        with open(target_filepath, 'w') as f:
-            f.write("\n".join(new_lines))
-
-        # Optionally, draw the bounding boxes on the corresponding image.
[…]

### 2025-03-15 src/yolo/merge_labeled_data.py

@@ -1,42 +1,0 @@
-from utils import get_labels_path
-import os
-import shutil
-
-def merge_labeled_data():
-    # to store paths
-    all_images = []
-    all_labels = []
-    old_labels = []
-
-    # walk through all the directories and get all the images and labels paths
-    for root, dirs, files in os.walk(get_labels_path()):
-        for file in files:
-            if "old_labels" in root and file.endswith(".txt"):
-                old_labels.append(os.path.join(root, file))
-            elif file.endswith(".jpg"):
-                all_images.append(os.path.join(root, file))
-            elif file.endswith(".txt"):
-                all_labels.append(os.path.join(root, file))
-
-    # cp all the images and labels to a new directory
-    target_dir = os.path.join(get_labels_path(), 'merged_data')
-    if not os.path.exists(target_dir):
-        os.makedirs(target_dir)
-        os.makedirs(os.path.join(target_dir, 'images'))
-        os.makedirs(os.path.join(target_dir, 'labels'))
-        os.makedirs(os.path.join(target_dir, 'old_labels'))
-
-    for image in all_images:
-        shutil.copy(image, os.path.join(target_dir, 'images'))
-    for label in all_labels:
-        shutil.copy(label, os.path.join(target_dir, 'labels'))
-    for old_label in old_labels:
-        shutil.copy(old_label, os.path.join(target_dir, 'old_labels'))
-    print(f"Total images: {len(all_images)}")
-    print(f"Total labels: {len(all_labels)}")
-    print(f"Total old labels: {len(old_labels)}")
-
-    print("Data merged successfully")
-
-if __name__ == "__main__":
-    merge_labeled_data()

### 2025-03-15 src/yolo/predict.py

@@ -1,53 +1,0 @@
-from ultralytics import YOLO
-import argparse
-import os
-
-cur_dir = os.path.dirname(os.path.realpath(__file__))
-
-
-def predict(model_path, input_path, output_path, imgsz, conf, iou):
-    """Run predictions on the input data."""
-    model = YOLO(model_path)
-
-    results = model.predict(
-        source=input_path,  # Path to input image or directory
-        imgsz=imgsz,  # Image size
-        conf=conf,  # Confidence threshold
-        iou=iou,  # IOU threshold
-        device="0",  # GPU device
-        save=True,  # Save output images
-        save_txt=True,  # Save predictions in text files
-        save_conf=True,  # Save confidences in text files
-        project=output_path,  # Directory to save results
-        name="predictions"  # Subdirectory name
-    )
-    return results
-
-
-def main():
-    """Main function to execute prediction pipeline."""
-    parser = argparse.ArgumentParser(description="YOLO Prediction Script")
-    parser.add_argument("--weights", "-w", type=str, required=True, help="Path to the trained YOLO model")
-    parser.add_argument("--input-path", "-i", type=str, required=True, help="Path to input images or directory")
-    parser.add_argument("--output-path", "-o", type=str, required=True, help="Directory to save prediction results")
-    parser.add_argument("--imgsz", type=int, default=640, help="Image size (default: 640)")
-    parser.add_argument("--conf", type=float, default=0.95, help="Confidence threshold (default: 0.25)")
-    parser.add_argument("--iou", type=float, default=0.6, help="IOU threshold (default: 0.45)")
-
-    args = parser.parse_args()
-
-    results = predict(
-        model_path=args.weights,
-        input_path=args.input_path,
-        output_path=args.output_path,
-        imgsz=args.imgsz,
-        conf=args.conf,
-        iou=args.iou
-    )
-
-    print("Prediction complete.")
-    print(f"Results saved to: {os.path.join(args.output_path, 'predictions')}")
-
-
-if __name__ == "__main__":
-    main()

### 2025-03-15 src/yolo/split_data.py

@@ -1,63 +1,0 @@
-import os
-import shutil
-import random
-from utils import get_labels_path
-
-def split_data():
-    src_dir = os.path.join(get_labels_path(), 'merged_data')
-    dest_train_dir = os.path.join(get_labels_path(), 'yolo_train_data')
-    dest_val_dir = os.path.join(get_labels_path(), 'yolo_val_data')
-
-    # Ensure destination directories exist
-    if not os.path.exists(dest_train_dir):
-        os.makedirs(dest_train_dir)
-    if not os.path.exists(dest_val_dir):
-        os.makedirs(dest_val_dir)
-
-    # List all subdirectories in src_dir
-    all_dirs = [d for d in os.listdir(src_dir)
-                if os.path.isdir(os.path.join(src_dir, d))]
-    # Create matching subdirectories in both train and val folders
-    for d in all_dirs:
-        os.makedirs(os.path.join(dest_train_dir, d), exist_ok=True)
-        os.makedirs(os.path.join(dest_val_dir, d), exist_ok=True)
-
-    # collect all names from for example image dir
-    all_files = []
-    for img in os.listdir(os.path.join(src_dir, 'images')):
-        if img.endswith('.jpg') or img.endswith('.jpeg') or img.endswith('.png'):
-            all_files.append(os.path.splitext(img)[0])
-
-    # Shuffle the list of all files
-    random.shuffle(all_files)
-
-    # Split the list of all files into train and val lists
-    split_ratio = 0.9
-    split_idx = int(len(all_files) * split_ratio)
-    train_files = all_files[:split_idx]
-    val_files = all_files[split_idx:]
-
-    # Copy files to train and val directories
-    for f in train_files:
-        for d in all_dirs:
-            if "label" in d:
-                shutil.copy(os.path.join(src_dir, d, f + '.txt'),
-                            os.path.join(dest_train_dir, d, f + '.txt'))
-            else:
-                shutil.copy(os.path.join(src_dir, d, f + '.jpg'),
-                            os.path.join(dest_train_dir, d, f + '.jpg'))
-    for f in val_files:
-        for d in all_dirs:
-            if "label" in d:
-                shutil.copy(os.path.join(src_dir, d, f + '.txt'),
-                            os.path.join(dest_val_dir, d, f + '.txt'))
-            else:
-                shutil.copy(os.path.join(src_dir, d, f + '.jpg'),
-                            os.path.join(dest_val_dir, d, f + '.jpg'))
-
[…]

### 2025-03-15 src/yolo/train.py

@@ -1,60 +1,0 @@
-from ultralytics import YOLO
-import yaml
-import os
-import argparse
-
-cur_dir = os.path.dirname(os.path.realpath(__file__))
-
-
-def load_config(config_path):
-    with open(config_path, "r") as f:
-        config = yaml.safe_load(f)
-    return config
-
-def parse_args():
-    parser = argparse.ArgumentParser(description="Train YOLO model")
-    parser.add_argument(
-        "--config", default=os.path.join(cur_dir, "train_configs.yaml"), type=str
-    )
-    args = parser.parse_args()
-    return args
-
-def train(cfg):
-    model = YOLO(cfg["model_path"], verbose=False)
-    results = model.train(
-        data=cfg["data_path"],
-        imgsz=cfg["imgsz"],
-        epochs=cfg["epochs"],
-        device="0",
-        cache=cfg["cache"],
-        batch=cfg["batch"],
-        hsv_h=cfg["hsv_h"],
-        hsv_s=cfg["hsv_s"],
-        hsv_v=cfg["hsv_v"],
-        degrees=cfg["degrees"],
-        translate=cfg["translate"],
-        scale=cfg["scale"],
-        shear=cfg["shear"],
-        fliplr=cfg["fliplr"],
-    )
-    return results
-
-
-def validate(cfg, best_model_path):
-    model = YOLO(best_model_path)
-    results = model.val(data=cfg["data_path"], imgsz=cfg["imgsz"], device="0")
-    return results
-
-
-def main(cfg):
-    results = train(cfg)
-    run_path = results.save_dir
-    print(f"Results saved to {run_path}")
-    # best_model_path = os.path.join(run_path, "weights", "best.pt")
-    # val_results = validate(cfg, best_model_path)
-
-
-if __name__ == "__main__":
-    args = parse_args()
-    cfg = load_config(args.config)
-    main(cfg)

### 2025-03-15 src/yolo/utils.py

@@ -1,13 +1,0 @@
-import os
-import shutil
-from random import shuffle
-from datetime import datetime
-from dotenv import load_dotenv
-import argparse
-
-load_dotenv()
-
-PROJECT_DIR = os.getenv('PROJECT_DIR')
-
-def get_labels_path():
-    return os.path.join(PROJECT_DIR, 'labeled')
